### 2021-11-10 papers/main.tex
Added a bunch

% \documentclass{uai2021} % for initial submission
\documentclass[]{uai2021} % after acceptance, for a revised
                                    % version; also before submission to
                                    % see how the non-anonymous paper
                                    % would look like
%% There is a class option to choose the math font
% \documentclass[mathfont=ptmx]{uai2021} % ptmx math instead of Computer
                                         % Modern (has noticable issues)
% \documentclass[mathfont=newtx]{uai2021} % newtx fonts (improves upon
                                          % ptmx; less tested, no support)
% NOTE: Only keep *one* line above as appropriate, as it will be replaced
%       automatically for papers to be published. Do not make any other
%       change above this note for an accepted version.

%% Choose your variant of English; be consistent
\usepackage[american]{babel}
% \usepackage[british]{babel}

%% Some suggested packages, as needed:
\usepackage{natbib} % has a nice set of citation styles and commands
    \bibliographystyle{plainnat}
    \renewcommand{\bibsection}{\subsubsection*{References}}
\usepackage{mathtools} % amsmath with fixes and additions
% \usepackage{siunitx} % for proper typesetting of numbers and units
\usepackage{booktabs} % commands to create good-looking tables
\usepackage{tikz} % nice language for creating drawings and diagrams
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{bm}

%% Provided macros
% \smaller: Because the class footnote size is essentially LaTeX's \small,
%           redefining \footnotesize, we provide the original \footnotesize
%           using this macro.
%           (Use only sparingly, e.g., in drawings, as it is quite small.)

%% Self-defined macros
\newcommand{\swap}[3][-]{#3#1#2} % just an example
\newcommand{\defeq}{\vcentcolon=}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\X}{\mathbf{X}}
\newcommand{\f}{\mathbf{f}}
\newcommand{\state}{\mathcal{S}}
\newcommand{\action}{\mathcal{A}}
\newcommand{\KL}{\mathrm{KL}}

\title{}

% The standard author block has changed for UAI 2021 to provide
% more space for long author lists and allow for complex affiliations
%
% All author information is authomatically removed by the class for the
% anonymous submission version of your paper, so you can already add your
% information below.
%
% Add authors
\author[1]{\href{mailto:<jj@example.edu>?Subject=LALAL}{Author}{}}

\begin{document}
\maketitle

\begin{abstract}
%   This is the abstract for this article.
%   It should give a self-contained single-paragraph summary of the article's contents, including context, results, and conclusions.
%   Avoid citations; but if you do, you must give essentially the whole reference.
%   For example: This whole paper is devoted to praising É. Š. Åland von Vèreweg's most recent book (“Utopia's government formation problems during the last millenium”, Springevier Publishers, 2016).
%   Also, do not put mathematical notation and abbreviations in your abstract; be descriptive.
%   So not “we solve \(x^2+A xy+y^2\), where \(A\) is an RV”, but “we solve quadratic equations in two unknowns in which a single coefficient is a random variable”.
%   The reason is that mathematical notation will not display correctly when the abstract is reused on the proceedings website, for example, and that one should not assume the abstract's reader knows the abbreviation.
%   Of course the same remarks hold for your paper's title.
\end{abstract}

\section{Introduction}
Bayesian reinforcement learning is an approach to RL that expresses uncertainty in the
Markov decision process (MDP) via a posterior distribution \citep{ghavamzadeh_bayesian_2015}.
The posterior captures the uncertainty in transition and reward distributions.

\section{Background}
\citet{fellows_bayesian_2021} defines the Bayesian Bellman operator (BBO) as:
\begin{equation}
    \B_{\omega, N}^\star(s,a) \defeq \E_{P(\phi \vert \D_\omega^N)} \left[ \hat{B}_\phi(s,a) \right],
\end{equation}
where \(\hat{B}_\phi(s,a) = \E_{P(b \mid s, a, \phi)}[b]\), is the conditional mean of the
parametric distribution \(P(b \vert s, a, \phi)\), which is a model of the true
data-generating distribution \(P(b \vert s, a, \omega)\). They further show that we can
find \(\omega^\star\) such that \(\hat{Q}_{\omega^\star} = \B^\star_{\omega^\star, N}\)
by minimising the mean squared Bayesian Bellman error (MSBBE):

\begin{equation}
    \mathrm{MSBBE}_N(\omega) \defeq \lVert \hat{Q}_{\omega} - \B^\star_{\omega, N} \lVert^2_{\rho, \pi}
\end{equation}
An unbiased estimate of \(\nabla_\omega \mathrm{MSBBE}_N(\omega)\) can be calculated as
long as we can sample from \(P(\phi \vert \D_\omega^N)\).

Nonlinear function approximators such as neural networks typically have an intractable
posterior, so we cannot calculate the posterior analytically. Instead we use a posterior approximation
\(q(\phi \vert \D_\omega^N) \approx P(\phi \vert \D_\omega^N)\), together with an algorithm
for approximate inference. \citet{fellows_bayesian_2021} presents the Bayesian Bellman Actor-Critic
using randomized priors \citep{osband_randomized_2018}, and show state of the art exploratory
behaviour.

For most approximate inference methods in deep learning, it is difficult to incorporate domain
knowledge into the prior. Typically the prior distribution is defined on the parameters as \(P(\phi)\),
while the knowledge exists in the function space \(P(a \vert s)\).

Functional variational Bayesian neural networks \citep{sun_functional_2019} lets us define a prior on the
\emph{function space}. In a Q-learning algorithm, this would be a function
\(f : \state \times \action \rightarrow \R\). For now we generalize, and say that
\(f : \mathcal{X} \rightarrow \mathcal{Y}\).
\citet{sun_functional_2019} show that for two stochastic processes \(P\) and \(Q\):

\begin{equation}
    \KL[P \Vert Q] = \sup_{n \in \N, \X \in \mathcal{X}^n} \KL \left[ P_\X \Vert Q_\X \right],
\end{equation}

where \(\X \in \mathcal{X}^n\) is a finite measurement set and \(P_\X, Q_\X\) are the marginal distributions
at \(\X\). They further show that if \(\f^\X\) are the function values at points \(\X\), then

\begin{multline}\label{eq:fkl}
    \nabla_\phi \KL[q_\phi(\f^X) \Vert p(\f^\X)] \\
    = \E \left[ \nabla_\phi \f^\X( \nabla_\f \log q(\f^\X) - \nabla_\f \log p(\f^\X)) \right].
\end{multline}

The difficult part in \eqref{eq:fkl} is to estimate \(\nabla_\f \log q(\f^\X)\) and \(\nabla_\f \log p(\f^\X)\).
To estimate these log-density gradients, they use a spectral Stein gradient estimator \citep{shi_spectral_2018}.
Given enough function value samples, the spectral Stein gradient estimator can estimate score functions
for both in-distribution and out-of-distribution samples. This means that we can use it to estimate
both gradients. \(\nabla_\f \log q(\f^\X)\) is likely intractable intractable, considering \(q_\phi\) is
a neural network with stochastic weights. Depending on how we define the prior, however, \(\nabla_\f \log p(\f^\X)\)
can be easy to compute analytically. To reduce variance in the gradients we aim to define tractable priors.

\section{Method}
Instead of a prior on the parameter space, we would like to have a prior on the \(Q\)-function space.
Using the functional variational neural network framework explored earlier, our maximization target
becomes:

\begin{equation}
    \log p(\D_\omega^N \vert f) - \KL \left[ q(\f^{\D_\omega^N}, \f^M) \Vert p(\f^{\D_\omega^N}, \f^M) \right],
\end{equation}
where \(\f^{\D_\omega^N}\) is \(f\) applied to the dataset \(\D_\omega^N\), and \(\f^M\) is \(f\) applied to
a set of i.i.d. random points \(M = \{m_i \sim c \mid i=1,\dots,k\} \subseteq \state \times \action\)
with full support. We will let

\begin{equation}
    M = \{(s_i, a_j) \; \forall s_i \in \D_\omega^N,\, \forall a_j \in \action\}. 
\end{equation}
To justify this we need to show that \(supp(c) = \state \times \action\). Assumption 1 from
\citet{fellows_bayesian_2021} assumes that each state \(s_i\) is drawn i.i.d from a distribution with
support over \(\state\), or from an ergodic Markov chain defined over a \(\sigma\)-algebra that is
countably generated from \(\state\). If we keep this assumption, then by definition \(supp(c) = \state \times \action\).

Since we are modeling \(q_\phi\) with a Bayesian neural network, and \(Q_\omega\) with a neural network,
we have a bilevel optimization problem. To solve this, we employ a similar strategy to \cite{fellows_bayesian_2021},
where we have a two-timescale gradient update. \(\phi\) and \(\omega\) are updated using stochastic
gradient descent at different timescales to ensure stable convergence.

% We can now define a prior \(P(f)\), however, this prior exists in the space
% \(P(Q \vert s, a) : (\state \times \action \rightarrow \R) \rightarrow \R\), which can be hard to
% define. We would like the prior to be of the form \(P(a \vert s)\).

\begin{algorithm}
\caption{Functional Bayesian RL}
\begin{algorithmic}
    \State \(\D \gets \emptyset\)
    \State \(s \sim P_0\)
    \State Initialize \(\phi, \omega\)
    \While{not converged}
        \State \(f \sim q_\phi\)
        \State \(a \sim \arg\max_a f(s,a)\)
        \State \(s' \sim P(\cdot \vert s,a)\)
        \State \(r = r(s',a,s)\)
        \State \(\D \gets \D \cup \{s,a,r,s'\}\)
        \State \Call{UpdatePosterior}{$\phi, \omega, \D$}
    \EndWhile
    \Statex
    \Function{UpdatePosterior}{$\phi, \omega, \D$}
    \State \(k \gets 0\)
        \While{not converged}
            \State \(T \sim \D\)
            \State \(\f \gets \{f_i \sim q_\phi \text{ for } i=1,\dots,k\}\)
            \State \(\mathcal{F} \gets \emptyset\)
            \State \(\Delta_\mathcal{L} \gets 0\)
            \For{\(\{s,a,r,s'\} \in T\)}
                \State \(\bm{\hat{a}} \gets \arg\max_a \f(s,a)\)
                \State \(\mathcal{F} \gets \mathcal{F} \cup \f(s,a)\)
                \State \(G \gets r + \gamma Q_\omega(s,a)\)
                \State \(\Delta_\mathcal{L} \gets \Delta_\mathcal{L} - \frac{1}{k} \frac{1}{\lvert T \rvert} \nabla_\phi \log p(\bm{\hat{a}} \vert G)\)
            \EndFor
            \State \(\Delta_\KL \gets SSGE(p, \mathcal{F})\)
            \State \(\phi \gets \phi + \eta_\phi (\Delta_\mathcal{L} - \Delta_\KL)\)
            \State \(\hat{B}_\phi \gets \frac{1}{k}\frac{1}{\lvert T \rvert}\sum_{i=1}^k \sum_{b \in \mathcal{F}} b\)
            \State \(\Delta_\omega \gets \sum_{\{s,a,r,s'\} \in T} \nabla_\omega \lVert \hat{B}_\phi(s,a) - Q_\omega(s,a) \rVert^2_2 \)
            \State \(\omega \gets \omega - \eta_\omega \Delta_\omega\)
        \EndWhile
    \EndFunction
\end{algorithmic}
\end{algorithm}

\section{Background}
A reinforcement learning environement is modelled as a Markov decision process (MDP)
\(M = \langle \state, \action, R, P, P_0, \gamma \rangle\), where \(\state\) is the
state space and \(\action\) is the set of available actions. At time \(t=0\) a state
\(s_0\) is sampled from the distribution \(P_0(\cdot)\). At each timestep an action
\(a_t \sim \pi(\cdot \vert s_t)\) is selected and the agent transitions to a new state
state \(s_{t+1} \sim P(\cdot \vert s_t, a_t)\). A scalar reward
\(r_t \sim R(\cdot \vert s_{t+1}, s_t, a_t)\) is observed.

\begin{acknowledgements} % will be removed in pdf for initial submission,
                         % so you can already fill it to test with the
                         % ‘accepted’ class option
    Briefly acknowledge people and organizations here.

    \emph{All} acknowledgements go in this section.
\end{acknowledgements}

\bibliography{uai2021-template}

\appendix
% NOTE: necessary when ptmx or no mathfont class option is given
% \providecommand{\upGamma}{\Gamma}
% \providecommand{\uppi}{\pi}
% \section{Math font exposition}
% How math looks in equations is important:
% \begin{equation*}
%   F_{\alpha,\beta}^\eta(z) = \upGamma(\tfrac{3}{2}) \prod_{\ell=1}^\infty\eta \frac{z^\ell}{\ell} + \frac{1}{2\uppi}\int_{-\infty}^z\alpha \sum_{k=1}^\infty x^{\beta k}\mathrm{d}x.
% \end{equation*}
% However, one should not ignore how well math mixes with text:
% The frobble function \(f\) transforms zabbies \(z\) into yannies \(y\).
% It is a polynomial \(f(z)=\alpha z + \beta z^2\), where \(-n<\alpha<\beta/n\leq\gamma\), with \(\gamma\) a positive real number.

\end{document}

### 2021-11-19 papers/main.tex
Friday commit

@@
 
-\section{Introduction}
-Bayesian reinforcement learning is an approach to RL that expresses uncertainty in the
-Markov decision process (MDP) via a posterior distribution \citep{ghavamzadeh_bayesian_2015}.
-The posterior captures the uncertainty in transition and reward distributions.
+% \section{Introduction}
+% Bayesian reinforcement learning is an approach to RL that expresses uncertainty in the
+% Markov decision process (MDP) via a posterior distribution \citep{ghavamzadeh_bayesian_2015}.
+% The posterior captures the uncertainty in transition and reward distributions.
 
 \section{Background}
-\citet{fellows_bayesian_2021} defines the Bayesian Bellman operator (BBO) as:
+A reinforcement learning environement is modelled as a Markov decision process (MDP)
+\(M = \langle \state, \action, r, P, P_0, \gamma \rangle\), where \(\state\) is the
+state space and \(\action\) is the set of available actions. At time \(t=0\) a state
+\(s_0\) is sampled from the distribution \(P_0(\cdot)\). At each timestep an action
+\(a_t \sim \pi(\cdot \vert s_t)\) is selected and the agent transitions to a new state
+state \(s_{t+1} \sim P(\cdot \vert s_t, a_t)\). A scalar reward
+\(r_{t+1} = r(\cdot \vert s_{t+1}, s_t, a_t)\) is observed. As the agent and environement
+interact in a sequence of time steps, a history of observations
+\(\mathcal{H}_t = (s_0, a_0, s_1, r_1, a_1, s_2, r_2, \dots, s_t, r_t)\) is collected.
+The goal is to find a policy \(\pi^\star\), such that sampling actions
+\(a \sim \pi^*(\cdot \vert s)\) maximizes the expected future reward,
+\(J^\pi \defeq \E_\pi \left[ \sum_{t=0}^\infty \gamma^t r_t \right]\). An efficient
+agent must be able to learn from the data it collects, but since the data is
+dependent on the policy, it must also prioritize to explore states and actions that
+the agent can learn a lot from.
+
+The \(Q\)-function, \(Q^\pi(s,a)\), is defined as the expected reward of taking action
+\(a\) in state \(s\) and then following policy \(\pi\) thereafter:
+\(Q^\pi \defeq \E_\pi \left[ \sum_{t=0}^\infty \gamma^t r_t \vert s_0=0, a_0=0 \right]\).
+The Bellman operator on \(Q^\pi\) is defined as
+\(\B[Q^\pi](s_t,a_t) \defeq \E_{P(s_{t+1} \vert s_t, a_t)\pi(a_{t+1} \vert s+t)}
+\left[ r(s_{t+1}, s_t, a) + \gamma Q^\pi(s_{t+1}, a_{t+1}) \right]\). With the
+\(Q\)-function we can define a policy \(\pi(a \vert s) = \arg\max_a Q(s,a)\).
+In deep RL, we model \(Q\) with a neural network \(\hat{Q}_\omega\).
+One way to facilitate exploration in this policy is to introduce uncertainty in the
+\(Q\)-value. \cite{fellows_bayesian_2021} does this by defining the Bayesian Bellman
+operator (BBO). They define \(P_B(b \vert s, a, \omega)\) as the distribution over
+Bellman functions such that for a noisy sample \(b_i \sim P_B(b \vert s,a,\omega)\),
+\(b_i = \B[\hat{Q}_\omega](s_i, a_i) + \eta_i\). Then we approximate this with a
+distribution parameterized by \(\phi\) such that
+\(P(b \vert s,a,\phi) \approx P(b \vert s,a,\omega)\).
 \begin{equation}
-    \B_{\omega, N}^\star(s,a) \defeq \E_{P(\phi \vert \D_\omega^N)} \left[ \hat{B}_\phi(s,a) \right],
+    \B_{\omega, N}^\star(s,a) \defeq \E_{P(\phi \vert \D_\omega^N)} \left[ \hat{B}_\phi(s,a) \right].
 \end{equation}
-where \(\hat{B}_\phi(s,a) = \E_{P(b \mid s, a, \phi)}[b]\), is the conditional mean of the
-parametric distribution \(P(b \vert s, a, \phi)\), which is a model of the true
-data-generating distribution \(P(b \vert s, a, \omega)\). They further show that we can
-find \(\omega^\star\) such that \(\hat{Q}_{\omega^\star} = \B^\star_{\omega^\star, N}\)
+Here, \(\hat{B}_\phi(s,a) = \E_{P(b \mid s, a, \phi)}[b]\), is the conditional mean of
+\(P(b \vert s, a, \phi)\), and the data \(\D_\omega^N\) is defined as the collection of
+sampled \(Q\)-values, states and actions \(\D_\omega^N \defeq \{b_i, s_i, a_i\}_{i=1:N}\).
+Under the assumption that each state \(s_i\) is drawn i.i.d from a distribution with
+support over \(\state\), or from an ergodic Markov chain defined over a \(\sigma\)-algebra that is
+countably generated from \(\state\) they find that \(\omega^\star\) such that
+\(\hat{Q}_{\omega^\star} = \B^\star_{\omega^\star, N}\) can be found 
 by minimising the mean squared Bayesian Bellman error (MSBBE):
-
 \begin{equation}
-    \mathrm{MSBBE}_N(\omega) \defeq \lVert \hat{Q}_{\omega} - \B^\star_{\omega, N} \lVert^2_{\rho, \pi}
+    \mathrm{MSBBE}_N(\omega) \defeq \lVert \hat{Q}_{\omega} - \B^\star_{\omega, N} \lVert^2_{\rho, \pi},
 \end{equation}
-An unbiased estimate of \(\nabla_\omega \mathrm{MSBBE}_N(\omega)\) can be calculated as
-long as we can sample from \(P(\phi \vert \D_\omega^N)\).
+And that an unbiased estimate of \(\nabla_\omega \mathrm{MSBBE}_N(\omega)\) can be calculated
+as long as we can sample from \(P(\phi \vert \D_\omega^N)\).
 
@@
 
+% \section{Background}
+% \citet{fellows_bayesian_2021} defines the Bayesian Bellman operator (BBO) as:
+% \begin{equation}
+%     \B_{\omega, N}^\star(s,a) \defeq \E_{P(\phi \vert \D_\omega^N)} \left[ \hat{B}_\phi(s,a) \right],
+% \end{equation}
+% where \(\hat{B}_\phi(s,a) = \E_{P(b \mid s, a, \phi)}[b]\), is the conditional mean of the
+% parametric distribution \(P(b \vert s, a, \phi)\), which is a model of the true
+% data-generating distribution \(P(b \vert s, a, \omega)\). They further show that we can
+% find \(\omega^\star\) such that \(\hat{Q}_{\omega^\star} = \B^\star_{\omega^\star, N}\)
+% by minimising the mean squared Bayesian Bellman error (MSBBE):
+
+% \begin{equation}
+%     \mathrm{MSBBE}_N(\omega) \defeq \lVert \hat{Q}_{\omega} - \B^\star_{\omega, N} \lVert^2_{\rho, \pi}
+% \end{equation}
+% An unbiased estimate of \(\nabla_\omega \mathrm{MSBBE}_N(\omega)\) can be calculated as
+% long as we can sample from \(P(\phi \vert \D_\omega^N)\).
+
+% Nonlinear function approximators such as neural networks typically have an intractable
+% posterior, so we cannot calculate the posterior analytically. Instead we use a posterior approximation
+% \(q(\phi \vert \D_\omega^N) \approx P(\phi \vert \D_\omega^N)\), together with an algorithm
+% for approximate inference. \citet{fellows_bayesian_2021} presents the Bayesian Bellman Actor-Critic
+% using randomized priors \citep{osband_randomized_2018}, and show state of the art exploratory
+% behaviour.
+
+% For most approximate inference methods in deep learning, it is difficult to incorporate domain
+% knowledge into the prior. Typically the prior distribution is defined on the parameters as \(P(\phi)\),
+% while the knowledge exists in the function space \(P(a \vert s)\).
+
+% Functional variational Bayesian neural networks \citep{sun_functional_2019} lets us define a prior on the
+% \emph{function space}. In a Q-learning algorithm, this would be a function
+% \(f : \state \times \action \rightarrow \R\). For now we generalize, and say that
+% \(f : \mathcal{X} \rightarrow \mathcal{Y}\).
+% \citet{sun_functional_2019} show that for two stochastic processes \(P\) and \(Q\):
+
+% \begin{equation}
+%     \KL[P \Vert Q] = \sup_{n \in \N, \X \in \mathcal{X}^n} \KL \left[ P_\X \Vert Q_\X \right],
+% \end{equation}
+
+% where \(\X \in \mathcal{X}^n\) is a finite measurement set and \(P_\X, Q_\X\) are the marginal distributions
+% at \(\X\). They further show that if \(\f^\X\) are the function values at points \(\X\), then
+
+% \begin{multline}\label{eq:fkl}
+%     \nabla_\phi \KL[q_\phi(\f^X) \Vert p(\f^\X)] \\
+%     = \E \left[ \nabla_\phi \f^\X( \nabla_\f \log q(\f^\X) - \nabla_\f \log p(\f^\X)) \right].
+% \end{multline}
+
+% The difficult part in \eqref{eq:fkl} is to estimate \(\nabla_\f \log q(\f^\X)\) and \(\nabla_\f \log p(\f^\X)\).
+% To estimate these log-density gradients, they use a spectral Stein gradient estimator \citep{shi_spectral_2018}.
+% Given enough function value samples, the spectral Stein gradient estimator can estimate score functions
+% for both in-distribution and out-of-distribution samples. This means that we can use it to estimate
+% both gradients. \(\nabla_\f \log q(\f^\X)\) is likely intractable intractable, considering \(q_\phi\) is
+% a neural network with stochastic weights. Depending on how we define the prior, however, \(\nabla_\f \log p(\f^\X)\)
+% can be easy to compute analytically. To reduce variance in the gradients we aim to define tractable priors.
+
 \section{Method}
@@
 \end{equation}
-To justify this we need to show that \(supp(c) = \state \times \action\). Assumption 1 from
-\citet{fellows_bayesian_2021} assumes that each state \(s_i\) is drawn i.i.d from a distribution with
-support over \(\state\), or from an ergodic Markov chain defined over a \(\sigma\)-algebra that is
-countably generated from \(\state\). If we keep this assumption, then by definition \(supp(c) = \state \times \action\).
+To justify this we need to show that \(supp(c) = \state \times \action\).
+Under the same assumption about the distribution of each state \(s_i\) from BBO,
+\(supp(c) = \state \times \action\) follows trivially.
 
@@
     \Function{UpdatePosterior}{$\phi, \omega, \D$}
-    \State \(k \gets 0\)
         \While{not converged}
@@
 \end{algorithm}
-
-\section{Background}
-A reinforcement learning environement is modelled as a Markov decision process (MDP)
-\(M = \langle \state, \action, R, P, P_0, \gamma \rangle\), where \(\state\) is the
-state space and \(\action\) is the set of available actions. At time \(t=0\) a state
-\(s_0\) is sampled from the distribution \(P_0(\cdot)\). At each timestep an action
-\(a_t \sim \pi(\cdot \vert s_t)\) is selected and the agent transitions to a new state
-state \(s_{t+1} \sim P(\cdot \vert s_t, a_t)\). A scalar reward
-\(r_t \sim R(\cdot \vert s_{t+1}, s_t, a_t)\) is observed.
 

### 2021-11-19 scripts/RLExp_DUQN_Atari.jl

@@ -1,0 +1,231 @@
+using Base.Iterators: tail
+using BSON: @load, @save
+using Conda
+using CUDA
+using Distributions: Uniform, Product
+using DrWatson
+using Flux
+using Images
+using Logging
+using RLExp
+using Random
+using ReinforcementLearning
+using Setfield
+using Statistics
+using Wandb
+
+applychain(::Tuple{}, x, n) = x
+function applychain(fs::Tuple, x, n)
+    f = first(fs)
+    if isa(f, NoisyDense) || isa(f, NoisyConv) || isa(f, Split{Tuple{NoisyDense, NoisyDense}})
+        y = applychain(tail(fs), f(x, n), n)
+    else
+        y = applychain(tail(fs), f(x), n)
+    end
+    y
+end
+(c::Chain)(x, n) = applychain(c.layers, x, n)
+
+function RL.Experiment(
+    ::Val{:RLExp},
+    ::Val{:DUQN},
+    ::Val{:Atari},
+    name::AbstractString;
+    restore=nothing,
+    seed = 1
+)
+    """
+    SEEDS
+    """
+    rng = Random.GLOBAL_RNG
+    Random.seed!(rng, seed)
+    device_rng = CUDA.functional() ? CUDA.CURAND.RNG() : rng
+    Random.seed!(device_rng, isnothing(seed) ? nothing : hash(seed + 1))
+
+    """
+    SET UP ENVIRONMENT
+    """
+    N_FRAMES = 4
+    STATE_SIZE = (84, 84)
+    env = atari_env_factory(
+        name,
+        STATE_SIZE,
+        N_FRAMES;
+        seed = isnothing(seed) ? nothing : hash(seed + 1),
+    )
+    N_ACTIONS = length(action_space(env))
+
+    """
+    SET UP LOGGING
+    """
+    simulation = @ntuple seed
+    lg = WandbLogger(project = "RLExp", name="DUQN_Atari_" * savename(simulation))
+    save_dir = datadir("sims", "DUQN", "CartPole", $(now()))
+
+    """
+    CREATE MODELS
+    """
+    init = glorot_uniform(rng)
+
+    if restore === nothing
+        B_model = Chain(
+            x -> x ./ 255,
+            CrossCor((8, 8), N_FRAMES => 32, relu; stride = 4, pad = 2, init = init),
+            CrossCor((4, 4), 32 => 64, relu; stride = 2, pad = 2, init = init),
[…]

### 2021-11-19 scripts/RLExp_DUQN_MountainCar.jl

@@ -44,7 +44,7 @@ function RL.Experiment(
     save_dir = datadir("sims", "DUQN", savename(simulation, "jld2"))
 
     """
-    CREATE MODEL
+    CREATE MODELS
     """
     init = glorot_uniform(rng)
 
@@ -54,43 +54,14 @@ function RL.Experiment(
         NoisyDense(128, 128, relu; init_μ = init),
         Split(NoisyDense(128, na; init_μ = init),
               NoisyDense(128, na, softplus; init_μ = init))
-    ) |> cpu
-    opt = ADAM(3e-3)
+    ) |> gpu
 
     model2 = Chain(
         Dense(ns, 128, relu; init = init),
         Dense(128, 128, relu; init = init),
         Dense(128, na; init = init),
-    ) |> cpu
-    opt2 = ADAM(3e-3)
+    ) |> gpu
 
-    # u = Product([Uniform(-1.2f0, 0.6f0),
-    #             Uniform(-0.07f0, 0.07f0)])
-    # sse = SpectralSteinEstimator(0.05, nothing, 0.99)
-
-    # for _=1:1_000
-    #     samples = rand(u, 32)
-
-    #     gs = gradient(params(model)) do
-    #         b_all = model(samples, 100)
-    #         b_rand = reshape(b_all[1], :, 100)
-    #         S = entropy_surrogate(sse, permutedims(b_rand, (2, 1)))
-    #         pr = [-1 0 1] .* samples[2,:]
-    #         pr = reshape(repeat(pr, 1,  100), :, 100)
-    #         H = sum((b_rand .- 100 .* pr) .^ 2 ./ (2 * 100.0f0 .^ 2)) ./ (size(b_rand, 2) .* 32)
-    #         KL = H - S
-    #     end
-    #     Flux.update!(opt, params(model), gs)
-        
-    #     gs = gradient(params(model2)) do 
-    #         b = model(samples, 100)[1]
-    #         B̂ = dropdims(mean(b, dims=ndims(b)), dims=ndims(b))
-    #         q = model2(samples)
-    #         𝐿 = sum((q .- B̂) .^ 2)
-    #         return 𝐿
-    #     end
-    #     Flux.update!(opt2, params(model2), gs)
-    # end
 
     """
     CREATE AGENT
@@ -100,18 +71,20 @@ function RL.Experiment(
             learner = DUQNLearner(
                 B_approximator = NeuralNetworkApproximator(
                     model = model,
-                    optimizer = ADAM(3e-3),
[…]

### 2021-11-19 src/RLExp.jl

@@ -1,12 +1,11 @@
 module RLExp
 
-export BDQNLearner, atari_env_factory, NoisyDense, Split, BayesianGreedyExplorer
+export BDQNLearner, atari_env_factory, NoisyDense, NoisyConv, Split, BayesianGreedyExplorer
 export SpectralSteinEstimator, entropy_surrogate
 export TotalOriginalRewardPerEpisode, TotalBatchOriginalRewardPerEpisode, CloseLogger
 export ResizeImage
 export get_screen
-export NoisyDense2
-export DUQNLearner
+export DUQNLearner, FlatPrior, GeneralPrior, GaussianPrior
 
 using ArcadeLearningEnvironment
 using ArcadeLearningEnvironment: getScreenRGB, getScreenWidth, getScreenHeight
@@ -30,6 +29,5 @@ include("algorithms/common.jl")
 include("algorithms/BDQN.jl")
 include("algorithms/GDQN.jl")
 include("algorithms/DUQN.jl")
-include("algorithms/explorers.jl")
 
 end

### 2021-11-19 src/algorithms/DUQN.jl

@@ -1,9 +1,8 @@
-export DUQNLearner
+export DUQNLearner, FlatPrior, GeneralPrior, GaussianPrior
 import ReinforcementLearning.RLBase.update!
 
 using DataStructures: DefaultDict
 using Distributions: Uniform, Product
-using Random: randn!
 using StatsBase: sample
 import Statistics.mean
 
@@ -11,44 +10,73 @@ Statistics.mean(a::CuArray) = sum(a) / length(a)
 Statistics.mean(a::CuArray, dims) = sum(a, dims) / prod(size(a, dims))
 
 
+abstract type AbstractPrior end
+
+struct FlatPrior <: AbstractPrior end
+(p::FlatPrior)(s::AbstractArray, t::AbstractArray) = zero(eltype(t))
+
+struct GeneralPrior{F} <: AbstractPrior
+    f::F
+end
+(p::GeneralPrior)(s::AbstractArray, t::AbstractArray) = p.f(s, t)
+
+struct GaussianPrior <: AbstractPrior
+    μ
+    σ
+end
+(p::GaussianPrior)(_, t::AbstractArray) = sum((t .- p.μ) .^ 2 ./ (2p.σ .^ 2))
+
+abstract type AbstractMeasure end
+
 mutable struct DUQNLearner{
     Tq<:AbstractApproximator,
     Tt<:AbstractApproximator,
+    P<:AbstractPrior,
+    M<:Union{AbstractMeasure, Nothing},
     R<:AbstractRNG,
 } <: AbstractLearner
     B_approximator::Tq
     Q_approximator::Tt
+    prior::P
+    obs_var::Union{Float32, Nothing}
     min_replay_history::Int
     B_update_freq::Int
     Q_update_freq::Int
+    updates_per_step::Int
     update_step::Int
     sampler::NStepBatchSampler
     rng::R
     sse::SpectralSteinEstimator
     injected_noise::Float32
     n_samples::Int
-    # for logging
+    measure::M
+    training::Bool
     logging_params
 end
 
 function DUQNLearner(;
     B_approximator::Tq,
     Q_approximator::Tt,
-    stack_size::Union{Int,Nothing} = nothing,
+    prior::AbstractPrior = FlatPrior(),
+    obs_var::Union{Float32, Nothing} = nothing,
+    stack_size::Union{Int, Nothing} = nothing,
     γ::Float32 = 0.99f0,
     batch_size::Int = 32,
     update_horizon::Int = 1,
[…]

### 2021-11-19 src/algorithms/explorers.jl

@@ -1,4 +1,0 @@
-struct BayesianGreedyExplorer <: AbstractExplorer end
-
-# (s::BayesianGreedyExplorer)(values) = print(values);findmax(values[1])[2]
-# (s::BayesianGreedyExplorer)(values, mask) = findmax(values[1], mask)[2]

### 2021-12-03 scripts/RLExp_DUQN_Atari.jl
TEMPORARY DEPLOY COMMIT

@@ -56,7 +56,7 @@ function RL.Experiment(
                         "n_samples" => 100,
                         "η" => 0.01,
                         "nev" => 20,
-                        "is_enable_double_DQN" => true,
+                        "is_enable_double_DQN" => false,
                         "traj_capacity" => 1_000_000,
                         "seed" => 1,
                      ),

### 2021-12-09 papers/main.tex
TEMPORARY DEPLOY COMMIT

@@
 One way to facilitate exploration in this policy is to introduce uncertainty in the
-\(Q\)-value. \cite{fellows_bayesian_2021} does this by defining the Bayesian Bellman
+\(Q\)-value.
+\citet{fortunato_noisy_2019} introduced noisy networks for exploration.
+These are networks with stochastic weights, where each weight \(w^{(l)}_{ij}\)
+has an added pertrubaition sampled from a noise distribution with standard deviation \(\sigma^{(l)}_{ij}\).
+After initializing \(\bm{\mu}\) and \(\bm{\sigma}\) such that the network has sufficient
+stochasticity for exploration, both parameters are learned using standard backpropagation.
+The approach is similar to variational inference schemes such as bayes by backprop~\cite{blundell_weight_2015} where the weights are normally distributed with mean 
+\(\mu^{(l)}_{ij}\) and standard deviation \(\sigma^{(l)}_{ij}\),
+
+\cite{fellows_bayesian_2021} does this by defining the Bayesian Bellman
 operator (BBO). They define \(P_B(b \vert s, a, \omega)\) as the distribution over

### 2021-12-09 scripts/RLExp_DUQN_Atari.jl

@@ -40,8 +40,8 @@ function RL.Experiment(
     lg = WandbLogger(project = "RLExp",
                      name="DUQN_Atari($name)",
                      config = Dict(
-                        "B_lr" => 6.25e-5,
-                        "Q_lr" => 0.001,
+                        "B_lr" => 1e-4,
+                        "Q_lr" => 1e-3,
                         "B_clip_norm" => 10.0,
                         "B_update_freq" => 4,
                         "Q_update_freq" => 4,
@@ -49,14 +49,14 @@ function RL.Experiment(
                         "gamma" => 0.99,
                         "update_horizon" => 1,
                         "batch_size" => 32,
-                        "min_replay_history" => 20000,
+                        "min_replay_history" => 50000,
                         "updates_per_step" => 1,
                         "λ" => 1.0,
                         "prior" => "GaussianPrior(0, 10)",
                         "n_samples" => 100,
                         "η" => 0.01,
                         "nev" => 20,
-                        "is_enable_double_DQN" => false,
+                        "is_enable_double_DQN" => true,
                         "traj_capacity" => 1_000_000,
                         "seed" => 1,
                      ),

### 2021-12-09 scripts/RLExp_DUQN_MountainCar.jl

@@ -1,9 +1,11 @@
 using Base.Iterators: tail
 using Conda
 using CUDA
+using Dates: now
 using Distributions: Uniform, Product
 using DrWatson
 using Flux
+using Flux: Optimiser
 using Logging
 using RLExp
 using Random
@@ -12,20 +14,51 @@ using Setfield
 using Statistics
 using Wandb
 
-applychain(::Tuple{}, x, n) = x
-applychain(fs::Tuple, x, n) = applychain(tail(fs), first(fs)(x, n), n)
-(c::Chain)(x, n) = applychain(c.layers, x, n)
+applychain(::Tuple{}, x, n; kwargs...) = x
+applychain(fs::Tuple, x, n; kwargs...) = applychain(tail(fs), first(fs)(x, n; kwargs...), n; kwargs...)
+(c::Chain)(x, n; kwargs...) = applychain(c.layers, x, n; kwargs...)
 
 function RL.Experiment(
     ::Val{:RLExp},
     ::Val{:DUQN},
     ::Val{:MountainCar},
-    seed = 1
-)
+    name,
+   )
+
+    """
+    SET UP LOGGING
+    """
+    lg = WandbLogger(project = "RLExp",
+                     name="DUQN_MountainCar",
+                     config = Dict(
+                        "B_lr" => 1e-3,
+                        "Q_lr" => 0.05,
+                        "B_clip_norm" => 1.0,
+                        "B_update_freq" => 1,
+                        "Q_update_freq" => 1,
+                        "B_opt" => "ADAM",
+                        "gamma" => 1.0,
+                        "update_horizon" => 1,
+                        "batch_size" => 32,
+                        "min_replay_history" => 1,
+                        "updates_per_step" => 1,
+                        "λ" => 1.0,
+                        "prior" => "GaussianPrior(0, 100)",
+                        "n_samples" => 100,
+                        "η" => 0.01,
+                        "nev" => 20,
+                        "is_enable_double_DQN" => true,
+                        "traj_capacity" => 1_000_000,
+                        "seed" => 1,
+                     ),
+    )
+    save_dir = datadir("sims", "DUQN", "MountainCar", "$(now())")
+
     """
     SEEDS
     """
-    rng = Random.GLOBAL_RNG
+    seed = get_config(lg, "seed")
+    rng = MersenneTwister()
     Random.seed!(rng, seed)
[…]

### 2021-12-20 papers/main.tex
TEMPORARY DEPLOY COMMIT

--- 2021-11-19 papers/main.tex
@@
 
-\title{}
+\title{Scalable and Parameter-Free Optimal Regret Reinforcement Learning}
 
@@
 The goal is to find a policy \(\pi^\star\), such that sampling actions
-\(a \sim \pi^*(\cdot \vert s)\) maximizes the expected future reward,
-\(J^\pi \defeq \E_\pi \left[ \sum_{t=0}^\infty \gamma^t r_t \right]\). An efficient
+\(a \sim \pi^*(\cdot \vert s)\) maximizes the expected accumulated and discounted future reward,
+\(J^\pi \defeq \E_\pi \left[ \sum_{t=1}^\infty \gamma^t r_t \right]\). An efficient
 agent must be able to learn from the data it collects, but since the data is
@@
 
+The efficiency of exploration can be measured in regret.
+The regret of a policy is the difference in the expected reward obtained by
+following that policy, and the expected reward for an optimal policy.
+An learning algorithm's efficiency in exploration can be measured by its
+cumulative regret over time. One of the simplest reinforcement learning 
+problems is the multi-arm bandit problem. This is an MDP with no state and no
+transition probabilities. One exploration strategy employed in most Q-learning
+algorithms to date, \(\epsilon\)-greedy is provably inefficient, and has a
+regret bound that grows linearly with time. There are several optimal algorithms
+for this problem, but perhaps the simplest one is called Thompson sampling.
+Thompson sampling approximates a posterior distribution of the expected reward
+for each action. The next action is decided by sampling rewards for each action
+from the posterior distribution, and selecting the action that gave the highest
+reward. Bayesian methods been also been shown to behave efficiently with respect
+to cumulative regret \cite{osband_generalization_2016} on general MDPs.
+%\textcolor{red}{Optimal Regret + Thompson sampling }
+
 The \(Q\)-function, \(Q^\pi(s,a)\), is defined as the expected reward of taking action
 \(a\) in state \(s\) and then following policy \(\pi\) thereafter:
-\(Q^\pi \defeq \E_\pi \left[ \sum_{t=0}^\infty \gamma^t r_t \vert s_0=0, a_0=0 \right]\).
+\(Q^\pi \defeq \E_\pi \left[ \sum_{t=0}^\infty \gamma^t r_t \vert s_0=S, a_0=A \right]\).
 The Bellman operator on \(Q^\pi\) is defined as
-\(\B[Q^\pi](s_t,a_t) \defeq \E_{P(s_{t+1} \vert s_t, a_t)\pi(a_{t+1} \vert s+t)}
+\(\B[Q^\pi](s_t,a_t) \defeq \E_{P(s_{t+1} \vert s_t, a_t)\pi(a_{t+1} \vert s_t)}
 \left[ r(s_{t+1}, s_t, a) + \gamma Q^\pi(s_{t+1}, a_{t+1}) \right]\). With the
-\(Q\)-function we can define a policy \(\pi(a \vert s) = \arg\max_a Q(s,a)\).
-In deep RL, we model \(Q\) with a neural network \(\hat{Q}_\omega\).
-One way to facilitate exploration in this policy is to introduce uncertainty in the
-\(Q\)-value. \cite{fellows_bayesian_2021} does this by defining the Bayesian Bellman
-operator (BBO). They define \(P_B(b \vert s, a, \omega)\) as the distribution over
-Bellman functions such that for a noisy sample \(b_i \sim P_B(b \vert s,a,\omega)\),
-\(b_i = \B[\hat{Q}_\omega](s_i, a_i) + \eta_i\). Then we approximate this with a
-distribution parameterized by \(\phi\) such that
-\(P(b \vert s,a,\phi) \approx P(b \vert s,a,\omega)\).
-\begin{equation}
-    \B_{\omega, N}^\star(s,a) \defeq \E_{P(\phi \vert \D_\omega^N)} \left[ \hat{B}_\phi(s,a) \right].
-\end{equation}
-Here, \(\hat{B}_\phi(s,a) = \E_{P(b \mid s, a, \phi)}[b]\), is the conditional mean of
-\(P(b \vert s, a, \phi)\), and the data \(\D_\omega^N\) is defined as the collection of
-sampled \(Q\)-values, states and actions \(\D_\omega^N \defeq \{b_i, s_i, a_i\}_{i=1:N}\).
-Under the assumption that each state \(s_i\) is drawn i.i.d from a distribution with
-support over \(\state\), or from an ergodic Markov chain defined over a \(\sigma\)-algebra that is
-countably generated from \(\state\) they find that \(\omega^\star\) such that
-\(\hat{Q}_{\omega^\star} = \B^\star_{\omega^\star, N}\) can be found 
-by minimising the mean squared Bayesian Bellman error (MSBBE):
-\begin{equation}
-    \mathrm{MSBBE}_N(\omega) \defeq \lVert \hat{Q}_{\omega} - \B^\star_{\omega, N} \lVert^2_{\rho, \pi},
-\end{equation}
-And that an unbiased estimate of \(\nabla_\omega \mathrm{MSBBE}_N(\omega)\) can be calculated
-as long as we can sample from \(P(\phi \vert \D_\omega^N)\).
+\(Q\)-function we can define a policy that always picks the action with the 
+highest \(Q\)-value in any state. We can't find \(Q\) exactly, but with a good
+approximation this policy, \(\pi(a \vert s) = \arg\max_a Q(s,a)\), should
+hopefully be close to optimal. In deep RL, we model \(Q\) with a
+neural network \(\hat{Q}_\omega\). One way to facilitate exploration in this
+policy is to introduce uncertainty in the
+\(Q\)-value.
+\citet{fortunato_noisy_2019} introduced NoisyNet for exploration.
+These are networks with stochastic weights, where each weight \(w^{(l)}_{ij}\)
+has an added pertrubaition sampled from a noise distribution with standard deviation \(\sigma^{(l)}_{ij}\).
+After initializing \(\bm{w}\) and \(\bm{\sigma}\) such that the network has sufficient
+stochasticity for exploration, both parameters are learned using standard backpropagation.
+The approach is similar to variational inference schemes such as Bayes by backprop~\citep{blundell_weight_2015} where the weights of a neural network model are assumed to be normally distributed with mean
+\(\mu^{(l)}_{ij}\) and standard deviation \(\sigma^{(l)}_{ij}\). The objective of
+Bayes by backprop, however, is to approximate the posterior distribution
+\(p(\bm{w} \vert \mathcal{D})\) in a task with a fixed dataset \(\mathcal{D}\).
+The parameter distribution in NoisyNet does not necessarily
+converge to an approximate posterior. This means that it does not have the same
+guarantee on total regret as methods that approximate a posterior over the
+value functions~\citep{osband_generalization_2016}. They do, however, have
+experimental results which shows that the function does not always converge to
+a deterministic solution, but it is unclear why the network learns to introduce
+more noise into the network parameters.
 
-Nonlinear function approximators such as neural networks typically have an intractable
-posterior, so we cannot calculate the posterior analytically. Instead we use a posterior approximation
-\(q(\phi \vert \D_\omega^N) \approx P(\phi \vert \D_\omega^N)\), together with an algorithm
-for approximate inference. \citet{fellows_bayesian_2021} presents the Bayesian Bellman Actor-Critic
-using randomized priors \citep{osband_randomized_2018}, and show state of the art exploratory
-behaviour.
+\citet{fortunato_noisy_2019} apply NoisyNet to three reinforcement learning
+algorithms, DQN, Dueling DQN, and A3C, and show improved performance on all
+of them. Later NoisyNet was used in the Rainbow 
+algorithm~\citep{hessel_rainbow_2017}, a combination of six extensions to the
+DQN algorithms~\citep{fortunato_noisy_2019, bellemare_distributional_2017, wang_dueling_2016,van_hasselt_deep_2015,schaul_prioritized_2016,mnih_asynchronous_2016}, that shows state-of-the-art performance across 57 Atari games.
 
-For most approximate inference methods in deep learning, it is difficult to incorporate domain
-knowledge into the prior. Typically the prior distribution is defined on the parameters as \(P(\phi)\),
-while the knowledge exists in the function space \(P(a \vert s)\).
+%To properly adapt Bayesian inference to MDPs, \cite{fellows_bayesian_2021} define the Bayesian Bellman
+%operator (BBO), \(P_B(b \vert s, a, \omega)\), as the distribution over
+%Bellman functions such that for a noisy sample \(b_i \sim P_B(b \vert s,a,\omega)\),
+%\(b_i = \B[\hat{Q}_\omega](s_i, a_i) + \eta_i\). Then approximates this with a
+%distribution parameterized by \(\phi\) such that
+%\(P(b \vert s,a,\phi) \approx P(b \vert s,a,\omega)\).
+%\begin{equation}
+%    \B_{\omega, N}^\star(s,a) \defeq \E_{P(\phi \vert \D_\omega^N)} \left[ \hat{B}_\phi(s,a) \right].
+%\end{equation}
+%Here, \(\hat{B}_\phi(s,a) = \E_{P(b \mid s, a, \phi)}[b]\), is the conditional mean of
+%\(P(b \vert s, a, \phi)\), and the data \(\D_\omega^N\) is defined as the collection of
+%sampled \(Q\)-values, states and actions \(\D_\omega^N \defeq \{b_i, s_i, a_i\}_{i=1:N}\).
+%Under the assumption that each state \(s_i\) is drawn i.i.d from a distribution with
+%support over \(\state\), or from an ergodic Markov chain defined over a \(\sigma\)-algebra that is
+%countably generated from \(\state\) they find that \(\omega^\star\) such that
+%\(\hat{Q}_{\omega^\star} = \B^\star_{\omega^\star, N}\) can be found 
+%by minimising the mean squared Bayesian Bellman error (MSBBE):
+%\begin{equation}
+%    \mathrm{MSBBE}_N(\omega) \defeq \lVert \hat{Q}_{\omega} - \B^\star_{\omega, N} \lVert^2_{\rho, \pi},
+%\end{equation}
+%And that an unbiased estimate of \(\nabla_\omega \mathrm{MSBBE}_N(\omega)\) can be calculated
+%as long as we can sample from \(P(\phi \vert \D_\omega^N)\).
 
-Functional variational Bayesian neural networks \citep{sun_functional_2019} lets us define a prior on the
-\emph{function space}. In a Q-learning algorithm, this would be a function
-\(f : \state \times \action \rightarrow \R\). For now we generalize, and say that
-\(f : \mathcal{X} \rightarrow \mathcal{Y}\).
+%Nonlinear function approximators such as neural networks typically have an intractable
+%posterior, so we cannot calculate the posterior analytically. Instead we use a posterior approximation
+%\(q(\phi \vert \D_\omega^N) \approx P(\phi \vert \D_\omega^N)\), together with an algorithm
+%for approximate inference. \citet{fellows_bayesian_2021} presents the Bayesian Bellman Actor-Critic
+%using randomized priors \citep{osband_randomized_2018}, and show state of the art exploratory
+%behaviour.
+
+%For most approximate inference methods in deep learning, it is difficult to incorporate domain
+%knowledge into the prior. Typically the prior distribution is defined on the parameters as \(P(\phi)\),
+%while the knowledge exists in the function space \(P(a \vert s)\).
+%This is also the case for randomized priors.
+% We therefore want to
+
+In NoisyNet \citep{fortunato_noisy_2019}, the Q-function space can be seen
+as a stochastic process on the probability space \((\Omega, \mathcal{F}, P)\).
+The stochastic process can simply be written as
+\(\{Q(\bm{s}, \bm{a}) : (\bm{s}, \bm{a}) \in \state \times \action \}\). For
+any \(\omega \in \Omega\), \(Q(\cdot, \cdot, \omega)\) is a sample function
+mapping \(\state \times \action \rightarrow \mathbb{R}\). To simplify notation
+we will denote sample functions as \(f\). NoisyNet, specifically, is a stochastic
+process parameterized by its weights and their standard deviation. We will define
+this parameterized function as \(g_\phi\), and their sampling distribution as
+\(q_\phi \in \mathcal{Q}\). Given a noise vector \(\xi\), we have
+\(f(\bm{s}, \bm{a}) = g_\phi(\bm{a}, \bm{s}, \xi)\).
+
+Functional variational Bayesian neural networks \citep{sun_functional_2019} is 
+a variational inference method for neural networks that approximates the 
+posterior distribution in function space.
 \citet{sun_functional_2019} show that for two stochastic processes \(P\) and \(Q\):
@@
 
-The difficult part in \eqref{eq:fkl} is to estimate \(\nabla_\f \log q(\f^\X)\) and \(\nabla_\f \log p(\f^\X)\).
-To estimate these log-density gradients, they use a spectral Stein gradient estimator \citep{shi_spectral_2018}.
-Given enough function value samples, the spectral Stein gradient estimator can estimate score functions
-for both in-distribution and out-of-distribution samples. This means that we can use it to estimate
-both gradients. \(\nabla_\f \log q(\f^\X)\) is likely intractable intractable, considering \(q_\phi\) is
-a neural network with stochastic weights. Depending on how we define the prior, however, \(\nabla_\f \log p(\f^\X)\)
-can be easy to compute analytically. To reduce variance in the gradients we aim to define tractable priors.
+The difficult part in \eqref{eq:fkl} is to estimate \(\nabla_\f \log q(\f^\X)\)
+and \(\nabla_\f \log p(\f^\X)\). \(\nabla_\f \log q(\f^\X)\) is likely 
+intractable, considering \(q_\phi\) is a neural network with stochastic weights.
+Depending on how we define the prior, however, \(\nabla_\f \log p(\f^\X)\)
+can be easy to compute analytically. To reduce variance in the gradients we
+define tractable priors in this paper. To estimate the log-density gradient
+\(\nabla_\f \log q(\f^\X)\), they use a spectral Stein gradient estimator
+\citep{shi_spectral_2018}.
 
@@
 \section{Method}
-Instead of a prior on the parameter space, we would like to have a prior on the \(Q\)-function space.
-Using the functional variational neural network framework explored earlier, our maximization target
-becomes:
+% Motivation:
+% * Optimal regret
+% * Meaningful priors
+We will present a method that allows the following:
 
+\begin{itemize}
+    \item Optimal regret \textcolor{red}{TODO: define optimal regret}
+    \item Incorporate domain knowledge
+\end{itemize}
+
+\textcolor{red}{A natural step for finding
+the optimal sampling distribution \(q_\phi\) is to minimize the KL-divergence
+between it and the true Q-value function. This is different from the optimization
+scheme in NoisyNet, which only tries to maximize the likelihood that samples from
+\(q_\phi\) comes from the true Q-value function.} \textcolor{green}{This should probably go under method}
+
+We would like to approximate the posterior distribution of the Q value function.
+This would (1) give optimal regret, (2) let us incorporate domain knowledge
+through an appropriate prior distribution.
+We can use the functional variational bayesian neural
+network (FVBNN)~\citep{sun_functional_2019} framework discussed earlier.
+NoisyNet uses one sample from Q for each optimization step. We will instead use
+\(N\) samples
+from Q. This lets us add the KL-term from FVBNN to the loss function that
+encourages stochasticity.
+The maximization target becomes:
 \begin{equation}
@@
 \end{equation}
-To justify this we need to show that \(supp(c) = \state \times \action\).
-Under the same assumption about the distribution of each state \(s_i\) from BBO,
-\(supp(c) = \state \times \action\) follows trivially.
+%To justify this we need to show that \(supp(c) = \state \times \action\).
+%Under the same assumption about the distribution of each state \(s_i\) from BBO,
+%\(supp(c) = \state \times \action\) follows trivially.
 
 Since we are modeling \(q_\phi\) with a Bayesian neural network, and \(Q_\omega\) with a neural network,
-we have a bilevel optimization problem. To solve this, we employ a similar strategy to \cite{fellows_bayesian_2021},
+we have a bilevel optimization problem. To solve this, we employ a similar strategy to \citet{fellows_bayesian_2021},
 where we have a two-timescale gradient update. \(\phi\) and \(\omega\) are updated using stochastic
@@
 % define. We would like the prior to be of the form \(P(a \vert s)\).
+
+\begin{algorithm}
+\caption{NoisyNet RL}
+\begin{algorithmic}
+    \State \(\D \gets \emptyset\)
+    \State \(s \sim P_0\)
+    \State Initialize \(\phi, \omega\)
+    \While{not converged}
+        \State \(f \sim q_\phi\)
+        \State \(a \sim \arg\max_a f(s,a)\)
+        \State \(s' \sim P(\cdot \vert s,a)\)
+        \State \(r = r(s',a,s)\)
+        \State \(\D \gets \D \cup \{s,a,r,s'\}\)
+        \State \Call{UpdateNoisyNet}{$\phi, \omega, \D$}
+    \EndWhile
+    \Statex
+    \Function{UpdateNoisyNet}{$\phi, \omega, \D$}
+        \State \(T \sim \D\)
+        \State \(f \sim q_\phi\)
+        \State \(b \sim q_\omega\)
+        \State \(\Delta_\mathcal{L} \gets 0\)
+        \For{\(\{s,a,r,s'\} \in T\)}
+            \State \(\bm{q} \gets \max_a \f(s,a)\)
+            \State \(\mathcal{F} \gets \mathcal{F} \cup \f(s,a)\)
+            \State \(G \gets r + \gamma b(s,a)\)
+            \State \(\Delta_\mathcal{L} \gets \Delta_\mathcal{L} - \frac{1}{\lvert T \rvert} \nabla_\phi \log p(\bm{q} \vert \bm{G})\)
+        \EndFor
+        \State \(\phi \gets \phi + \eta_\phi \Delta_\mathcal{L}\)
+        \State \(\omega \gets \omega + \eta_\omega (\omega - \phi)\)
+    \EndFunction
+\end{algorithmic}
+\end{algorithm}
 
@@
     \Function{UpdatePosterior}{$\phi, \omega, \D$}
-        \While{not converged}
         \State \(T \sim \D\)
-            \State \(\f \gets \{f_i \sim q_\phi \text{ for } i=1,\dots,k\}\)
+        \State \(f \gets \{f_i \sim q_\phi \mid i=1,\dots,k\}\)
+        \State \(\mathbf{b} \gets \{b_i \sim q_\omega \mid i=1,\dots,k\}\)
         \State \(\mathcal{F} \gets \emptyset\)
@@
         \For{\(\{s,a,r,s'\} \in T\)}
-                \State \(\bm{\hat{a}} \gets \arg\max_a \f(s,a)\)
+            \State \(\bm{q} \gets \max_a \f(s,a)\)
             \State \(\mathcal{F} \gets \mathcal{F} \cup \f(s,a)\)
-                \State \(G \gets r + \gamma Q_\omega(s,a)\)
-                \State \(\Delta_\mathcal{L} \gets \Delta_\mathcal{L} - \frac{1}{k} \frac{1}{\lvert T \rvert} \nabla_\phi \log p(\bm{\hat{a}} \vert G)\)
+            \State \(\bm{G} \gets \{r + \gamma b_i(s,a) \mid i = 1, 
+        \dots, k\}\)
+            \State \(\Delta_\mathcal{L} \gets \Delta_\mathcal{L} - \frac{1}{\lvert T \rvert} \nabla_\phi \log p(\bm{q} \vert \bm{G})\)
         \EndFor
         \State \(\Delta_\KL \gets SSGE(p, \mathcal{F})\)
-            \State \(\phi \gets \phi + \eta_\phi (\Delta_\mathcal{L} - \Delta_\KL)\)
-            \State \(\hat{B}_\phi \gets \frac{1}{k}\frac{1}{\lvert T \rvert}\sum_{i=1}^k \sum_{b \in \mathcal{F}} b\)
-            \State \(\Delta_\omega \gets \sum_{\{s,a,r,s'\} \in T} \nabla_\omega \lVert \hat{B}_\phi(s,a) - Q_\omega(s,a) \rVert^2_2 \)
-            \State \(\omega \gets \omega - \eta_\omega \Delta_\omega\)
-        \EndWhile
+        \State \(\phi \gets \phi + \eta_\phi (\Delta_\mathcal{L} - \lambda \Delta_\KL)\)
+        \State \(\omega \gets \omega + \eta_\omega (\omega - \phi)\)
     \EndFunction
@@
 \end{algorithm}
+
+\section{Experiments}
+\subsection{Uninformative Prior}
+\subsection{Informative Prior}
+
+\section{Discussion}
 

### 2021-12-20 src/algorithms/common.jl

@@ -49,12 +49,33 @@ function (l::NoisyDense)(x, num_samples::Union{Int, Nothing}=nothing; rng::Union
     if num_samples === nothing
         ϵ = Zygote.@ignore randn!(rng, similar(μ, size(μ, 1), 1))
     else
-        ϵ = Zygote.@ignore randn!(rng, similar(μ, size(μ, 1), 1, num_samples))
+        ϵ_1 = Zygote.@ignore randn!(rng, similar(μ, size(μ, 1), 1, 1))
+        ϵ_2 = Zygote.@ignore randn!(rng, similar(μ, 1, 1, num_samples))
+        ϵ = ϵ_1 .* ϵ_2
     end
     μ = reshape(μ, size(μ, 1), size(x, 2), :)
     σ² = reshape(σ², size(μ, 1), size(x, 2), :)
     return y = l.f.(μ .+ ϵ .* sqrt.(σ²))
 end
+
+# function (l::NoisyDense)(x, num_samples::Union{Int, Nothing}=nothing; rng::Union{AbstractRNG, Nothing}=nothing)
+#     rng = rng === nothing ? l.rng : rng
+#     x = ndims(x) == 2 ? unsqueeze(x, 3) : x
+#     tmp_x = reshape(x, size(x, 1), :)
+#     μ = l.w_μ * tmp_x .+ l.b_μ
+#     wσ² = softplus.(l.w_ρ)
+#     bσ² = softplus.(l.w_ρ)
+#     if num_samples === nothing
+#         wϵ = Zygote.@ignore randn!(rng, similar(μ, size(μ, 1), size(μ, 2)))
+#         bϵ = Zygote.@ignore randn!(rng, similar(μ, size(μ, 1), 1))
+#     else
+#         wϵ = Zygote.@ignore randn!(rng, similar(μ, size(μ, 1), size(μ, 2), 100))
+#         bϵ = Zygote.@ignore randn!(rng, similar(μ, size(μ, 1), 1, 100))
+#     end
+#     μ = reshape(μ, size(μ, 1), size(x, 2), :)
+#     σ² = reshape(σ², size(μ, 1), size(x, 2), :)
+#     return y = l.f.(μ .+ ϵ .* sqrt.(σ²))
+# end
 
 struct NoisyConv{N, M, F, A, V} <: AbstractNoisy
     f::F
[…]

### 2022-01-04 scripts/RLExp_DUQNS_Atari.jl
TEMPORARY DEPLOY COMMIT

@@ -28,7 +28,7 @@ end
 
 function RL.Experiment(
     ::Val{:RLExp},
-    ::Val{:DUQN},
+    ::Val{:DUQNS},
     ::Val{:Atari},
     name;
     restore=nothing,
@@ -38,7 +38,7 @@ function RL.Experiment(
     SET UP LOGGING
     """
     lg = WandbLogger(project = "RLExp",
-                     name="DUQN_Atari($name)",
+                     name="DUQNS_Atari($name)",
                      config = Dict(
                         "B_lr" => 1e-4,
                         "Q_lr" => 1e-3,
@@ -61,7 +61,7 @@ function RL.Experiment(
                         "seed" => 1,
                      ),
     )
-    save_dir = datadir("sims", "DUQN", "Atari($name)", "$(now())")
+    save_dir = datadir("sims", "DUQNS", "Atari($name)", "$(now())")
 
     """
     SEEDS
@@ -99,7 +99,10 @@ function RL.Experiment(
             Conv((3, 3), 64 => 64, relu; stride = 1, pad = 1, init = initc),
             x -> reshape(x, :, size(x)[end]),
             NoisyDense(11 * 11 * 64, 512, relu; init_μ = init),
-            NoisyDense(512, N_ACTIONS; init_μ = init),
+            Split(
+                NoisyDense(512, N_ACTIONS; init_μ = init),
+                NoisyDense(512, N_ACTIONS; init_μ = init),
+            )
         ) |> gpu
 
         Q_model = Chain(
@@ -109,7 +112,10 @@ function RL.Experiment(
             Conv((3, 3), 64 => 64, relu; stride = 1, pad = 1, init = initc),
             x -> reshape(x, :, size(x)[end]),
             NoisyDense(11 * 11 * 64, 512, relu; init_μ = init),
-            NoisyDense(512, N_ACTIONS; init_μ = init),
+            Split(
+                NoisyDense(512, N_ACTIONS; init_μ = init),
+                NoisyDense(512, N_ACTIONS; init_μ = init),
+            )
         ) |> gpu
 
     else
@@ -126,7 +132,7 @@ function RL.Experiment(
 
     agent = Agent(
         policy = QBasedPolicy(
-            learner = DUQNLearner(
+            learner = DUQNSLearner(
                 B_approximator = NeuralNetworkApproximator(
                     model = B_model,
[…]

### 2022-01-04 src/RLExp.jl

@@ -6,6 +6,7 @@ export TotalOriginalRewardPerEpisode, TotalBatchOriginalRewardPerEpisode, CloseL
 export ResizeImage
 export get_screen
 export DUQNLearner, FlatPrior, GeneralPrior, GaussianPrior
+export DUQNSLearner
 export stop, CenteredRMSProp
 
 using ArcadeLearningEnvironment
@@ -31,5 +32,6 @@ include("algorithms/common.jl")
 include("algorithms/BDQN.jl")
 include("algorithms/GDQN.jl")
 include("algorithms/DUQN.jl")
+include("algorithms/DUQNS.jl")
 
 end

### 2022-01-06 papers/main.tex
TEMPORARY DEPLOY COMMIT

@@
 
-\title{Scalable and Parameter-Free Optimal Regret Reinforcement Learning}
+\title{Scalable and Parameter-Free Exploration in Deep Reinforcement Learning}
 
@@
 
-\section{Background}
+\section{Introduction}
 A reinforcement learning environement is modelled as a Markov decision process (MDP)
@@
 state \(s_{t+1} \sim P(\cdot \vert s_t, a_t)\). A scalar reward
-\(r_{t+1} = r(\cdot \vert s_{t+1}, s_t, a_t)\) is observed. As the agent and environement
+\(r_t = r(\cdot \vert s_t, a_t)\) is observed. As the agent and environement
 interact in a sequence of time steps, a history of observations
-\(\mathcal{H}_t = (s_0, a_0, s_1, r_1, a_1, s_2, r_2, \dots, s_t, r_t)\) is collected.
+\(\mathcal{H}_t = (s_0, a_0, r_0, s_1, a_1, r_1, \dots, s_t, a_t, r_t)\) is collected.
 The goal is to find a policy \(\pi^\star\), such that sampling actions
 \(a \sim \pi^*(\cdot \vert s)\) maximizes the expected accumulated and discounted future reward,
-\(J^\pi \defeq \E_\pi \left[ \sum_{t=1}^\infty \gamma^t r_t \right]\). An efficient
+\(J^\pi \defeq \E_\pi \left[ \sum_{t=0}^\infty \gamma^t r_t \right]\). An efficient
 agent must be able to learn from the data it collects, but since the data is
@@
 The regret of a policy is the difference in the expected reward obtained by
-following that policy, and the expected reward for an optimal policy.
+following that policy, and the expected reward of following an optimal policy.
 An learning algorithm's efficiency in exploration can be measured by its
@@
 regret bound that grows linearly with time. There are several optimal algorithms
-for this problem, but perhaps the simplest one is called Thompson sampling.
+for this problem, but perhaps the simplest one is Thompson sampling~\citep{thompson_likelihood_1933}.
 Thompson sampling approximates a posterior distribution of the expected reward
@@
 \(\B[Q^\pi](s_t,a_t) \defeq \E_{P(s_{t+1} \vert s_t, a_t)\pi(a_{t+1} \vert s_t)}
-\left[ r(s_{t+1}, s_t, a) + \gamma Q^\pi(s_{t+1}, a_{t+1}) \right]\). With the
+\left[ r(s_t, a) + \gamma Q^\pi(s_{t+1}, a_{t+1}) \right]\). With the
 \(Q\)-function we can define a policy that always picks the action with the 
-highest \(Q\)-value in any state. We can't find \(Q\) exactly, but with a good
-approximation this policy, \(\pi(a \vert s) = \arg\max_a Q(s,a)\), should
-hopefully be close to optimal. In deep RL, we model \(Q\) with a
+highest \(Q\)-value in any state. In deep RL, we model \(Q\) with a
 neural network \(\hat{Q}_\omega\). One way to facilitate exploration in this
 policy is to introduce uncertainty in the
-\(Q\)-value.
+\(Q\)-value function.
+
 \citet{fortunato_noisy_2019} introduced NoisyNet for exploration.
@@
 DQN algorithms~\citep{fortunato_noisy_2019, bellemare_distributional_2017, wang_dueling_2016,van_hasselt_deep_2015,schaul_prioritized_2016,mnih_asynchronous_2016}, that shows state-of-the-art performance across 57 Atari games.
+
+In this paper we will introduce an extension to NoisyNet that puts it into a Bayesian context.
+A limitation of NoisyNet is that the initial uncertainty in the Q-value function is crucial to exploration.
+If the uncertainty is too high, algorithm will struggle to learn anything, while if the uncertainty is too low, there is nothing incentivizing exploration, and the algorithm will likely be stuck in a poor local minimum.
+
+\section{Background}
 
@@
 \begin{itemize}
-    \item Optimal regret \textcolor{red}{TODO: define optimal regret}
+    \item Optimal regret
     \item Incorporate domain knowledge
+    \item Avoid hyperparameter optimization
 \end{itemize}
@@
 \section{Experiments}
+Since our method is essentially an extension of NoisyNet~\cite{fortunato_noisy_2019}, all experiments will compare the performance results of these two methods.
 \subsection{Uninformative Prior}
+First, it is interesting to see how our method will compare in environments without the advantage of prior knowledge.
+We hypothesize that the added KL-term will push the algorithm to keep exploring more than NoisyNet, and
+
+\begin{figure}
+    \includegraphics[width=\columnwidth]{Example_Figure_1}
+    \caption{Example figure 1}
+    \label{fig:fig_1}
+\end{figure}
+
 \subsection{Informative Prior}

### 2022-01-06 src/algorithms/common.jl

@@ -69,20 +69,20 @@ function (l::NoisyDense)(x, num_samples::Union{Int, Nothing}=nothing; rng::Union
 
     if num_samples === nothing
         tmp_x = reshape(x, size(x, 1), :)
-        wϵ = Zygote.@ignore randn!(rng, similar(x, size(wσ², 1), size(wσ², 2)))
-        bϵ = Zygote.@ignore randn!(rng, similar(x, size(bσ², 1), 1))
+        wϵ = Zygote.@ignore CUDA.randn!(rng, similar(x, size(wσ², 1), size(wσ², 2)))
+        bϵ = Zygote.@ignore CUDA.randn!(rng, similar(x, size(bσ², 1), 1))
 
         w = l.w_μ .+ wϵ .* wσ²
         b = l.b_μ .+ bϵ .* bσ²
         return y = l.f.(w * tmp_x .+ b)
     else
         tmp_x = x
-        wϵ_1 = Zygote.@ignore randn!(rng, similar(x, size(wσ², 1), 1, 1))
-        wϵ_2 = Zygote.@ignore randn!(rng, similar(x, 1, size(wσ², 2), 1))
-        wϵ_3 = Zygote.@ignore randn!(rng, similar(x, 1, 1, num_samples))
-        wϵ = Zygote.@ignore wϵ_1 .* wϵ_2 .* wϵ_2
-        bϵ_1 = Zygote.@ignore randn!(rng, similar(x, size(bσ², 1), 1, 1))
-        bϵ_2 = Zygote.@ignore randn!(rng, similar(x, 1, 1, num_samples))
+        wϵ_1 = Zygote.@ignore CUDA.randn!(rng, similar(x, size(wσ², 1), 1, 1))
+        wϵ_2 = Zygote.@ignore CUDA.randn!(rng, similar(x, 1, size(wσ², 2), num_samples))
+        # wϵ_3 = Zygote.@ignore randn!(rng, similar(x, 1, 1, num_samples))
+        wϵ = Zygote.@ignore wϵ_1 .* wϵ_2 #.* wϵ_2
+        bϵ_1 = Zygote.@ignore CUDA.randn!(rng, similar(x, size(bσ², 1), 1, 1))
+        bϵ_2 = Zygote.@ignore CUDA.randn!(rng, similar(x, 1, 1, num_samples))
         bϵ = Zygote.@ignore bϵ_1 .* bϵ_2
 
         w = l.w_μ .+ wϵ .* wσ²

### 2022-01-07 papers/main.tex
TEMPORARY DEPLOY COMMIT

@@
 scheme in NoisyNet, which only tries to maximize the likelihood that samples from
-\(q_\phi\) comes from the true Q-value function.} \textcolor{green}{This should probably go under method}
+\(q_\phi\) comes from the true Q-value function.}
 
-We would like to approximate the posterior distribution of the Q value function.
+We would like to approximate the posterior distribution of the Q-value function.
 This would (1) give optimal regret, (2) let us incorporate domain knowledge
@@
 \subsection{Informative Prior}
+We will also look at how our method can utilize domain knowledge to improve sample efficiency. We will use the following method to calculate the prior distribution on the Q-values:
+
+\textcolor{red}{Discuss how to go from policy prior to Q-value prior.}
+
+\begin{figure}
+    \includegraphics[width=\columnwidth]{example-image}
+    \caption{Performance on the CartPole-v1 environment.}
+\end{figure}
 

### 2022-01-07 scripts/RLExp_DUQNS_Atari.jl

@@ -49,7 +49,7 @@ function RL.Experiment(
                         "gamma" => 0.99,
                         "update_horizon" => 1,
                         "batch_size" => 32,
-                        "min_replay_history" => 100,
+                        "min_replay_history" => 50000,
                         "updates_per_step" => 1,
                         "λ" => 1,
                         "prior" => "GaussianPrior(0, 10)",
@@ -90,18 +90,19 @@ function RL.Experiment(
     """
     initc = glorot_uniform(rng)
     init(a, b) = (2 .* rand(a, b) .- 1) .* √(3 / a)
+    init_σ(dims) = fill(0.5f0, dims)
 
     if restore === nothing
         B_model = Chain(
             x -> x ./ 255,
-            Conv((8, 8), N_FRAMES => 32, relu; stride = 4, pad = 2, init = initc),
-            Conv((4, 4), 32 => 64, relu; stride = 2, pad = 2, init = initc),
-            Conv((3, 3), 64 => 64, relu; stride = 1, pad = 1, init = initc),
+            Conv((8, 8), N_FRAMES => 32, relu; stride = 4, pad = 2, init = initc, init_σ = init_σ),
+            Conv((4, 4), 32 => 64, relu; stride = 2, pad = 2, init = initc, init_σ = init_σ),
+            Conv((3, 3), 64 => 64, relu; stride = 1, pad = 1, init = initc, init_σ = init_σ),
             x -> reshape(x, :, size(x)[end]),
-            NoisyDense(11 * 11 * 64, 512, relu; init_μ = init),
+            NoisyDense(11 * 11 * 64, 512, relu; init_μ = init, init_σ = init_σ),
             Split(
-                NoisyDense(512, N_ACTIONS; init_μ = init),
-                NoisyDense(512, N_ACTIONS; init_μ = init),
+                NoisyDense(512, N_ACTIONS; init_μ = init, init_σ = init_σ),
+                NoisyDense(512, N_ACTIONS; init_μ = init, init_σ = init_σ),
             )
         ) |> gpu
 

### 2022-01-10 papers/main.tex
TEMPORARY DEPLOY COMMIT

@@
 \(q_\phi \in \mathcal{Q}\). Given a noise vector \(\xi\), we have
-\(f(\bm{s}, \bm{a}) = g_\phi(\bm{a}, \bm{s}, \xi)\).
+\(f(\bm{s}, \bm{a}) = g_\phi(\bm{a}, \bm{s}, \xi)\). This means that NoisyNet
+gives a new policy function for each noise vector \(\xi\).
 
@@
 
-\textcolor{red}{A natural step for finding
-the optimal sampling distribution \(q_\phi\) is to minimize the KL-divergence
-between it and the true Q-value function. This is different from the optimization
-scheme in NoisyNet, which only tries to maximize the likelihood that samples from
-\(q_\phi\) comes from the true Q-value function.}
+% A natural step for finding
+% the optimal sampling distribution \(q_\phi\) is to minimize the KL-divergence
+% between it and the true Q-value function. This is different from the optimization
+% scheme in NoisyNet, which only tries to maximize the likelihood that samples from
+% \(q_\phi\) comes from the true Q-value function.
 

### 2022-01-10 scripts/RLExp_DUQNS_Atari.jl

@@ -49,7 +49,7 @@ function RL.Experiment(
                         "gamma" => 0.99,
                         "update_horizon" => 1,
                         "batch_size" => 32,
-                        "min_replay_history" => 100,
+                        "min_replay_history" => 50_000,
                         "updates_per_step" => 1,
                         "λ" => 1,
                         "prior" => "GaussianPrior(0, 10)",

### 2022-01-10 src/algorithms/common.jl

@@ -50,10 +50,10 @@ function (l::NoisyDense)(x, num_samples::Union{Int, Nothing}=nothing; rng::Union
     if num_samples === nothing
         ϵ = Zygote.@ignore randn!(rng, similar(μ, size(μ, 1), 1))
     else
-        # ϵ_1 = Zygote.@ignore randn!(rng, similar(μ, size(μ, 1), 1, 1))
-        # ϵ_2 = Zygote.@ignore randn!(rng, similar(μ, 1, 1, num_samples))
-        # ϵ = Zygote.@ignore ϵ_1 .* ϵ_2
-        ϵ = Zygote.@ignore randn!(rng, similar(μ, size(μ, 1), 1, num_samples))
+        ϵ_1 = Zygote.@ignore randn!(rng, similar(μ, size(μ, 1), 1, 1))
+        ϵ_2 = Zygote.@ignore randn!(rng, similar(μ, 1, 1, num_samples))
+        ϵ = Zygote.@ignore ϵ_1 .* ϵ_2
+        # ϵ = Zygote.@ignore randn!(rng, similar(μ, size(μ, 1), 1, num_samples))
     end
     μ = reshape(μ, size(μ, 1), size(x, 2), :)
     σ² = reshape(σ², size(μ, 1), size(x, 2), :)
@@ -256,6 +256,7 @@ function compute_gradients(
 )
     M = size(xm, 1)
     Kxx, dKxx, _ = grad_gram(xm, xm, lengthscale)
+    Kxx .+= 0.01f0 .* I
 
     if typeof(x) <: CuArray
         Kxx = cpu(Kxx)

### 2022-01-10 papers/main.tex
TEMPORARY DEPLOY COMMIT

@@
 
+\subsection{Noisy Networks}
 In NoisyNet \citep{fortunato_noisy_2019}, the Q-function space can be seen
@@
 \(f(\bm{s}, \bm{a}) = g_\phi(\bm{a}, \bm{s}, \xi)\). This means that NoisyNet
-gives a new policy function for each noise vector \(\xi\).
+gives a new policy function for each noise vector \(\xi\). Although this means
+that NoisyNet can model stochastic policies, \citet{fortunato_noisy_2019} point
+out that for the loss function it is optimising, there always exsit a deterministic
+optimal policy. They show through emipirical analysis, however, that this does not
+mean that the policy necessarily disregards the noise and converges to a deterministic
+policy.
 
+\subsection{Functional Variational Bayesian Neural Networks}
+There are several ways of approximating the posterior distribution of the weights
+in a neural network with respect to a prior and a dataset. Typically, a static dataset
+\(\D\)
 Functional variational Bayesian neural networks \citep{sun_functional_2019} is 

### 2022-01-10 papers/main.tex
TEMPORARY DEPLOY COMMIT

@@
 There are several ways of approximating the posterior distribution of the weights
-in a neural network with respect to a prior and a dataset. Typically, a static dataset
-\(\D\)
+in a neural network with respect to a prior and a dataset. Typically, the dataset
+\(\D\) is static and with datapoints \(\bm{x}\) and labels \(\bm{y}\), and the 
+prior is defined as a distribution over the weights
+\(p(\bm{w})\)~\citep{rezende_stochastic_2014,blundell_weight_2015,ritter_scalable_2018,maddox_simple_2019}.
+
 Functional variational Bayesian neural networks \citep{sun_functional_2019} is 

### 2022-01-10 scripts/RLExp_DUQNS_Atari.jl

@@ -90,7 +90,7 @@ function RL.Experiment(
     """
     initc = glorot_uniform(rng)
     init(a, b) = (2 .* rand(a, b) .- 1) .* √(3 / a)
-    init_σ(dims...) = fill(0.005f0, dims)
+    init_σ(dims...) = fill(0.0005f0, dims)
 
     if restore === nothing
         B_model = Chain(

### 2022-01-10 src/algorithms/common.jl

@@ -50,10 +50,10 @@ function (l::NoisyDense)(x, num_samples::Union{Int, Nothing}=nothing; rng::Union
     if num_samples === nothing
         ϵ = Zygote.@ignore randn!(rng, similar(μ, size(μ, 1), 1))
     else
-        ϵ_1 = Zygote.@ignore randn!(rng, similar(μ, size(μ, 1), 1, 1))
-        ϵ_2 = Zygote.@ignore randn!(rng, similar(μ, 1, 1, num_samples))
-        ϵ = Zygote.@ignore ϵ_1 .* ϵ_2
-        # ϵ = Zygote.@ignore randn!(rng, similar(μ, size(μ, 1), 1, num_samples))
+        # ϵ_1 = Zygote.@ignore randn!(rng, similar(μ, size(μ, 1), 1, 1))
+        # ϵ_2 = Zygote.@ignore randn!(rng, similar(μ, 1, 1, num_samples))
+        # ϵ = Zygote.@ignore ϵ_1 .* ϵ_2
+        ϵ = Zygote.@ignore randn!(rng, similar(μ, size(μ, 1), 1, num_samples))
     end
     μ = reshape(μ, size(μ, 1), size(x, 2), :)
     σ² = reshape(σ², size(μ, 1), size(x, 2), :)

### 2022-01-11 papers/main.tex
TEMPORARY DEPLOY COMMIT

@@
 \(p(\bm{w})\)~\citep{rezende_stochastic_2014,blundell_weight_2015,ritter_scalable_2018,maddox_simple_2019}.
+By defining a prior over the weights, they can use approximate variational inference
+methods to approximate \(p(\bm{w} \vert \D) = \frac{p(\D \vert \bm{w})p(\bm{w})}{p(\D)}\).
+The disadvantage of this is that \(p(\bm{w})\) only acts as a regularizer, and cannot be
+used to incorporate actual prior knowledge. Any prior knowledge we might have about the
+function we are finding would be very difficult to translate into a prior distribution
+in the weight space.
 
@@
 a variational inference method for neural networks that approximates the 
-posterior distribution in function space.
+posterior distribution in function space. This means that our prior will be a distribution
+over functions, also known as a stochastic process.
 \citet{sun_functional_2019} show that for two stochastic processes \(P\) and \(Q\):

### 2022-01-11 papers/main.tex
TEMPORARY DEPLOY COMMIT

--- 2022-01-10 papers/main.tex
@@
 \(p(\bm{w})\)~\citep{rezende_stochastic_2014,blundell_weight_2015,ritter_scalable_2018,maddox_simple_2019}.
+By defining a prior over the weights, they can use approximate variational inference
+methods to approximate \(p(\bm{w} \vert \D) = \frac{p(\D \vert \bm{w})p(\bm{w})}{p(\D)}\).
+The disadvantage of this is that \(p(\bm{w})\) only acts as a regularizer, and is not
+used to incorporate prior knowledge. Any prior knowledge we might have about the optimizer
+function would be very difficult to translate into a prior distribution in the weight space.
 
@@
 \begin{equation}
-    \KL[P \Vert Q] = \sup_{n \in \N, \X \in \mathcal{X}^n} \KL \left[ P_\X \Vert Q_\X \right],
+    \KL[Q \Vert P] = \sup_{n \in \N, \X \in \mathcal{X}^n} \KL \left[ Q_\X \Vert P_\X \right],
 \end{equation}

### 2022-01-11 scripts/RLExp_DUQNS_Atari.jl

@@ -40,7 +40,7 @@ function RL.Experiment(
     lg = WandbLogger(project = "RLExp",
                      name="DUQNS_Atari($name)",
                      config = Dict(
-                        "B_lr" => 1e-4,
+                        "B_lr" => 1e-5,
                         "Q_lr" => 1,
                         "B_clip_norm" => 10.0,
                         "B_update_freq" => 4,

### 2022-01-12 papers/main.tex
TEMPORARY DEPLOY COMMIT

@@
 over functions, also known as a stochastic process.
-\citet{sun_functional_2019} show that for two stochastic processes \(P\) and \(Q\):
+\citet{sun_functional_2019} show that for two stochastic processes \(P\) and \(Q\), the
+KL-divergence from \(Q\) to \(P\) is the supremum of the marginal KL-divergences over
+all finite measurement sets. Let \(P_\X\) be the marginal distribution of function values
+at \(\X \in \mathcal{X}^n\), then:
 
@@
 
-where \(\X \in \mathcal{X}^n\) is a finite measurement set and \(P_\X, Q_\X\) are the marginal distributions
-at \(\X\). They further show that if \(\f^\X\) are the function values at points \(\X\), then
+Now the stochastic processes are a neural network \(q_\phi\) and a prior \(p\). In a similar
+manner to NoisyNet, we sample a function \(f\) from \(q\) by sampling a random noise vector
+\(\xi\), and then defining \(f(\bm{x}) = g_\phi(\bm{x}, \xi)\). They further show that the
+gradient of the KL-divergence for functions evaluated at the measurement set \(\X\) is
 
 \begin{multline}\label{eq:fkl}
-    \nabla_\phi \KL[q_\phi(\f^X) \Vert p(\f^\X)] \\
-    = \E \left[ \nabla_\phi \f^\X( \nabla_\f \log q(\f^\X) - \nabla_\f \log p(\f^\X)) \right].
+    \nabla_\phi \KL[q_\phi(\f^\X) \Vert p(\f^\X)] = \E_q \left[ \nabla_\phi \log q_\phi (\f^\X) \right]\\
+    + \E_\xi \left[ \nabla_\phi \f^\X( \nabla_\f \log q(\f^\X) - \nabla_\f \log p(\f^\X)) \right].
 \end{multline}
+
+The measurement set \(\X\) is created by concatenating the training points \(\X^D\) and a
+set of \(M\) points \(\X^M\) drawn from some distribution \(c\) that has full support
+in the space of interesting test cases.
 
@@
 % * Meaningful priors
-We will present a method that allows the following:
+We will present a method based on functional variational Bayesian neural
+networks~\citep{sun_functional_2019} that allows the following:
 
 \begin{itemize}
-    \item Optimal regret
+    \item Near-optimal regret
     \item Incorporate domain knowledge
@@
 We would like to approximate the posterior distribution of the Q-value function.
-This would (1) give optimal regret, (2) let us incorporate domain knowledge
+This would (1) give near-optimal regret, (2) let us incorporate domain knowledge
 through an appropriate prior distribution.

### 2022-01-12 scripts/RLExp_DUQNS_Atari.jl

@@ -40,7 +40,7 @@ function RL.Experiment(
     lg = WandbLogger(project = "RLExp",
                      name="DUQNS_Atari($name)",
                      config = Dict(
-                        "B_lr" => 1e-5,
+                        "B_lr" => 1e-4,
                         "Q_lr" => 1,
                         "B_clip_norm" => 10.0,
                         "B_update_freq" => 4,
@@ -56,7 +56,7 @@ function RL.Experiment(
                         "n_samples" => 100,
                         "η" => 0.01,
                         "nev" => 20,
-                        "is_enable_double_DQN" => true,
+                        "is_enable_double_DQN" => false,
                         "traj_capacity" => 1_000_000,
                         "seed" => 1,
                      ),

### 2022-01-12 papers/main.tex
TEMPORARY DEPLOY COMMIT

@@
 \begin{itemize}
-    \item Near-optimal regret
+    \item Efficient exploration
     \item Incorporate domain knowledge
@@
 We would like to approximate the posterior distribution of the Q-value function.
-This would (1) give near-optimal regret, (2) let us incorporate domain knowledge
-through an appropriate prior distribution.
+\citet{osband_why_2017} proove that in finite horizon MDPs posterior sampling for
+reinforcement learning has at least a near-optimal regret bound. They further conjecture
+that this cound can be further improved to show an optimal regret bound. Additionally,
+a posterior sampling based reinfrocement learning algorithm could be made to utilize
+prior information or domain knowledge through an appropriate prior. This should improve
+policy convergence rate.
+Combined with the computational efficiency of posterior sampling, this motivates the
+development of a Bayesian reinforcement learning algorithm with functional priors.
+
 We can use the functional variational bayesian neural
@@
 NoisyNet uses one sample from Q for each optimization step. We will instead use
-\(N\) samples
-from Q. This lets us add the KL-term from FVBNN to the loss function that
+\(N\) samples from Q. This lets us add the KL-term from FVBNN to the loss function that
 encourages stochasticity.
@@
 \begin{equation}
-    \log p(\D_\omega^N \vert f) - \KL \left[ q(\f^{\D_\omega^N}, \f^M) \Vert p(\f^{\D_\omega^N}, \f^M) \right],
+    \log p(\D_\omega^N \vert f) - \KL \left[ q(\f^{\D_\omega^N}, \f^\mathbf{M}) \Vert p(\f^{\D_\omega^N}, \f^\mathbf{M}) \right],
 \end{equation}
-where \(\f^{\D_\omega^N}\) is \(f\) applied to the dataset \(\D_\omega^N\), and \(\f^M\) is \(f\) applied to
-a set of i.i.d. random points \(M = \{m_i \sim c \mid i=1,\dots,k\} \subseteq \state \times \action\)
-with full support. We will let
+where \(\f^{\D_\omega^N}\) is \(f\) applied to the dataset \(\D_\omega^N\), and \(\f^\mathbf{M}\) is \(f\) applied to
+a set of i.i.d. random points \(\mathbf{M} = \{m_i \sim c \mid i=1,\dots,k\} \subseteq \state \times \action\)
+with full support. We will let the measurement \(\mathbf{M}\) be the the set of all state-action
+pairs for states we have already explored. If the MDP is ergodic, then \(\textbf{M}\) will eventually
+have full support in \(\state \times \action\).
 
 \begin{equation}
-    M = \{(s_i, a_j) \; \forall s_i \in \D_\omega^N,\, \forall a_j \in \action\}. 
+    \mathbf{M} = \{(s_i, a_j) \; \forall s_i \in \D_\omega^N,\, \forall a_j \in \action\}. 
 \end{equation}
+
 %To justify this we need to show that \(supp(c) = \state \times \action\).
@@
 
-Since we are modeling \(q_\phi\) with a Bayesian neural network, and \(Q_\omega\) with a neural network,
-we have a bilevel optimization problem. To solve this, we employ a similar strategy to \citet{fellows_bayesian_2021},
-where we have a two-timescale gradient update. \(\phi\) and \(\omega\) are updated using stochastic
-gradient descent at different timescales to ensure stable convergence.
+% Since we are modeling \(q_\phi\) with a Bayesian neural network, and \(Q_\omega\) with a neural network,
+% we have a bilevel optimization problem. To solve this, we employ a similar strategy to \citet{fellows_bayesian_2021},
+% where we have a two-timescale gradient update. \(\phi\) and \(\omega\) are updated using stochastic
+% gradient descent at different timescales to ensure stable convergence.
 
@@
 \section{Experiments}
-Since our method is essentially an extension of NoisyNet~\cite{fortunato_noisy_2019}, all experiments will compare the performance results of these two methods.
+Our method most closely resembles that of NoisyNet~\cite{fortunato_noisy_2019}, so
+all experiments will mainly compare the performance of these two methods.
 \subsection{Uninformative Prior}
-First, it is interesting to see how our method will compare in environments without the advantage of prior knowledge.
-We hypothesize that the added KL-term will push the algorithm to keep exploring more than NoisyNet, and
+First, it is interesting to see how our method will compare to NoisyNet
+in environments without the advantage of prior knowledge.
+We hypothesize that the added KL-term will push the algorithm to keep exploring unexplored
+state-action pairs more than NoisyNet, thus
 
@@
 \subsection{Informative Prior}
-We will also look at how our method can utilize domain knowledge to improve sample efficiency. We will use the following method to calculate the prior distribution on the Q-values:
+One of the benefits of a functional prior is that we can incorporate domain knowledge to
+get more efficient exploration. We will now look at how our method can utilize domain
+knowledge to improve sample efficiency.
 
-\textcolor{red}{Discuss how to go from policy prior to Q-value prior.}
+% We will use the following method to calculate the prior distribution on the Q-values:
+
+% \textcolor{red}{Discuss how to go from policy prior to Q-value prior.}
 
@@
 \section{Discussion}
+
+\section{Conclusion}
 

### 2022-01-20 scripts/RLExp_DUQNS_Atari.jl
TEMPORARY DEPLOY COMMIT

@@ -42,9 +42,9 @@ function RL.Experiment(
                      config = Dict(
                         "B_lr" => 1e-4,
                         "Q_lr" => 1,
-                        "B_clip_norm" => 40.0,
-                        "B_update_freq" => 1,
-                        "Q_update_freq" => 1_000,
+                        "B_clip_norm" => 1000,
+                        "B_update_freq" => 4,
+                        "Q_update_freq" => 40_000,
                         "B_opt" => "ADAM",
                         "gamma" => 0.99,
                         "update_horizon" => 1,
@@ -58,7 +58,7 @@ function RL.Experiment(
                         "η" => 0.01,
                         "nev" => 20,
                         "is_enable_double_DQN" => true,
-                        "traj_capacity" => 100_000,
+                        "traj_capacity" => 1_000_000,
                         "seed" => 1,
                      ),
     )
@@ -91,8 +91,7 @@ function RL.Experiment(
     """
     initc = glorot_uniform(rng)
     init(a, b) = (2 .* rand(a, b) .- 1) ./ sqrt(b)
-    # init_σ(dims...) = fill(0.005f0, dims)
-    init_σ(dims...) = fill(0.1f0 / Float32(sqrt(dims[end])), dims)
+    init_σ(dims...) = fill(0.4f0 / Float32(sqrt(dims[end])), dims)
 
     if restore === nothing
         B_model = Chain(
@@ -269,7 +268,7 @@ function RL.Experiment(
         end,
         CloseLogger(lg),
     )
-    stop_condition = StopAfterStep(1_000_000, is_show_progress=true)
+    stop_condition = StopAfterStep(50_000_000, is_show_progress=true)
 
     """
     RETURN EXPERIMENT

### 2022-01-20 src/algorithms/common.jl

@@ -81,7 +81,7 @@ end
 #     end
 #     noisy_x = x .* ϵ_2
 #     noisy_x = reshape(noisy_x, size(noisy_x, 1), :)
-#     σ² = softplus.(l.w_ρ) * noisy_x .+ softplus.(l.b_ρ)
+#     σ² = l.w_ρ * noisy_x .+ l.b_ρ
 
 #     σ² = reshape(σ², size(σ²,1), size(x, 2), :) .* ϵ_1
 

### 2022-01-21 papers/main.tex
TEMPORARY DEPLOY COMMIT

@@
 \usepackage{bm}
+\usepackage{subcaption}
 
@@
 
-\title{Scalable and Parameter-Free Exploration in Deep Reinforcement Learning}
+\title{Parameter-Free Exploration in Deep Reinforcement Learning}
 
@@
 from the posterior distribution, and selecting the action that gave the highest
-reward. Bayesian methods been also been shown to behave efficiently with respect
+reward. Bayesian methods has also been shown to behave efficiently with respect
 to cumulative regret \cite{osband_generalization_2016} on general MDPs.
@@
 \(a\) in state \(s\) and then following policy \(\pi\) thereafter:
-\(Q^\pi \defeq \E_\pi \left[ \sum_{t=0}^\infty \gamma^t r_t \vert s_0=S, a_0=A \right]\).
+\(Q^\pi(s_0, a_0) \defeq \E_\pi \left[ \sum_{t=0}^\infty \gamma^t r_t \vert s_0=S, a_0=A \right]\).
 The Bellman operator on \(Q^\pi\) is defined as
@@
 We would like to approximate the posterior distribution of the Q-value function.
-\citet{osband_why_2017} proove that in finite horizon MDPs posterior sampling for
+\citet{osband_why_2017} prove that in finite horizon MDPs posterior sampling for
 reinforcement learning has at least a near-optimal regret bound. They further conjecture
@@
 NoisyNet uses one sample from Q for each optimization step. We will instead use
-\(N\) samples from Q. This lets us add the KL-term from FVBNN to the loss function that
+\(k\) samples from Q. This lets us add the KL-term from FVBNN to the loss function that
 encourages stochasticity.
@@
         \State \(T \sim \D\)
-        \State \(f \gets \{f_i \sim q_\phi \mid i=1,\dots,k\}\)
+        \State \(\f \gets \{f_i \sim q_\phi \mid i=1,\dots,k\}\)
         \State \(\mathbf{b} \gets \{b_i \sim q_\omega \mid i=1,\dots,k\}\)
@@
         \State \(\Delta_\mathcal{L} \gets 0\)
+        \State \(S \gets 0\)
         \For{\(\{s,a,r,s'\} \in T\)}
-            \State \(\bm{q} \gets \max_a \f(s,a)\)
+            \State \(\bm{q_\mu}, \bm{q_\sigma} \gets \max_a \f(s,a)\)
             \State \(\mathcal{F} \gets \mathcal{F} \cup \f(s,a)\)
@@
         \dots, k\}\)
-            \State \(\Delta_\mathcal{L} \gets \Delta_\mathcal{L} - \frac{1}{\lvert T \rvert} \nabla_\phi \log p(\bm{q} \vert \bm{G})\)
+            \State \(S \gets S + \frac{1}{k}p(\bm{q} \vert s, a)\)
+            \State \(\Delta_\mathcal{L} \gets \Delta_\mathcal{L} - \frac{1}{\lvert k \rvert} \nabla_\phi \log p(\bm{q_\mu} \vert \bm{G}, \bm{q_\sigma})\)
         \EndFor
-        \State \(\Delta_\KL \gets SSGE(p, \mathcal{F})\)
-        \State \(\phi \gets \phi + \eta_\phi (\Delta_\mathcal{L} - \lambda \Delta_\KL)\)
+        \State \(\Delta_\KL \gets S - SSGE(\mathcal{F})\)
+        \State \(\phi \gets \phi + \eta_\phi (\Delta_\mathcal{L} - \Delta_\KL)\)
         \State \(\omega \gets \omega + \eta_\omega (\omega - \phi)\)
@@
 \begin{figure}
-    \includegraphics[width=\columnwidth]{Example_Figure_1}
+    \centering
+    \begin{subfigure}[b]{0.45\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{charts/Cartpole_score}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{charts/MountainCar_score}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{charts/Cartpole_score}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{charts/MountainCar_score}
+    \end{subfigure}
     \caption{Example figure 1}
@@
 \begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{example-image}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{example-image}
+    \end{subfigure}
     \includegraphics[width=\columnwidth]{example-image}

### 2022-01-21 scripts/run_experiment.jl

@@ -16,14 +16,15 @@ addprocs_slurm(n_workers; topology = :master_worker, exeflags=["--project=.", "-
 @everywhere using DrWatson
 @everywhere @quickactivate :RLExp
 # include("RLExp_DUQN_Atari.jl")
-include("RLExp_DUQNS_Atari.jl")
+# include("RLExp_DUQNS_Atari.jl")
+include("RLExp_Noisy_Atari.jl")
 # include("RLExp_GDQN_Atari.jl")
 # include("Dopamine_DQN_Atari.jl")
 # include("RLExp_NDQN_Atari.jl")
 
 # games = ["breakout"]
 # experiments = [E`RLExp_BDQN_Atari($(game))` for game in games]
-experiments = [E`RLExp_DUQNS_Atari(pong)`]
+experiments = [E`RLExp_Noisy_Atari(pong)`]
 # experiments = [E`Dopamine_DQN_Atari(pong)`]
 
 # pmap(run, experiments)

### 2022-01-27 papers/main.tex
TEMPORARY DEPLOY COMMIT

@@
 
-\title{Parameter-Free Exploration in Deep Reinforcement Learning}
+\title{Bayesian Exploration in Deep Reinforcement Learning}
 
@@
 
+The first term is just the expected value of the score function, which is zero.
 The difficult part in \eqref{eq:fkl} is to estimate \(\nabla_\f \log q(\f^\X)\)
@@
 define tractable priors in this paper. To estimate the log-density gradient
-\(\nabla_\f \log q(\f^\X)\), they use a spectral Stein gradient estimator
-\citep{shi_spectral_2018}.
+\(\nabla_\f \log q(\f^\X)\), they use the Spectral Stein Gradient Estimator (SSGE)
+\citep{shi_spectral_2018}. In short, this is a method for estimating the gradient
+function of implicit distributions using approximations to eigenfunctions of a 
+kernel based operator. We bring three hyperparameters into the algorithm from this
+method, the number of samples \(k\) from the implicit distribution used to approximate
+the gradient, the number of eigenvectors \(J\) used to approximate the gradient, and
+\(\eta\), a regularization parameter that smooths the gradient function.
+
+The full minimization target for the functional Bayesian neural network becomes
+\begin{multline}
+    {\frac{1}{\lvert \D_s \rvert}} \sum_{()\bm{x}, y) \in D_s} \E_{q_\phi}
+    \left[ p(y \vert f(\bm{x})) \right]\\ - \lambda \KL
+    \left[ q(\f^{\D_s}, \f^\mathbf{M}) \Vert p(\f^{\D_s}, \f^\mathbf{M}) \right].
+\end{multline}
+
+In order for this to match the functional ELBO and be a proper lower bound
+for \(\log p(\D)\), \(\lambda\) should be set as \(\frac{1}{\lvert \D \rvert}\).
+\cite{sun_functional_2019} note, however, that the minimization target is only a lower
+bound for \(\KL \left[ \lvert q(f) \Vert p(f) \right]\), so a larger
+value for \(\lambda\) is likely necessary to prevent overfitting. They use,
+\(\lambda = \frac{1}{\lvert D_s \rvert}\), a value of one over the batch size instead.
+This means that the minimization target becomes a proper lower bound of \(\log p(\D_s)\).
 
@@
 \begin{equation}
-    \log p(\D_\omega^N \vert f) - \KL \left[ q(\f^{\D_\omega^N}, \f^\mathbf{M}) \Vert p(\f^{\D_\omega^N}, \f^\mathbf{M}) \right],
+    \log p(\D_\omega^N \vert f) - \lambda \KL \left[ q(\f^{\D_\omega^N}, \f^\mathbf{M}) \Vert p(\f^{\D_\omega^N}, \f^\mathbf{M}) \right],
 \end{equation}
@@
 \end{equation}
+
+To calculate \(\log p(\D_\omega^N \vert f)\) we assume that the observation noise is sampled
+from a Gaussian distribution. We then model the network to produce two output vectors,
+\(\mu\) and \(\rho = \log \sigma\). This gives the following loss function:
+
+\begin{equation}
+    \mathcal{L} = \frac{1}{\lvert \D_s \rvert}\sum_{i=1}^{\lvert \D_s \rvert} \rho_i + \left( \mu_i - q_i \right)^2
+    \exp (-\rho_i) + \lambda \KL[q \Vert p].
+\end{equation}
+
+We take inspiration from \cite{sun_functional_2019} and let \(\lambda\) be one over
+the batch size, \(\frac{1}{\lvert \D_s \rvert}\).
 
@@
 all experiments will mainly compare the performance of these two methods.
+
+\subsection{Details and Hyperparameters}
+We compare our method with NoisyNet~\citep{fortunato_noisy_2019} on four different
+environments in the OpenAI Gym~\citep{brockman_openai_2016-2}. The hyperparameters
+are the same as those described in \cite{han_nrowan-dqn_2020}. Our method additionally
+has hyperparameters related to the functional KL-divergence. These are shown in
+Table~\ref{tab:hyperparams}.
+
+\begin{table}
+    \centering
+    \caption{Hyperparameters for LFM.}\label{tab:hyperparams}
+    \begin{tabular}{rl}
+      \toprule % from booktabs package
+      Hyperparameter & Value \\
+      \midrule % from booktabs package
+      \(k\) (number of samples) & 100\\
+      \(J\) (Number of eigenvalues) & 6\\
+      \(\lambda\) & \(\frac{1}{\lvert \mathcal{D}_s \rvert}\)\\
+      \(\eta\) (Regularization coefficient for SSGE) & 0.95\\
+      \bottomrule % from booktabs package
+    \end{tabular}
+\end{table}
+
 \subsection{Uninformative Prior}
 First, it is interesting to see how our method will compare to NoisyNet
-in environments without the advantage of prior knowledge.
-We hypothesize that the added KL-term will push the algorithm to keep exploring unexplored
-state-action pairs more than NoisyNet, thus
+in environments without the advantage of prior knowledge. The training curves
+of our model compared to that of standard NoisyNet-DQN on the four selected OpenAI
+Gym~\citep{brockman_openai_2016} enivornments is shown in Figure~\ref{fig:training_curves}.
+We hypothesize that the added KL-term will push the algorithm keep weight uncertinaty high
+in order to keep a higher uncertainty in the output. While both methods are able to
+find an optimal policy in Cartpole, our method method uses considerably fewer frames
+to do so.
 
@@
         \centering
-        \includegraphics[width=\columnwidth]{charts/Cartpole_score}
+        \includegraphics[width=\columnwidth]{example-image}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\columnwidth]{charts/MountainCar_score}
+        \includegraphics[width=\columnwidth]{example-image}
     \end{subfigure}
-    \caption{Example figure 1}
-    \label{fig:fig_1}
+    \caption{Comparison of learning curves of LFM and NoisyNet-DQN on
+    Pong, Cartpole, MountainCar, and Acrobot averaged over 100 episodes.}
+    \label{fig:training_curves}
+\end{figure}
+
+\cite{fortunato_noisy_2019} noted that the learned variance in their weight increased
+in some games despite there existing an optimal deterministic solution, and the loss
+giving no incentive to maintain any uncertainty. Figure~\ref{fig:mean_std} shows
+the mean-absolute standard deviation for the penultimate and final layer. It is 
+interesting to see that the standard deviation for NoisyNet continous to decrease
+throughout the training, while LFM decreases faster, but then flattens out earlier.
+This seems to indicate that it has found a policy that
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{charts/penult}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{charts/ult}
+    \end{subfigure}
+    \caption{Comparison of mean-absolution standard deviation for NoisyNet and LFM
+    on Cartpole.}
+    \label{fig:mean_std}
 \end{figure}
@@
 
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.45\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{example-image}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.45\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{example-image}
-    \end{subfigure}
-    \includegraphics[width=\columnwidth]{example-image}
-    \caption{Performance on the CartPole-v1 environment.}
-\end{figure}
+% \begin{figure}
+%     \centering
+%     \begin{subfigure}[b]{0.45\columnwidth}
+%         \centering
+%         \includegraphics[width=\columnwidth]{example-image}
+%     \end{subfigure}
+%     \begin{subfigure}[b]{0.45\columnwidth}
+%         \centering
+%         \includegraphics[width=\columnwidth]{example-image}
+%     \end{subfigure}
+%     \includegraphics[width=\columnwidth]{example-image}
+%     \caption{Performance on the CartPole-v1 environment.}
+% \end{figure}
 
@@
 \section{Conclusion}
+We have developed a method for exploration with a DQN-style algorithm that can
+effectively utilize domain knowledge for faster learning.
 

### 2022-01-27 scripts/RLExp_DUQNS_Atari.jl

@@ -52,7 +52,7 @@ function RL.Experiment(
                         "batch_size" => 32,
                         "min_replay_history" => 10_000,
                         "updates_per_step" => 1,
-                        "λ" => 1,
+                        "λ" => 1e-6,
                         "prior" => "FlatPrior()",
                     #    "prior" => "GaussianPrior(0, 10)",
                         "n_samples" => 100,

### 2022-01-27 scripts/RLExp_DUQNS_Cartpole.jl

@@ -41,7 +41,7 @@ function RL.Experiment(
                      name="DUQNS_CartPole",
                      config = Dict(
                         "B_lr" => 1e-4,
-                        "Q_lr" => 1.0,
+                        "Q_lr" => 1,
                         "B_clip_norm" => 1000.0,
                         "B_update_freq" => 1,
                         "Q_update_freq" => 1000,
@@ -51,12 +51,13 @@ function RL.Experiment(
                         "batch_size" => 32,
                         "min_replay_history" => 32,
                         "updates_per_step" => 1,
-                        "λ" => 1.0,
+                        "λ" => 1,
                         # "prior" => "GaussianPrior(0, 10)",
                         "prior" => "FlatPrior()",
                         "n_samples" => 100,
-                        "η" => 0.01,
+                        "η" => 0.95,
                         "nev" => 10,
+                        "n_eigen_threshold" => 0.98,
                         "is_enable_double_DQN" => true,
                         "traj_capacity" => 1_000_000,
                         "seed" => 1,
@@ -85,7 +86,7 @@ function RL.Experiment(
         CREATE MODEL
         """
         # init = glorot_uniform(rng)
-        init(a, b) = (2 .* rand(a, b) .- 1) ./ sqrt(b)
+        init(dims...) = (2 .* rand(dims...) .- 1) ./ Float32(sqrt(dims[end]))
         init_σ(dims...) = fill(0.4f0 / Float32(sqrt(dims[end])), dims)
 
 
@@ -197,8 +198,8 @@ function RL.Experiment(
                     p = agent.policy.learner.logging_params
 
                     KL, H, S, L, Q = p["KL"], p["H"], p["S"], p["𝐿"], p["Q"]
-                    B_var, QA = p["B_var"], p["QA"]
-                    @info "training" KL = KL H = H S = S L = L Q = Q B_var = B_var QA = QA
+                    B_var, QA, s = p["B_var"], p["QA"], p["s"]
+                    @info "training" KL = KL H = H S = S L = L Q = Q B_var = B_var QA = QA s = s
 
                     last_layer = agent.policy.learner.B_approximator.model[end].paths[1][end].w_ρ
                     penultimate_layer = agent.policy.learner.B_approximator.model[end].paths[1][end-1].w_ρ

### 2022-01-27 scripts/RLExp_GDQN_Atari.jl

@@ -38,7 +38,6 @@ function RL.Experiment(
     simulation = @ntuple name lr bz tuf seed
     lg = WandbLogger(project = "RLExp", name="GDQN_" * savename(simulation))
     save_dir = datadir("sim", "GDQN", savename(simulation, "jld2"))
-    mkpath(save_dir)
 
     """
     SET UP ENVIRONMENT

### 2022-01-27 scripts/RLExp_Noisy_Acrobot.jl

@@ -40,7 +40,7 @@ function RL.Experiment(
                        "batch_size" => 32,
                        "min_replay_history" => 32,
                        "updates_per_step" => 1,
-                       "λ" => 1.0,
+                       "λ" => 0.1,
                        # "prior" => "GaussianPrior(0, 10)",
                        "prior" => "FlatPrior()",
                        "n_samples" => 100,

### 2022-01-27 src/algorithms/DUQNS.jl

@@ -78,7 +78,7 @@ function DUQNSLearner(;
         update_step,
         sampler,
         rng,
-        SpectralSteinEstimator(Float32(η), nev, nothing),
+        SpectralSteinEstimator(Float32(η), nev, 0.99),
         Float32(injected_noise),
         n_samples,
         is_enable_double_DQN,
@@ -177,7 +177,7 @@ function RLBase.update!(learner::DUQNSLearner, batch::NamedTuple)
         ss = s_all[a, :]
         B̂ = dropdims(mean(b, dims=ndims(b)), dims=ndims(b))
         λ = learner.λ
-        𝐿 = sum(ss .+ (b .- G) .^ 2 .* exp.(-ss))
+        𝐿 = sum(ss ./ 2 .+ (b .- G) .^ 2 .* exp.(-ss))
         𝐿 /= n_samples * batch_size
 
         b_rand = reshape(b_all, :, n_samples) ## SLOW

### 2022-01-27 src/algorithms/common.jl

@@ -65,62 +65,62 @@ function make_noise_sqrt(rng, μ, dims...)
     return sign.(noise) .* sqrt.(abs.(noise))
 end
 
-function (l::NoisyDense)(x, num_samples::Union{Int, Nothing}=nothing; rng::Union{AbstractRNG, Nothing}=nothing)
-    rng = rng === nothing ? l.rng : rng
-    x = ndims(x) == 2 ? unsqueeze(x, 3) : x
-    tmp_x = reshape(x, size(x, 1), :)
-    μ = l.w_μ * tmp_x .+ l.b_μ
-
-    if num_samples === nothing
-        ϵ_1 = Zygote.@ignore make_noise_sqrt(rng, μ, size(μ, 1), 1)
-        ϵ_2 = Zygote.@ignore make_noise_sqrt(rng, μ, size(l.w_μ, 2), 1)
-    else
-        ϵ_1 = Zygote.@ignore make_noise_sqrt(rng, μ, size(μ, 1), 1, num_samples)
-        ϵ_2 = Zygote.@ignore make_noise_sqrt(rng, μ, size(l.w_μ, 2), 1, num_samples)
-    end
-    noisy_x = x .* ϵ_2
-    noisy_x = reshape(noisy_x, size(noisy_x, 1), :)
-    σ² = l.w_ρ * noisy_x .+ l.b_ρ
-
-    σ² = reshape(σ², size(σ²,1), size(x, 2), :) .* ϵ_1
-
-    μ = reshape(μ, size(μ, 1), size(x, 2), :)
-    σ² = reshape(σ², size(μ, 1), size(x, 2), :)
-    return y = l.f.(μ .+ σ²)
-end
-
-
 # function (l::NoisyDense)(x, num_samples::Union{Int, Nothing}=nothing; rng::Union{AbstractRNG, Nothing}=nothing)
 #     rng = rng === nothing ? l.rng : rng
 #     x = ndims(x) == 2 ? unsqueeze(x, 3) : x
-#     # μ = l.w_μ * tmp_x .+ l.b_μ
-#     wσ² = l.w_ρ
-#     bσ² = l.b_ρ
+#     # tmp_x = reshape(x, size(x, 1), :)
+#     μ = batched_mul(l.w_μ, x) .+ l.b_μ
 
 #     if num_samples === nothing
-#         tmp_x = reshape(x, size(x, 1), :)
[…]

### 2022-01-28 papers/main.tex
TEMPORARY DEPLOY COMMIT

@@
 \usepackage{booktabs} % commands to create good-looking tables
+\usepackage{multicol}
 \usepackage{tikz} % nice language for creating drawings and diagrams
@@
 
-In this paper we will introduce an extension to NoisyNet that puts it into a Bayesian context.
+In this paper, we will introduce an extension to NoisyNet that puts it into a Bayesian context.
 A limitation of NoisyNet is that the initial uncertainty in the Q-value function is crucial to exploration.
@@
 that NoisyNet can model stochastic policies, \citet{fortunato_noisy_2019} point
-out that for the loss function it is optimising, there always exsit a deterministic
+out that for the loss function it is optimising, there always exsists a deterministic
 optimal policy. They show through emipirical analysis, however, that this does not
@@
 \begin{equation}
-    \KL[Q \Vert P] = \sup_{n \in \N, \X \in \mathcal{X}^n} \KL \left[ Q_\X \Vert P_\X \right],
+    \KL[A \Vert B] = \sup_{n \in \N, \X \in \mathcal{X}^n} \KL \left[ A_\X \Vert B_\X \right],
 \end{equation}
 
-Now the stochastic processes are a neural network \(q_\phi\) and a prior \(p\). In a similar
+Now the stochastic processes is represented by a neural network \(q_\phi\) and a prior \(p\). In a similar
 manner to NoisyNet, we sample a function \(f\) from \(q\) by sampling a random noise vector
@@
 % * Meaningful priors
+
+\citet{osband_why_2017} prove that in finite horizon MDPs, posterior sampling for
+reinforcement learning has at least a near-optimal regret bound. They further conjecture
+that this can be improved to show an optimal regret bound. Additionally,
+a posterior sampling-based reinforcement learning algorithm can be made to utilize
+prior information or domain knowledge through an appropriate prior. This should improve
+the policy convergence rate.
+Combined with the computational efficiency of posterior sampling, this motivates the
+development of a Bayesian reinforcement learning algorithm with functional priors.
+
 We will present a method based on functional variational Bayesian neural
@@
 
+We would like to approximate the posterior distribution of the Q-value function.
+%% BNN useful for both
+
 % A natural step for finding
@@
 
-We would like to approximate the posterior distribution of the Q-value function.
-\citet{osband_why_2017} prove that in finite horizon MDPs posterior sampling for
-reinforcement learning has at least a near-optimal regret bound. They further conjecture
-that this cound can be further improved to show an optimal regret bound. Additionally,
-a posterior sampling based reinfrocement learning algorithm could be made to utilize
-prior information or domain knowledge through an appropriate prior. This should improve
-policy convergence rate.
-Combined with the computational efficiency of posterior sampling, this motivates the
-development of a Bayesian reinforcement learning algorithm with functional priors.
-
-We can use the functional variational bayesian neural
+We can use the functional variational Bayesian neural
 network (FVBNN)~\citep{sun_functional_2019} framework discussed earlier.
@@
     \caption{Hyperparameters for LFM.}\label{tab:hyperparams}
-    \begin{tabular}{rl}
+    \begin{tabular}{rll}
       \toprule % from booktabs package
-      Hyperparameter & Value \\
+      \multicolumn{2}{c}{Hyperparameter} & Value \\
       \midrule % from booktabs package
-      \(k\) (number of samples) & 100\\
-      \(J\) (Number of eigenvalues) & 6\\
-      \(\lambda\) & \(\frac{1}{\lvert \mathcal{D}_s \rvert}\)\\
-      \(\eta\) (Regularization coefficient for SSGE) & 0.95\\
+      \(k\)         & Number of function samples & 100\\
+      \(J\)         & Number of eigenvectors & 6\\
+      \(\lambda\)   & KL regularization parameter & \(\frac{1}{\lvert \mathcal{D}_s \rvert}\)\\
+      \(\eta\)      & Regularization coefficient for SSGE & 0.95\\
       \bottomrule % from booktabs package
@@
 in order to keep a higher uncertainty in the output. While both methods are able to
-find an optimal policy in Cartpole, our method method uses considerably fewer frames
+find an optimal policy in Cartpole, our method uses considerably fewer frames
 to do so.
+
+Future
 
@@
 in some games despite there existing an optimal deterministic solution, and the loss
-giving no incentive to maintain any uncertainty. Figure~\ref{fig:mean_std} shows
+gives no incentive to maintain any uncertainty. Figure~\ref{fig:mean_std} shows
 the mean-absolute standard deviation for the penultimate and final layer. It is 
@@
 throughout the training, while LFM decreases faster, but then flattens out earlier.
-This seems to indicate that it has found a policy that
+This seems to indicate that it has found a stable policy, where optimizing further would
+be overfitting to noise.
 
@@
 
-\section{Discussion}
+\section{Conclusion and Discussion}
+We have presented a method for exploration with a DQN-style algorithm that can
+effectively utilize domain knowledge for faster learning. Our results show that
+it outperforms standard DQN with NoisyNet exploration with regards to sample efficiency
+on all four selected environments even without prior knowledge.
 
-\section{Conclusion}
-We have developed a method for exploration with a DQN-style algorithm that can
-effectively utilize domain knowledge for faster learning.
+One interesting avenue for future work is to extend the approach to methods other than
+the standard DQN. A functional Bayesian approach for policy evaluation would permit direct
+prior distribution in policy space rather than in value space, which seems like a
+more intuitive prior in many domains.
 

### 2022-01-28 scripts/RLExp_DUQNS_Atari.jl

@@ -47,7 +47,7 @@ function RL.Experiment(
                         "B_update_freq" => 4,
                         "Q_update_freq" => 40_000,
                         "B_opt" => "ADAM",
-                        "gamma" => 0.99,
+                        "gamma" => 0.99f0,
                         "update_horizon" => 1,
                         "batch_size" => 32,
                         "min_replay_history" => 10_000,
@@ -93,7 +93,7 @@ function RL.Experiment(
         CREATE MODEL
         """
         initc = glorot_uniform(rng)
-        init(a, b) = (2 .* rand(a, b) .- 1) ./ sqrt(b)
+        init(a, b) = (2 .* rand(rng, Float32, a, b) .- 1) ./ Float32(sqrt(b))
         init_σ(dims...) = fill(0.4f0 / Float32(sqrt(dims[end])), dims)
         
         B_model = Chain(
@@ -173,7 +173,7 @@ function RL.Experiment(
     """
     EVALUATION_FREQ = 250_000
     STEP_LOG_FREQ = 1_000
-    EPISODE_LOG_FREQ = 100
+    EPISODE_LOG_FREQ = 1
     MAX_EPISODE_STEPS_EVAL = 27_000
 
     screens = []

### 2022-01-28 scripts/RLExp_Noisy_MountainCar.jl

@@ -35,17 +35,11 @@ function RL.Experiment(
                        "B_update_freq" => 1,
                        "Q_update_freq" => 1000,
                        "B_opt" => "ADAM",
-                       "gamma" => 0.99,
+                       "gamma" => 0.99f0,
                        "update_horizon" => 1,
                        "batch_size" => 32,
                        "min_replay_history" => 10_000,
                        "updates_per_step" => 1,
-                       "λ" => 1.0,
-                       # "prior" => "GaussianPrior(0, 10)",
-                       "prior" => "FlatPrior()",
-                       "n_samples" => 100,
-                       "η" => 0.01,
-                       "nev" => 10,
                        "is_enable_double_DQN" => true,
                        "traj_capacity" => 1_000_000,
                        "seed" => 1,
@@ -85,7 +79,7 @@ function RL.Experiment(
                             NoisyDense(128, 128, relu; init_μ = init, init_σ = init_σ, rng = device_rng),
                             NoisyDense(128, na; init_μ = init, init_σ = init_σ, rng = device_rng),
                     ),
-                    optimizer = ADAM(1e-3),
+                    optimizer = ADAM(get_config(lg, "B_lr")),
                 ) |> gpu,
                 target_approximator = NeuralNetworkApproximator(
                     model = Chain(
@@ -97,17 +91,18 @@ function RL.Experiment(
                 ) |> gpu,
                 loss_func = mse,
                 stack_size = nothing,
-                batch_size = 32,
-                update_horizon = 1,
-                min_replay_history = 32,
-                update_freq = 1,
-                target_update_freq = 1_000,
+                γ = Float32(get_config(lg, "gamma")),
+                batch_size = get_config(lg, "batch_size"),
+                update_horizon = get_config(lg, "update_horizon"),
+                min_replay_history = get_config(lg, "min_replay_history"),
+                update_freq = get_config(lg, "B_update_freq"),
+                target_update_freq = get_config(lg, "Q_update_freq"),
                 rng = rng,
             ),
             explorer = GreedyExplorer(),
         ),
         trajectory = CircularArraySARTTrajectory(
-            capacity = 1_000_000,
+            capacity = get_config(lg, "traj_capacity"),
             state = Vector{Float32} => (ns,),
         ),
     )

### 2022-01-28 src/algorithms/common.jl

@@ -25,7 +25,7 @@ function NoisyDense(
     out,
     f=identity;
     init_μ=glorot_uniform,
-    init_σ=(dims...) -> fill(0.1f0 / Float32(sqrt(dims[end])), dims),
+    init_σ=(dims...) -> fill(0.4f0 / Float32(sqrt(dims[end])), dims),
     # init_σ=(dims...) -> fill(0.017f0, dims),
     rng=Random.GLOBAL_RNG,
 )

### 2022-01-28 papers/main.tex
TEMPORARY DEPLOY COMMIT

@@
 are the same as those described in \cite{han_nrowan-dqn_2020}. Our method additionally
-has hyperparameters related to the functional KL-divergence. These are shown in
+has hyperparameters related to the functional KL-divergence. These are reported in
 Table~\ref{tab:hyperparams}.
@@
 of our model compared to that of standard NoisyNet-DQN on the four selected OpenAI
-Gym~\citep{brockman_openai_2016} enivornments is shown in Figure~\ref{fig:training_curves}.
-We hypothesize that the added KL-term will push the algorithm keep weight uncertinaty high
-in order to keep a higher uncertainty in the output. While both methods are able to
+Gym~\citep{brockman_openai_2016} environments is shown in Figure~\ref{fig:training_curves}.
+We hypothesize that the added KL-term will push the algorithm to retain weight uncertainty high
+in order to keep a higher uncertainty in the output. While both methods can
 find an optimal policy in Cartpole, our method uses considerably fewer frames
@@
 in some games despite there existing an optimal deterministic solution, and the loss
-gives no incentive to maintain any uncertainty. Figure~\ref{fig:mean_std} shows
+provides no incentive to maintain any uncertainty. Figure~\ref{fig:mean_std} shows
 the mean-absolute standard deviation for the penultimate and final layer. It is 
-interesting to see that the standard deviation for NoisyNet continous to decrease
-throughout the training, while LFM decreases faster, but then flattens out earlier.
+interesting to see that the standard deviation for NoisyNet continues to decrease
+throughout the training while LFM decreases faster, but then flattens out earlier.
 This seems to indicate that it has found a stable policy, where optimizing further would

### 2022-01-28 scripts/RLExp_Noisy_MountainCar.jl

@@ -114,6 +114,20 @@ function RL.Experiment(
     hook = ComposedHook(
         step_per_episode,
         reward_per_episode,
+        DoEveryNStep() do t, agent, env
+            try
+                with_logger(lg) do
+                    last_layer = agent.policy.learner.approximator.model[end].w_ρ
+                    penultimate_layer = agent.policy.learner.approximator.model[end-1].w_ρ
+                    sul = sum(abs.(last_layer)) / length(last_layer)
+                    spl = sum(abs.(penultimate_layer)) / length(penultimate_layer)
+                    @info "training" sigma_penultimate_layer = spl sigma_ultimate_layer = sul
+                end
+            catch
+                close(lg)
+                stop("Program most likely terminated through WandB interface.")
+            end
+        end,
         DoEveryNEpisode(n = 50) do t, agent, env
             @info "evaluating agent at $t step..."
             p = agent.policy
@@ -133,7 +147,7 @@ function RL.Experiment(
             @info "finished evaluating agent in $(round(s, digits=2)) seconds" avg_length = avg_length avg_score = avg_score
             try
                 with_logger(lg) do
-                    @info "evaluating" avg_length = avg_length avg_score = avg_score log_step_increment = step_per_episode.steps[end]
+                    @info "evaluating" avg_length = avg_length avg_score = avg_score log_step_increment = 0
                     @info "training" episode_length = step_per_episode.steps[end] reward = reward_per_episode.rewards[end] log_step_increment = 0
                     @info "training" episode = t log_step_increment = 0
                     

### 2022-02-02 papers/main.tex
TEMPORARY DEPLOY COMMIT

@@
 this parameterized function as \(g_\phi\), and their sampling distribution as
-\(q_\phi \in \mathcal{Q}\). Given a noise vector \(\xi\), we have
+\(\rho_\phi \in \mathcal{P}\). Given a noise vector \(\xi\), we have
 \(f(\bm{s}, \bm{a}) = g_\phi(\bm{a}, \bm{s}, \xi)\). This means that NoisyNet
@@
 over functions, also known as a stochastic process.
-\citet{sun_functional_2019} show that for two stochastic processes \(P\) and \(Q\), the
-KL-divergence from \(Q\) to \(P\) is the supremum of the marginal KL-divergences over
-all finite measurement sets. Let \(P_\X\) be the marginal distribution of function values
+\citet{sun_functional_2019} show that for two stochastic processes \(A\) and \(B\), the
+KL-divergence from \(A\) to \(N\) is the supremum of the marginal KL-divergences over
+all finite measurement sets. Let \(A_\X\) be the marginal distribution of function values
 at \(\X \in \mathcal{X}^n\), then:
@@
 
-Now the stochastic processes is represented by a neural network \(q_\phi\) and a prior \(p\). In a similar
-manner to NoisyNet, we sample a function \(f\) from \(q\) by sampling a random noise vector
+Now the stochastic processes is represented by a neural network \(\rho_\phi\) and a prior \(p\). In a similar
+manner to NoisyNet, we sample a function \(f\) from \(\rho_\phi\) by sampling a random noise vector
 \(\xi\), and then defining \(f(\bm{x}) = g_\phi(\bm{x}, \xi)\). They further show that the
@@
 \begin{multline}\label{eq:fkl}
-    \nabla_\phi \KL[q_\phi(\f^\X) \Vert p(\f^\X)] = \E_q \left[ \nabla_\phi \log q_\phi (\f^\X) \right]\\
-    + \E_\xi \left[ \nabla_\phi \f^\X( \nabla_\f \log q(\f^\X) - \nabla_\f \log p(\f^\X)) \right].
+    \nabla_\phi \KL[q_\phi(\f(\X)) \Vert p(\f(\X))] = \E_\rho \left[ \nabla_\phi \log \rho_\phi (\f(\X)) \right]\\
+    + \E_\xi \left[ \nabla_\phi \f(\X)( \nabla_\f \log \rho_\phi(\f(\X)) - \nabla_\f \log p(\f(\X))) \right].
 \end{multline}
@@
 The first term is just the expected value of the score function, which is zero.
-The difficult part in \eqref{eq:fkl} is to estimate \(\nabla_\f \log q(\f^\X)\)
-and \(\nabla_\f \log p(\f^\X)\). \(\nabla_\f \log q(\f^\X)\) is likely 
-intractable, considering \(q_\phi\) is a neural network with stochastic weights.
+The difficult part in \eqref{eq:fkl} is to estimate \(\nabla_\f \log \rho(\f^\X)\)
+and \(\nabla_\f \log p(\f^\X)\). \(\nabla_\f \log \rho(\f^\X)\) is likely 
+intractable, considering \(\rho_\phi\) is a neural network with stochastic weights.
 Depending on how we define the prior, however, \(\nabla_\f \log p(\f^\X)\)
-can be easy to compute analytically. To reduce variance in the gradients we
+can be easy to compute analytically. To reduce variance in the gradients, we
 define tractable priors in this paper. To estimate the log-density gradient
-\(\nabla_\f \log q(\f^\X)\), they use the Spectral Stein Gradient Estimator (SSGE)
+\(\nabla_\f \log \rho(\f^\X)\), they use the Spectral Stein Gradient Estimator (SSGE)
 \citep{shi_spectral_2018}. In short, this is a method for estimating the gradient
 function of implicit distributions using approximations to eigenfunctions of a 
-kernel based operator. We bring three hyperparameters into the algorithm from this
+kernel-based operator. We bring three hyperparameters into the algorithm from this
 method, the number of samples \(k\) from the implicit distribution used to approximate
@@
 \begin{multline}
-    {\frac{1}{\lvert \D_s \rvert}} \sum_{()\bm{x}, y) \in D_s} \E_{q_\phi}
+    {\frac{1}{\lvert \D_s \rvert}} \sum_{(\bm{x}, y) \in D_s} \E_{\rho_\phi}
     \left[ p(y \vert f(\bm{x})) \right]\\ - \lambda \KL
-    \left[ q(\f^{\D_s}, \f^\mathbf{M}) \Vert p(\f^{\D_s}, \f^\mathbf{M}) \right].
+    \left[ \rho_\phi \left(\f(\D_s), \f(\mathbf{M}) \right) \Vert p \left(\f(\D_s), \f(\mathbf{M}) \right) \right].
 \end{multline}
@@
 \cite{sun_functional_2019} note, however, that the minimization target is only a lower
-bound for \(\KL \left[ \lvert q(f) \Vert p(f) \right]\), so a larger
+bound for \(\KL \left[ \lvert \rho(f) \Vert p(f) \right]\), so a larger
 value for \(\lambda\) is likely necessary to prevent overfitting. They use,
@@
 from a Gaussian distribution. We then model the network to produce two output vectors,
-\(\mu\) and \(\rho = \log \sigma\). This gives the following loss function:
+\(\mu\) and \(\tau = \log \sigma\). This gives the following loss function:
 
 \begin{equation}
-    \mathcal{L} = \frac{1}{\lvert \D_s \rvert}\sum_{i=1}^{\lvert \D_s \rvert} \rho_i + \left( \mu_i - q_i \right)^2
-    \exp (-\rho_i) + \lambda \KL[q \Vert p].
+    \mathcal{L} = \frac{1}{\lvert \D_s \rvert}\sum_{i=1}^{\lvert \D_s \rvert} \tau_i + \left( \mu_i - q_i \right)^2
+    \exp (-\tau_i) + \lambda \KL[\rho \Vert p].
 \end{equation}
@@
 \begin{algorithm}
-\caption{NoisyNet RL}
+\caption{DQN-update}
 \begin{algorithmic}
@@
         \State \(\D \gets \D \cup \{s,a,r,s'\}\)
-        \State \Call{UpdateNoisyNet}{$\phi, \omega, \D$}
+        \State \Call{UpdateNet}{$\phi, \omega, \D$}
     \EndWhile
-    \Statex
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{NoisyNet RL}
+\begin{algorithmic}
     \Function{UpdateNoisyNet}{$\phi, \omega, \D$}
@@
         \For{\(\{s,a,r,s'\} \in T\)}
-            \State \(\bm{q} \gets \max_a \f(s,a)\)
-            \State \(\mathcal{F} \gets \mathcal{F} \cup \f(s,a)\)
+            \State \(q \gets \max_a f(s,a)\)
             \State \(G \gets r + \gamma b(s,a)\)
-            \State \(\Delta_\mathcal{L} \gets \Delta_\mathcal{L} - \frac{1}{\lvert T \rvert} \nabla_\phi \log p(\bm{q} \vert \bm{G})\)
+            \State \(\Delta_\mathcal{L} \gets \Delta_\mathcal{L} - \frac{1}{\lvert T \rvert} \nabla_\phi \log p(q \vert G)\)
         \EndFor
@@
 \begin{algorithmic}
-    \State \(\D \gets \emptyset\)
-    \State \(s \sim P_0\)
-    \State Initialize \(\phi, \omega\)
-    \While{not converged}
-        \State \(f \sim q_\phi\)
-        \State \(a \sim \arg\max_a f(s,a)\)
-        \State \(s' \sim P(\cdot \vert s,a)\)
-        \State \(r = r(s',a,s)\)
-        \State \(\D \gets \D \cup \{s,a,r,s'\}\)
-        \State \Call{UpdatePosterior}{$\phi, \omega, \D$}
-    \EndWhile
-    \Statex
     \Function{UpdatePosterior}{$\phi, \omega, \D$}

### 2022-02-02 scripts/RLExp_DUQNS_Cartpole.jl

@@ -55,8 +55,8 @@ function RL.Experiment(
                         # "prior" => "GaussianPrior(0, 10)",
                         "prior" => "FlatPrior()",
                         "n_samples" => 100,
-                        "η" => 0.05,
-                        "nev" => 10,
+                        "η" => 0.95,
+                        "nev" => 6,
                         "n_eigen_threshold" => 0.98,
                         "is_enable_double_DQN" => true,
                         "traj_capacity" => 1_000_000,

### 2022-02-02 src/algorithms/DUQNS.jl

@@ -174,10 +174,11 @@ function RLBase.update!(learner::DUQNSLearner, batch::NamedTuple)
     gs = gradient(params(B)) do
         b_all, s_all = B(s, n_samples, rng = rng_B) ## SLOW
         b = b_all[a, :]
-        ss = s_all[a, :]
+        ss = clamp.(s_all[a, :], -2, 2)
         B̂ = dropdims(mean(b, dims=ndims(b)), dims=ndims(b))
         λ = learner.λ
         𝐿 = sum(ss .+ (b .- G) .^ 2 .* exp.(-ss))
+        # 𝐿 = sum((b .- G) .^ 2)
         𝐿 /= n_samples * batch_size
 
         b_rand = reshape(b_all, :, n_samples) ## SLOW

### 2022-02-02 src/algorithms/common.jl

@@ -62,7 +62,7 @@ Flux.@functor NoisyDense
 
 function make_noise_sqrt(dims...)
     noise = CUDA.randn(Float32, dims...)
-    noise .= copysign.(sqrt.(abs.(noise)), noise)
+    # noise .= copysign.(sqrt.(abs.(noise)), noise)
     return noise
 end
 

### 2022-02-03 papers/main.tex
TEMPORARY DEPLOY COMMIT

@@
 
+Before we dwelve into the background, we need to presicise some notation. Most of the
+theory will be based on stochastic functions. The stochastic process we are interested is
+generating value functions on an MDP, and exists on the probability space on the probability
+space \((\Omega, \mathcal{F}, P)\). It can be written as
+\(\{Q(\bm{s}, \bm{a}) : (\bm{s}, \bm{a}) \in \state \times \action \}\). For
+any \(\omega \in \Omega\), \(Q(\cdot, \cdot, \omega)\) is a sample function
+mapping \(\state \times \action \rightarrow \mathbb{R}\). To simplify notation
+we will denote sample functions as \(f\). For a set of multiple sampled functions we will
+use \(\f\), where \(\f(\X)\) means each sampled function evaluated at the same point,
+i.e. \(\{f(\X) \mid f \in \f\}\).
+
 %To properly adapt Bayesian inference to MDPs, \cite{fellows_bayesian_2021} define the Bayesian Bellman
@@
 \subsection{Noisy Networks}
-In NoisyNet \citep{fortunato_noisy_2019}, the Q-function space can be seen
-as a stochastic process on the probability space \((\Omega, \mathcal{F}, P)\).
-The stochastic process can simply be written as
-\(\{Q(\bm{s}, \bm{a}) : (\bm{s}, \bm{a}) \in \state \times \action \}\). For
-any \(\omega \in \Omega\), \(Q(\cdot, \cdot, \omega)\) is a sample function
-mapping \(\state \times \action \rightarrow \mathbb{R}\). To simplify notation
-we will denote sample functions as \(f\). NoisyNet, specifically, is a stochastic
-process parameterized by its weights and their standard deviation. We will define
+NoisyNet, specifically, is a stochastic
+process represented by a neural network with stochastic weights. We will define
 this parameterized function as \(g_\phi\), and their sampling distribution as
 \(\rho_\phi \in \mathcal{P}\). Given a noise vector \(\xi\), we have
-\(f(\bm{s}, \bm{a}) = g_\phi(\bm{a}, \bm{s}, \xi)\). This means that NoisyNet
-gives a new policy function for each noise vector \(\xi\). Although this means
+\(f(\bm{s}, \bm{a}) = g_\phi(\bm{a}, \bm{s}, \xi)\). Although this means
 that NoisyNet can model stochastic policies, \citet{fortunato_noisy_2019} point
@@
 \begin{multline}\label{eq:fkl}
-    \nabla_\phi \KL[q_\phi(\f(\X)) \Vert p(\f(\X))] = \E_\rho \left[ \nabla_\phi \log \rho_\phi (\f(\X)) \right]\\
+    \nabla_\phi \KL[q_\phi(\f(\X)) \Vert p(\f(\X))] = \E_\rho)\phi \left[ \nabla_\phi \log \rho_\phi (\f(\X)) \right]\\
     + \E_\xi \left[ \nabla_\phi \f(\X)( \nabla_\f \log \rho_\phi(\f(\X)) - \nabla_\f \log p(\f(\X))) \right].
@@
 The first term is just the expected value of the score function, which is zero.
-The difficult part in \eqref{eq:fkl} is to estimate \(\nabla_\f \log \rho(\f^\X)\)
-and \(\nabla_\f \log p(\f^\X)\). \(\nabla_\f \log \rho(\f^\X)\) is likely 
+The difficult part in \eqref{eq:fkl} is to estimate \(\nabla_\f \log \rho_\phi(\f(\X))\)
+and \(\nabla_\f \log p(\f(\X))\). \(\nabla_\f \log \rho_\phi(\f(\X))\) is likely 
 intractable, considering \(\rho_\phi\) is a neural network with stochastic weights.
-Depending on how we define the prior, however, \(\nabla_\f \log p(\f^\X)\)
+Depending on how we define the prior, however, \(\nabla_\f \log p(\f(\X))\)
 can be easy to compute analytically. To reduce variance in the gradients, we
 define tractable priors in this paper. To estimate the log-density gradient
-\(\nabla_\f \log \rho(\f^\X)\), they use the Spectral Stein Gradient Estimator (SSGE)
+\(\nabla_\f \log \rho_\phi(\f(\X))\), they use the Spectral Stein Gradient Estimator (SSGE)
 \citep{shi_spectral_2018}. In short, this is a method for estimating the gradient
@@
 \cite{sun_functional_2019} note, however, that the minimization target is only a lower
-bound for \(\KL \left[ \lvert \rho(f) \Vert p(f) \right]\), so a larger
+bound for \(\KL \left[ \lvert \rho_\phi(f) \Vert p(f) \right]\), so a larger
 value for \(\lambda\) is likely necessary to prevent overfitting. They use,
@@
     \mathcal{L} = \frac{1}{\lvert \D_s \rvert}\sum_{i=1}^{\lvert \D_s \rvert} \tau_i + \left( \mu_i - q_i \right)^2
-    \exp (-\tau_i) + \lambda \KL[\rho \Vert p].
+    \exp (-\tau_i) + \lambda \KL[\rho_\phi \Vert p].
 \end{equation}
@@
             \State \(\bm{q_\mu}, \bm{q_\sigma} \gets \max_a \f(s,a)\)
+            \State \(\bm{q_\sigma^\prime} \gets \max (\bm{q_\sigma}, \sigma_t)\)
             \State \(\mathcal{F} \gets \mathcal{F} \cup \f(s,a)\)
@@
             \State \(S \gets S + \frac{1}{k}p(\bm{q} \vert s, a)\)
-            \State \(\Delta_\mathcal{L} \gets \Delta_\mathcal{L} - \frac{1}{\lvert k \rvert} \nabla_\phi \log p(\bm{q_\mu} \vert \bm{G}, \bm{q_\sigma})\)
+            \State \(\Delta_\mathcal{L} \gets \Delta_\mathcal{L} - \frac{1}{\lvert k \rvert} \nabla_\phi \log p(\bm{q_\mu} \vert \bm{G}, \bm{q_\sigma^\prime})\)
         \EndFor

### 2022-02-03 papers/main.tex
TEMPORARY DEPLOY COMMIT

@@
 \subsection{Noisy Networks}
-NoisyNet, specifically, is a stochastic
+NoisyNet can be viewed as a stochastic
 process represented by a neural network with stochastic weights. We will define
 this parameterized function as \(g_\phi\), and their sampling distribution as
-\(\rho_\phi \in \mathcal{P}\). Given a noise vector \(\xi\), we have
+\(\rho_\phi\). Given a noise vector \(\xi\), we have
 \(f(\bm{s}, \bm{a}) = g_\phi(\bm{a}, \bm{s}, \xi)\). Although this means
 that NoisyNet can model stochastic policies, \citet{fortunato_noisy_2019} point
-out that for the loss function it is optimising, there always exsists a deterministic
+out that for the mean squared error loss in DQN, there always exsists a deterministic
 optimal policy. They show through emipirical analysis, however, that this does not
@@
 \begin{multline}\label{eq:fkl}
-    \nabla_\phi \KL[q_\phi(\f(\X)) \Vert p(\f(\X))] = \E_\rho)\phi \left[ \nabla_\phi \log \rho_\phi (\f(\X)) \right]\\
+    \nabla_\phi \KL[q_\phi(\f(\X)) \Vert p(\f(\X))] = \E_{\rho_\phi} \left[ \nabla_\phi \log \rho_\phi (\f(\X)) \right]\\
     + \E_\xi \left[ \nabla_\phi \f(\X)( \nabla_\f \log \rho_\phi(\f(\X)) - \nabla_\f \log p(\f(\X))) \right].

### 2022-02-08 papers/main.tex
Priors

@@
 optimal policy. They show through emipirical analysis, however, that this does not
-mean that the policy necessarily disregards the noise and converges to a deterministic
-policy.
+mean that the policy necessarily converges to a deterministic policy.
 
@@
 
-Now the stochastic processes is represented by a neural network \(\rho_\phi\) and a prior \(p\). In a similar
+We will use this identity to approximate the functional KL-divergence by sampling 
+measurement sets \(\X \in \mathcal{X}^n\). Note that because this KL-divergence is a 
+supremum, sampling measurment sets will always give us an underestimate of the true
+KL-divergence.
+
+In our case \(\mathcal{X} = \state \times \action\). First we start by
+defining \(\X^D\) as the set of datapoints \(\D \in \state \times \action\) that we have
+explored, but we also need points outside of what we have already explored. Sampling points
+from undiscovered states is difficult, however, since we typically don't know what the set
+of possible states includes. Since we know that each state only supports a finite number of
+actions, we propose to let \(\X^M\) be a set of state-action pairs that 
+The measurement set \(\X\) is created by concatenating the training points \(\X^D\) and a
+set of \(M\) points \(\X^M\) drawn from some distribution \(c\) that has full support
+in the space of interesting test cases.
+
+Now the stochastic processes is represented by a neural network \(g_\phi\) with sampling
+distribution \(\rho_\phi\) and a prior \(p\). In a similar
 manner to NoisyNet, we sample a function \(f\) from \(\rho_\phi\) by sampling a random noise vector
@@
 \end{multline}
-
-The measurement set \(\X\) is created by concatenating the training points \(\X^D\) and a
-set of \(M\) points \(\X^M\) drawn from some distribution \(c\) that has full support
-in the space of interesting test cases.
 
@@
 \begin{equation}
-    \log p(\D_\omega^N \vert f) - \lambda \KL \left[ q(\f^{\D_\omega^N}, \f^\mathbf{M}) \Vert p(\f^{\D_\omega^N}, \f^\mathbf{M}) \right],
+    \log p(\D_\omega^N \vert f) - \lambda \KL \left[ q(\f(\D_\omega^N), \f(\mathbf{M})) \Vert p(\f({\D_\omega^N}), \f(\mathbf{M})) \right],
 \end{equation}
-where \(\f^{\D_\omega^N}\) is \(f\) applied to the dataset \(\D_\omega^N\), and \(\f^\mathbf{M}\) is \(f\) applied to
+where \(\f({\D_\omega^N})\) is \(f\) applied to the dataset \(\D_\omega^N\), and \(\f(\mathbf{M})\) is \(f\) applied to
 a set of i.i.d. random points \(\mathbf{M} = \{m_i \sim c \mid i=1,\dots,k\} \subseteq \state \times \action\)
@@
 get more efficient exploration. We will now look at how our method can utilize domain
-knowledge to improve sample efficiency.
+knowledge to improve sample efficiency. To measure the effectiveness of priors we will use
+a distribution that has a higher concentration of large Q-values for actions that we want
+to incentivize.
 

### 2022-02-08 scripts/RLExp_DUQNS_Cartpole.jl

@@ -52,7 +52,8 @@ function RL.Experiment(
                         "min_replay_history" => 32,
                         "updates_per_step" => 1,
                         "λ" => 1,
-                        # "prior" => "GaussianPrior(0, 10)",
+                        # "prior" => "GaussianPrior(200, 100)",
+                        # "prior" => "CartpolePrior()",
                         "prior" => "FlatPrior()",
                         "n_samples" => 100,
                         "η" => 0.95,

### 2022-02-08 scripts/RLExp_DUQNS_MountainCar.jl

@@ -41,7 +41,7 @@ function RL.Experiment(
                      config = Dict(
                         "B_lr" => 1e-3,
                         "Q_lr" => 1.0,
-                        "B_clip_norm" => 100000.0,
+                        "B_clip_norm" => 10.0,
                         "B_update_freq" => 1,
                         "Q_update_freq" => 1_000,
                         "B_opt" => "ADAM",
@@ -52,8 +52,8 @@ function RL.Experiment(
                         "updates_per_step" => 1,
                         "λ" => 1.0,
                         # "prior" => "GaussianPrior(0, 10)",
-                        "prior" => "FlatPrior()",
-                        # "prior" => "MountainCarPrior()",
+                        # "prior" => "FlatPrior()",
+                        "prior" => "MountainCarPrior()",
                         "n_samples" => 100,
                         "η" => 0.95,
                         "nev" => 6,
@@ -179,8 +179,8 @@ function RL.Experiment(
                 with_logger(lg) do
                     p = agent.policy.learner.logging_params
                     KL, H, S, L, Q = p["KL"], p["H"], p["S"], p["𝐿"], p["Q"]
-                    B_var, QA = p["B_var"], p["QA"]
-                    @info "training" KL = KL H = H S = S L = L Q = Q B_var = B_var QA = QA
+                    B_var, QA, s = p["B_var"], p["QA"], p["s"]
+                    @info "training" KL = KL H = H S = S L = L Q = Q B_var = B_var QA = QA s = s
                     
                     last_layer = agent.policy.learner.B_approximator.model[end].paths[1].w_ρ
                     penultimate_layer = agent.policy.learner.B_approximator.model[end-1].w_ρ

### 2022-02-08 src/RLExp.jl

@@ -5,7 +5,7 @@ export SpectralSteinEstimator, entropy_surrogate
 export TotalOriginalRewardPerEpisode, TotalBatchOriginalRewardPerEpisode, CloseLogger
 export ResizeImage
 export get_screen
-export DUQNLearner, FlatPrior, GeneralPrior, GaussianPrior, MountainCarPrior
+export DUQNLearner, FlatPrior, GeneralPrior, GaussianPrior, MountainCarPrior, CartpolePrior
 export DUQNSLearner
 export stop, CenteredRMSProp
 export MountainCarPrior

### 2022-02-08 src/algorithms/DUQNS.jl

@@ -174,7 +174,7 @@ function RLBase.update!(learner::DUQNSLearner, batch::NamedTuple)
     gs = gradient(params(B)) do
         b_all, s_all = B(s, n_samples, rng = rng_B) ## SLOW
         b = b_all[a, :]
-        ss = clamp.(s_all[a, :], 0, 1e3)
+        ss = clamp.(s_all[a, :], -1, 1e2)
         # ss = sum(ss, dims=2) / n_samples
         B̂ = dropdims(mean(b, dims=ndims(b)), dims=ndims(b))
         λ = learner.λ

### 2022-02-08 src/algorithms/common.jl

@@ -248,7 +248,7 @@ end
 # ----- Spectral stein gradient estimator ----- #
 
 function rbf_kernel(x1::AbstractArray, x2::AbstractArray, lengthscale)
-    rb = -sum((x1 .- x2) .^ 2 ./ (2 .* lengthscale .^ 2); dims=3)  ## SLOW
+    rb = -sum((x1 .- x2) .^ 2 ./ (2 .* lengthscale .^ 2 .+ 1e-6); dims=3)  ## SLOW
     rb = dropdims(rb; dims=3)
     return exp.(rb)
 end
@@ -265,7 +265,7 @@ function grad_gram(x1::AbstractArray, x2::AbstractArray, lengthscale)
     x2 = Flux.unsqueeze(x2, 1)
     lengthscale = reshape(lengthscale, 1, 1, :)
     Kxx = rbf_kernel(x1, x2, lengthscale)  ## SLOW
-    diff = (x1 .- x2) ./ lengthscale .^ 2
+    diff = (x1 .- x2) ./ (lengthscale .^ 2 .+ 1e-8)
     dKxx_dx1 = Flux.unsqueeze(Kxx, 3) .* (-diff)
     dKxx_dx2 = Flux.unsqueeze(Kxx, 3) .* diff
     return Kxx, dKxx_dx1, dKxx_dx2
@@ -284,14 +284,14 @@ Zygote.@nograd function heuristic_lengthscale(x::AbstractArray, xm::AbstractArra
     ]
     kernel_width = flatten(kernel_width)
     kernel_width = kernel_width .* sqrt(Float32(x_dim))
-    return kernel_width = kernel_width .+ (kernel_width .< 1e-6)
+    return kernel_width = kernel_width .+ (kernel_width .< 1e-8)
 end
 
 function nystrom_ext(x, eval_points, eigen_vecs, eigen_vals, lengthscale)
     M = size(x, 1)
     Kxxm = gram(eval_points, x, lengthscale)
     phi_x = sqrt(M) .* (Kxxm * eigen_vecs)
-    return phi_x = phi_x ./ Flux.unsqueeze(eigen_vals, 1)
+    return phi_x = phi_x ./ (Flux.unsqueeze(eigen_vals, 1) .+ 1e-8)
 end
 
 abstract type BaseScoreEstimator end
@@ -337,14 +337,14 @@ function compute_gradients(
     phi_x = nystrom_ext(xm, x, eigen_vecs, eigen_vals, lengthscale)
[…]

### 2022-02-08 src/utils/priors.jl

@@ -1,4 +1,4 @@
-export FlatPrior, GeneralPrior, GaussianPrior, MountainCarPrior
+export FlatPrior, GeneralPrior, GaussianPrior, MountainCarPrior, CartpolePrior
 
 
 
@@ -22,18 +22,19 @@ end
 struct MountainCarPrior <: AbstractPrior end
 
 function (p::MountainCarPrior)(s::AbstractArray, t::AbstractArray)
-    μ = s[2,:] .> 0
-    μ = [(2f0 .* μ) zeros(size(μ)) (2f0 .* (1 - μ))]'
+    # μ = abs.(s[2,:])
+    μ = Zygote.@ignore 100f0 .* gpu([-1 -1; 0 0; 1 1]) * s
     σ = 1f0
     return sum((t .- μ) .^ 2 ./ (2σ .^ 2))
 end
 
 
-struct CartpoleCarPrior <: AbstractPrior end
+struct CartpolePrior <: AbstractPrior end
 
-function (p::CartpoleCarPrior)(s::AbstractArray, t::AbstractArray)
-    μ = s[2,:]
-    μ = [μ zeros(size(μ)) -μ]'
-    σ = 0.03f0
+function (p::CartpolePrior)(s::AbstractArray, t::AbstractArray)
+    # μ = Zygote.@ignore view(s .> 0, 3, :)
+    # μ = Zygote.@ignore [(1 .+ μ) (1 .- μ)]' .* 100f0
+    μ = Zygote.@ignore 100f0 .* gpu([0 0 0 0; 0 0 1 1]) * s
+    σ = 10f0
     return sum((t .- μ) .^ 2 ./ (2σ .^ 2))
 end

### 2022-02-10 papers/main.tex
TEMPORARY DEPLOY COMMIT

@@
 % \documentclass{uai2021} % for initial submission
-\documentclass[]{uai2021} % after acceptance, for a revised
+\documentclass[]{uai2022} % after acceptance, for a revised
                                     % version; also before submission to
@@
 \newcommand{\KL}{\mathrm{KL}}
+
+% \setlength{\tabcolsep}{12pt}
 
@@
 following that policy, and the expected reward of following an optimal policy.
-An learning algorithm's efficiency in exploration can be measured by its
+A learning algorithm's efficiency in exploration can be measured by its
 cumulative regret over time. One of the simplest reinforcement learning 
@@
 transition probabilities. One exploration strategy employed in most Q-learning
-algorithms to date, \(\epsilon\)-greedy is provably inefficient, and has a
+algorithms to date, \(\epsilon\)-greedy, is provably inefficient, and has a
 regret bound that grows linearly with time. There are several optimal algorithms
@@
 for each action. The next action is decided by sampling rewards for each action
-from the posterior distribution, and selecting the action that gave the highest
-reward. Bayesian methods has also been shown to behave efficiently with respect
+from the posterior distribution and selecting the action that gave the highest
+reward. Bayesian methods have also been shown to behave efficiently with respect
 to cumulative regret \cite{osband_generalization_2016} on general MDPs.
@@
 These are networks with stochastic weights, where each weight \(w^{(l)}_{ij}\)
-has an added pertrubaition sampled from a noise distribution with standard deviation \(\sigma^{(l)}_{ij}\).
+has an added perturbation sampled from a noise distribution with standard deviation \(\sigma^{(l)}_{ij}\).
 After initializing \(\bm{w}\) and \(\bm{\sigma}\) such that the network has sufficient
@@
 value functions~\citep{osband_generalization_2016}. They do, however, have
-experimental results which shows that the function does not always converge to
-a deterministic solution, but it is unclear why the network learns to introduce
+experimental results which show that the function does not always converge to
+a deterministic solution. It is unclear why the network learns to introduce
 more noise into the network parameters.
@@
 in a neural network with respect to a prior and a dataset. Typically, the dataset
-\(\D\) is static and with datapoints \(\bm{x}\) and labels \(\bm{y}\), and the 
+\(\D\) is given and with datapoints \(\bm{x}\) and labels \(\bm{y}\), and the 
 prior is defined as a distribution over the weights
@@
 The disadvantage of this is that \(p(\bm{w})\) only acts as a regularizer, and is not
-used to incorporate prior knowledge. Any prior knowledge we might have about the optimizer
+used to incorporate prior knowledge. Any prior knowledge we might have about the target
 function would be very difficult to translate into a prior distribution in the weight space.
@@
 \citet{sun_functional_2019} show that for two stochastic processes \(A\) and \(B\), the
-KL-divergence from \(A\) to \(N\) is the supremum of the marginal KL-divergences over
+KL-divergence from \(A\) to \(B\) is the supremum of the marginal KL-divergences over
 all finite measurement sets. Let \(A_\X\) be the marginal distribution of function values
@@
 measurement sets \(\X \in \mathcal{X}^n\). Note that because this KL-divergence is a 
-supremum, sampling measurment sets will always give us an underestimate of the true
+supremum, sampling measurement sets will always give us an underestimate of the true
 KL-divergence.
 
-In our case \(\mathcal{X} = \state \times \action\). First we start by
-defining \(\X^D\) as the set of datapoints \(\D \in \state \times \action\) that we have
-explored, but we also need points outside of what we have already explored. Sampling points
-from undiscovered states is difficult, however, since we typically don't know what the set
+In our case \(\mathcal{X} = \state \times \action\) and \(\X = \begin{bmatrix} s^T & a^T \end{bmatrix}^T\). First we start by
+defining \(\X^D\) as the set of data points \(\D \in \state \times \action\) that we have
+explored, but we also need points outside what we have already explored. Sampling points
+from undiscovered states is difficult, because we typically do not know what the set
 of possible states includes. Since we know that each state only supports a finite number of
@@
 function of implicit distributions using approximations to eigenfunctions of a 
-kernel-based operator. We bring three hyperparameters into the algorithm from this
-method, the number of samples \(k\) from the implicit distribution used to approximate
+kernel-based operator. They bring three hyperparameters into the algorithm, the number of samples \(k\) from the implicit distribution used to approximate
 the gradient, the number of eigenvectors \(J\) used to approximate the gradient, and
@@
 We hypothesize that the added KL-term will push the algorithm to retain weight uncertainty high
-in order to keep a higher uncertainty in the output. While both methods can
+to keep a higher uncertainty in the output. While both methods can
 find an optimal policy in Cartpole, our method uses considerably fewer frames
@@
 interesting to see that the standard deviation for NoisyNet continues to decrease
-throughout the training while LFM decreases faster, but then flattens out earlier.
+throughout the training while LFM decreases faster but then flattens out earlier.
 This seems to indicate that it has found a stable policy, where optimizing further would
@@
 One of the benefits of a functional prior is that we can incorporate domain knowledge to
-get more efficient exploration. We will now look at how our method can utilize domain
+get more efficient exploration. We will now see how our method can utilize domain
 knowledge to improve sample efficiency. To measure the effectiveness of priors we will use
@@
 to incentivize.
+
+\begin{align}
+    p(\bm{s},a) &\sim \mathcal{N}(\bm{\mu}, \sigma I ), \text{ where}\\
+    \bm{\mu} &= \lambda_1 + \lambda_2 \mathrm{A}_a \bm{s} \nonumber
+\end{align}
+
+% \begin{table}
+%     \centering
+%     \caption{Prior parameters}\label{tab:hyperparams}
+%     \begin{tabular}{cccl}
+%       \toprule % from booktabs package
+%       Environment & \(\lambda_1\) & \(\lambda_2\) & \(\mathrm{A}\) \\
+%       \midrule % from booktabs package
+%       Cartpole & 0 & 100 & \(\begin{bmatrix} 0 & 0 & 1 & 1 \\
+%                                              0 & 0 & -1 & -1
+%                              \end{bmatrix}\)\\
+%       MountainCar & 100 & 100 & \(\begin{bmatrix} 0 & -1 \\
+%                                                   0 & 0 \\
+%                                                   0 & 1
+%                                 \end{bmatrix}\)\\
+%       Acrobot & 100 & 100 & \(\begin{bmatrix} 0 & -1 & 0 & -1 & 0 & 0 \\
+%                                                0 & 0 & 0 & 0 & 0 & 0 \\
+%                                                0 & 1 & 0 & 1 & 0 & 0
+%                             \end{bmatrix}\)\\
+%       \bottomrule % from booktabs package
+%     \end{tabular}
+% \end{table}
 

### 2022-02-10 scripts/RLExp_DUQNS_Acrobot.jl

@@ -53,6 +53,7 @@ function RL.Experiment(
                         "λ" => 1.0,
                         # "prior" => "GaussianPrior(0, 10)",
                         "prior" => "FlatPrior()",
+                        # "prior" => "AcrobotPrior(1)",
                         "n_samples" => 100,
                         "η" => 0.01,
                         "nev" => 10,
@@ -62,6 +63,7 @@ function RL.Experiment(
                      ),
     )
     save_dir = datadir("sims", "DUQNS", "Acrobot", "$(now())")
+    mkpath(save_dir)
 
     """
     SEEDS
@@ -84,7 +86,7 @@ function RL.Experiment(
         """
         # init = glorot_uniform(rng)
         init(a, b) = (2 .* rand(a, b) .- 1) ./ sqrt(b)
-        init_σ(dims...) = fill(0.4f0 / Float32(sqrt(dims[end])), dims)
+        init_σ(dims...) = fill(0.05f0 / Float32(sqrt(dims[end])), dims)
 
 
         B_model = Chain(
@@ -238,7 +240,7 @@ function RL.Experiment(
         end,
         DoEveryNEpisode(n = 100) do t, agent, env
             @info "Saving agent at step $t to $save_dir"
-            @save save_dir agent
+            jldsave(save_dir * "/model_latest.jld2"; agent)
         end,
         CloseLogger(lg),
     )

### 2022-02-10 scripts/RLExp_DUQNS_Atari.jl

@@ -44,8 +44,8 @@ function RL.Experiment(
                         "B_lr" => 0.0001,
                         "Q_lr" => 1,
                         "B_clip_norm" => 10_000,
-                        "B_update_freq" => 4,
-                        "Q_update_freq" => 8_000,
+                        "B_update_freq" => 1,
+                        "Q_update_freq" => 1_000,
                         "B_opt" => "ADAM",
                         "gamma" => 0.99f0,
                         "update_horizon" => 1,
@@ -94,7 +94,7 @@ function RL.Experiment(
         """
         initc = glorot_uniform(rng)
         init(a, b) = (2 .* rand(rng, Float32, a, b) .- 1) ./ Float32(sqrt(b))
-        init_σ(dims...) = fill(0.4f0 / Float32(sqrt(dims[end])), dims)
+        init_σ(dims...) = fill(0.05f0 / Float32(sqrt(dims[end])), dims)
         
         B_model = Chain(
             x -> x ./ 255,

### 2022-02-10 src/RLExp.jl

@@ -5,7 +5,7 @@ export SpectralSteinEstimator, entropy_surrogate
 export TotalOriginalRewardPerEpisode, TotalBatchOriginalRewardPerEpisode, CloseLogger
 export ResizeImage
 export get_screen
-export DUQNLearner, FlatPrior, GeneralPrior, GaussianPrior, MountainCarPrior, CartpolePrior
+export DUQNLearner, FlatPrior, GeneralPrior, GaussianPrior, MountainCarPrior, CartpolePrior, AcrobotPrior
 export DUQNSLearner
 export stop, CenteredRMSProp
 export MountainCarPrior

### 2022-02-11 scripts/RLExp_DUQNS_Acrobot.jl
TEMPORARY DEPLOY COMMIT

@@ -1,5 +1,5 @@
 using Base.Iterators: tail
-using BSON: @load, @save
+using JLD2
 using CUDA
 using Dates: now
 using Distributions: Uniform, Product
@@ -52,8 +52,8 @@ function RL.Experiment(
                         "updates_per_step" => 1,
                         "λ" => 1.0,
                         # "prior" => "GaussianPrior(0, 10)",
-                        "prior" => "FlatPrior()",
-                        # "prior" => "AcrobotPrior(1)",
+                        # "prior" => "FlatPrior()",
+                        "prior" => "AcrobotPrior(1)",
                         "n_samples" => 100,
                         "η" => 0.01,
                         "nev" => 10,
@@ -179,7 +179,7 @@ function RL.Experiment(
             ),
         )
     else
-        @load restore agent
+        agent = load(restore; agent)
     end
 
     """

### 2022-02-11 scripts/RLExp_DUQN_MountainCar.jl

@@ -31,7 +31,7 @@ function RL.Experiment(
     lg = WandbLogger(project = "RLExp",
                      name="DUQN_MountainCar",
                      config = Dict(
-                        "B_lr" => 1e-3,
+                        "B_lr" => 1e-4,
                         "Q_lr" => 0.05,
                         "B_clip_norm" => 1.0,
                         "B_update_freq" => 1,

### 2022-02-11 scripts/RLExp_Noisy_Cartpole.jl

@@ -74,7 +74,7 @@ function RL.Experiment(
     """
     # init = glorot_uniform(rng)
     init(a, b) = (2 .* rand(a, b) .- 1) ./ sqrt(b)
-    init_σ(dims...) = fill(0.4f0 / Float32(sqrt(dims[end])), dims)
+    init_σ(dims...) = fill(0.05f0 / Float32(sqrt(dims[end])), dims)
 
 
     agent = Agent(

### 2022-02-11 src/RLExp.jl

@@ -9,7 +9,7 @@ export DUQNLearner, FlatPrior, GeneralPrior, GaussianPrior, MountainCarPrior, Ca
 export DUQNSLearner
 export stop, CenteredRMSProp
 export MountainCarPrior
-export AcrobotEnv
+export AcrobotEnv, GymEnv
 
 using ArcadeLearningEnvironment
 using ArcadeLearningEnvironment: getScreenRGB, getScreenWidth, getScreenHeight
@@ -29,6 +29,7 @@ using Zygote
 
 include("utils/hooks.jl")
 include("utils/atari.jl")
+include("utils/gym.jl")
 include("utils/acrobot.jl")
 include("utils/priors.jl")
 include("utils/utils.jl")

### 2022-02-11 src/algorithms/DUQNS.jl

@@ -174,7 +174,7 @@ function RLBase.update!(learner::DUQNSLearner, batch::NamedTuple)
     gs = gradient(params(B)) do
         b_all, s_all = B(s, n_samples, rng = rng_B) ## SLOW
         b = b_all[a, :]
-        ss = clamp.(s_all[a, :], -2, 1e2)
+        ss = clamp.(s_all[a, :], -10, 4)
         # ss = sum(ss, dims=2) / n_samples
         B̂ = dropdims(mean(b, dims=ndims(b)), dims=ndims(b))
         λ = learner.λ

### 2022-02-11 src/utils/priors.jl

@@ -74,13 +74,13 @@ struct AcrobotPrior <: AbstractPrior
 end
 
 function AcrobotPrior()
-    μ = s -> Zygote.@ignore 100 .+ 100f0 .* gpu([0 -1 0 -1 -0.2f0 -0.1f0; 0 0 0 0 0 0; 0 1 0 1 0.2f0 0.1f0]) * s
+    μ = s -> Zygote.@ignore 100 .+ 100f0 .* gpu([0 -1 0 -1 -0.1f0 -0.05f0; 0 0 0 0 0 0; 0 1 0 1 0.1f0 0.05f0]) * s
     σ = 10f0
     return AcrobotPrior(μ, σ)
 end
 
 function AcrobotPrior(σ)
-    μ = s -> Zygote.@ignore 100 .+ 100f0 .* gpu([0 -1 0 -1 -0.2f0 -0.1f0; 0 0 0 0 0 0; 0 1 0 1 0.2f0 0.1f0]) * s
+    μ = s -> Zygote.@ignore 100 .+ 100f0 .* gpu([0 -1 0 -1 -0.1f0 -0.05f0; 0 0 0 0 0 0; 0 1 0 1 0.1f0 0.05f0]) * s
     return AcrobotPrior(μ, Float32(σ))
 end
 

### 2022-02-17 papers/main.tex
TEMPORARY DEPLOY COMMIT

@@
 \usepackage{subcaption}
+\usepackage{etoolbox}
+\usepackage{lmodern}
+\usepackage{siunitx}
 
@@
 
-% \setlength{\tabcolsep}{12pt}
+\sisetup{detect-weight,mode=text}
+% for avoiding siunitx using bold extended
+\renewrobustcmd{\bfseries}{\fontseries{b}\selectfont}
+\renewrobustcmd{\boldmath}{}
+\newrobustcmd{\tB}{\bfseries}
+
+\setlength{\tabcolsep}{2pt}
 
@@
 state \(s_{t+1} \sim P(\cdot \vert s_t, a_t)\). A scalar reward
-\(r_t = r(\cdot \vert s_t, a_t)\) is observed. As the agent and environement
+\(r_t = r(s_t, a_t)\) is observed. As the agent and environement
 interact in a sequence of time steps, a history of observations
@@
 dependent on the policy, it must also prioritize to explore states and actions that
-the agent can learn a lot from.
+the agent has little information on.
 
@@
 reward. Bayesian methods have also been shown to behave efficiently with respect
-to cumulative regret \cite{osband_generalization_2016} on general MDPs.
+to cumulative regret \citep{osband_generalization_2016} on general MDPs.
 %\textcolor{red}{Optimal Regret + Thompson sampling }
@@
 \(a\) in state \(s\) and then following policy \(\pi\) thereafter:
-\(Q^\pi(s_0, a_0) \defeq \E_\pi \left[ \sum_{t=0}^\infty \gamma^t r_t \vert s_0=S, a_0=A \right]\).
+\(Q^\pi(s_0, a_0) \defeq \E_\pi \left[ \sum_{t=0}^\infty \gamma^t r_t \vert S=s, A_0=a \right]\).
 The Bellman operator on \(Q^\pi\) is defined as
@@
 
-Before we dwelve into the background, we need to presicise some notation. Most of the
+Before we dwelve into the background, we need to define some notation. Most of the
 theory will be based on stochastic functions. The stochastic process we are interested is
@@
 environments in the OpenAI Gym~\citep{brockman_openai_2016-2}. The hyperparameters
-are the same as those described in \cite{han_nrowan-dqn_2020}. Our method additionally
+are the same as those described  \cite{han_nrowan-dqn_2020}. Our method additionally
 has hyperparameters related to the functional KL-divergence. These are reported in
@@
     p(\bm{s},a) &\sim \mathcal{N}(\bm{\mu}, \sigma I ), \text{ where}\\
-    \bm{\mu} &= \lambda_1 + \lambda_2 \mathrm{A}_a \bm{s} \nonumber
+    \bm{\mu} &= \lambda_1 + \nu \lambda_2 \mathrm{A}_a \bm{s} \nonumber
 \end{align}
 
-% \begin{table}
-%     \centering
-%     \caption{Prior parameters}\label{tab:hyperparams}
-%     \begin{tabular}{cccl}
-%       \toprule % from booktabs package
-%       Environment & \(\lambda_1\) & \(\lambda_2\) & \(\mathrm{A}\) \\
-%       \midrule % from booktabs package
-%       Cartpole & 0 & 100 & \(\begin{bmatrix} 0 & 0 & 1 & 1 \\
-%                                              0 & 0 & -1 & -1
-%                              \end{bmatrix}\)\\
-%       MountainCar & 100 & 100 & \(\begin{bmatrix} 0 & -1 \\
-%                                                   0 & 0 \\
-%                                                   0 & 1
-%                                 \end{bmatrix}\)\\
-%       Acrobot & 100 & 100 & \(\begin{bmatrix} 0 & -1 & 0 & -1 & 0 & 0 \\
-%                                                0 & 0 & 0 & 0 & 0 & 0 \\
-%                                                0 & 1 & 0 & 1 & 0 & 0
-%                             \end{bmatrix}\)\\
-%       \bottomrule % from booktabs package
-%     \end{tabular}
-% \end{table}
+\begin{table}
+    \centering
+    \caption{Prior parameters}\label{tab:prior_hyperparams}
+    \begingroup
+    \setlength\arraycolsep{3pt}
+    \begin{tabular}{lccc}
+      \toprule % from booktabs package
+      Environment & \(\lambda_1\) & \(\lambda_2\) & \(\mathrm{A}\) \\
+      \midrule % from booktabs package
+      Cartpole & 0 & 100 & \(\begin{bmatrix} 0 & 0 & 1 & 1 \\
+                                             0 & 0 & -1 & -1
+                             \end{bmatrix}\)\\\addlinespace[0.3em]
+      MountainCar & -100 & 100 & \(\begin{bmatrix} 0 & -1 \\
+                                                  0 & 0 \\
+                                                  0 & 1
+                                \end{bmatrix}\)\\\addlinespace[0.3em]
+      Acrobot & -100 & 100 & \(\begin{bmatrix} 0 & -1 & 0 & -1 & -0.2 & -0.1 \\
+                                               0 & 0 & 0 & 0 & 0 & 0 \\
+                                               0 & 1 & 0 & 1 & 0.2 & 0.1
+                            \end{bmatrix}\)\\
+      \bottomrule % from booktabs package
+    \end{tabular}
+    \endgroup
+\end{table}
+
+\begin{table}
+    \centering
+    \caption{Number of episodes to beat select environments.}\label{tab:prior_results}
+    \begin{tabular}{cccc}
+        \toprule
+        Prior & Cartpole & MountainCar & LunarLander\\
+        \midrule
+        \(\nu = 1, \sigma = 1\)   & \tB 14  & 100 &\\
+        \(\nu = 1, \sigma = 10\)  &     33  & 1700 &\\
+        \(\nu = 1, \sigma = 50\)  &     113 & 1250 &\\
+        Flat prior                &     117 & 1650 &\\
+        \(\nu = -1, \sigma = 50\) &     177 & &\\
+        \(\nu = -1, \sigma = 20\) &     232 & &\\
+        \(\nu = -1, \sigma = 10\) &     --- & &\\
+        \midrule
+        NoisyNet                  &     219 & 1700 &\\
+        \bottomrule
+    \end{tabular}
+\end{table}
 

### 2022-02-17 scripts/RLExp_DUQNS_Atari.jl

@@ -191,7 +191,8 @@ function RL.Experiment(
                 with_logger(lg) do
                     p = agent.policy.learner.logging_params
                     KL, MSE, H, S, L, Q = p["KL"], p["mse"], p["H"], p["S"], p["𝐿"], p["Q"]
-                    @info "training" KL = KL MSE = MSE H = H S = S L = L Q = Q log_step_increment = STEP_LOG_FREQ
+                    s = p["s"]
+                    @info "training" KL = KL MSE = MSE H = H S = S L = L Q = Q s = s log_step_increment = STEP_LOG_FREQ
                     
                     last_layer = agent.policy.learner.B_approximator.model[end].paths[1].w_ρ
                     penultimate_layer = agent.policy.learner.B_approximator.model[end-1].w_ρ

### 2022-02-17 src/RLExp.jl

@@ -5,10 +5,10 @@ export SpectralSteinEstimator, entropy_surrogate
 export TotalOriginalRewardPerEpisode, TotalBatchOriginalRewardPerEpisode, CloseLogger
 export ResizeImage
 export get_screen
-export DUQNLearner, FlatPrior, GeneralPrior, GaussianPrior, MountainCarPrior, CartpolePrior, AcrobotPrior
+export DUQNLearner, FlatPrior, GeneralPrior, GaussianPrior, CartpolePrior, AcrobotPrior
 export DUQNSLearner
 export stop, CenteredRMSProp
-export MountainCarPrior
+export MountainCarPrior, LunarLanderPrior
 export AcrobotEnv, GymEnv
 
 using ArcadeLearningEnvironment

### 2022-02-17 src/algorithms/DUQNS.jl

@@ -144,7 +144,6 @@ function RLBase.update!(learner::DUQNSLearner, batch::NamedTuple)
 
     s, a, r, t, s′ = (send_to_device(D, batch[x]) for x in SARTS)
     a = CartesianIndex.(a, 1:batch_size)
-
     seed = hash(rand())
     rng_B = Random.MersenneTwister(seed)
     rng_Q = Random.MersenneTwister(seed + 1)
@@ -174,7 +173,7 @@ function RLBase.update!(learner::DUQNSLearner, batch::NamedTuple)
     gs = gradient(params(B)) do
         b_all, s_all = B(s, n_samples, rng = rng_B) ## SLOW
         b = b_all[a, :]
-        ss = clamp.(s_all[a, :], -10, 4)
+        ss = clamp.(s_all[a, :], -2, 4)
         # ss = sum(ss, dims=2) / n_samples
         B̂ = dropdims(mean(b, dims=ndims(b)), dims=ndims(b))
         λ = learner.λ
@@ -183,9 +182,20 @@ function RLBase.update!(learner::DUQNSLearner, batch::NamedTuple)
         𝐿 /= n_samples * batch_size
 
         b_rand = reshape(b_all, :, n_samples) ## SLOW
+        b_rand = Zygote.@ignore b_rand .+ 0.01f0 .* CUDA.randn(size(b_rand)...)
 
         S = entropy_surrogate(sse, permutedims(b_rand, (2, 1)))
         H = learner.prior(s, b_all) ./ (n_samples)
+
+        if any(isnan, [S, H, 𝐿]) || any(isinf, [S, H, 𝐿])
+            @show S
+            @show H
+            @show 𝐿
+            @show ss
+            @show b
+            Flux.stop()
+        end
+
 
         KL = H - S
 
@@ -202,6 +212,11 @@ function RLBase.update!(learner::DUQNSLearner, batch::NamedTuple)
         end
 
         return 𝐿 + λ * KL / batch_size
+    end
+    fff(x) = any(isnan, x)
+    if any(fff.(gs))
+        @show gs.grads
+        Flux.stop()
     end
     update!(B, gs)
 end

### 2022-02-17 src/algorithms/common.jl

@@ -106,11 +106,11 @@ function (l::NoisyDense)(x, num_samples::Union{Int, Nothing}=nothing; rng::Union
         bϵ = Zygote.@ignore make_noise_sqrt(size(bσ², 1), 1)
 
         act_w = l.w_μ * tmp_x
-        act_w_std = sqrt.((wσ² .^ 2) * (tmp_x .^ 2))
+        act_w_std = sqrt.(max.((wσ² .^ 2) * (tmp_x .^ 2), 1f-6))
 
         # println(size(act_w), size(act_w_std), size(wϵ))
         act_w_out = act_w .+ act_w_std .* wϵ
-        act_b_out = l.b_μ .+ bσ² .* bϵ
+        act_b_out = l.b_μ .+ bσ² .^ 2 .* bϵ
         
         # wϵ .= wϵ .* wσ² .+ l.w_μ
         # bϵ .= bϵ .* bσ² .+ l.b_μ
@@ -128,11 +128,18 @@ function (l::NoisyDense)(x, num_samples::Union{Int, Nothing}=nothing; rng::Union
         bϵ = ϵ_1
 
         act_w = batched_mul(l.w_μ, x)
-        act_w_std = sqrt.(batched_mul(wσ² .^ 2, x .^ 2))
+        act_w_std = sqrt.(max.(batched_mul(wσ² .^ 2, x .^ 2), 1f-6))
+        if any(isnan, act_w_std) || any(isinf, act_w)
+            @show act_w_std
+            @show act_w
+            @show l.w_μ
+            @show x
+            Flux.stop()
+        end
 
         # println(size(act_w), size(act_w_std), size(wϵ))
         act_w_out = act_w .+ act_w_std .* wϵ
-        act_b_out = l.b_μ .+ bσ² .* bϵ
+        act_b_out = l.b_μ .+ bσ² .^ 2 .* bϵ
 
         # w = muladd.(l.w_μ, wϵ, wσ²)
         # b = muladd.(l.b_μ, bϵ, bσ²)
@@ -248,7 +255,7 @@ end
 # ----- Spectral stein gradient estimator ----- #
 
 function rbf_kernel(x1::AbstractArray, x2::AbstractArray, lengthscale)
-    rb = -sum((x1 .- x2) .^ 2 ./ (2 .* lengthscale .^ 2 .+ 1e-6); dims=3)  ## SLOW
[…]

### 2022-02-17 src/utils/gym.jl

@@ -40,9 +40,8 @@ function GymEnv(name::String; seed::Union{Int, Nothing}=nothing)
         act_space,
         PyNULL(),
     )
-    env = discrete2standard_discrete(env)
     reset!(env) # reset immediately to init env.state
-    env
+    discrete2standard_discrete(env)
 end
 
 Base.nameof(env::GymEnv) = env.pyenv.__class__.__name__

### 2022-02-17 src/utils/utils.jl

@@ -1,6 +1,6 @@
 export stop, CenteredRMSProp
 
-const ϵ = 1e-8
+const ϵ = 1f-6
 
 stop(text="Stop.") = throw(StopException(text))
 

### 2022-03-04 scripts/RLExp_BDQN_Atari.jl
TEMPORARY DEPLOY COMMIT

@@ -1,201 +1,0 @@
-using Conda
-using CUDA
-using DrWatson
-using Flux
-using Flux: mse, logitcrossentropy
-using Images
-using Logging
-using RLExp
-using Random
-using ReinforcementLearning
-using Setfield
-using Statistics
-using Wandb
-
-function RL.Experiment(
-    ::Val{:RLExp},
-    ::Val{:BDQN},
-    ::Val{:Atari},
-    name::AbstractString;
-    lr::Real = 0.0000625,
-    bz::Int = 32,
-    tuf::Int = 8_000,
-    seed = nothing
-)
-    device = gpu
-
-    """
-    SEEDS
-    """
-    rng = Random.GLOBAL_RNG
-    Random.seed!(rng, seed)
-    device_rng = CUDA.functional() ? CUDA.CURAND.RNG() : rng
-    Random.seed!(device_rng, isnothing(seed) ? nothing : hash(seed + 1))
-
-    """
-    SET UP LOGGING
-    """
-    simulation = @ntuple name lr bz tuf seed
-    lg = WandbLogger(project = "RLExp", name=savename(simulation))
-    save_dir = datadir("sim", "BDQN", savename(simulation, "jld2"))
-
-    """
-    SET UP ENVIRONMENT
-    """
-    N_FRAMES = 4
-    STATE_SIZE = (84, 84)
-    env = atari_env_factory(
-        name,
-        STATE_SIZE,
-        N_FRAMES;
-        seed = isnothing(seed) ? nothing : hash(seed + 1),
-    )
-    N_ACTIONS = length(action_space(env))
-
-    """
-    CREATE MODEL
-    """
-    init = glorot_uniform(rng)
-    create_model() =
-        Chain(
-            x -> x ./ 255,
-            CrossCor((8, 8), N_FRAMES => 32, relu; stride = 4, pad = 2, init = init),
-            CrossCor((4, 4), 32 => 64, relu; stride = 2, pad = 2, init = init),
-            CrossCor((3, 3), 64 => 64, relu; stride = 1, pad = 1, init = init),
-            x -> reshape(x, :, size(x)[end]),
-            NoisyDense(11 * 11 * 64, 512, relu; init_μ = init),
-            Split(NoisyDense(512, N_ACTIONS; init_μ = init),
-                  NoisyDense(512, N_ACTIONS, softplus; init_μ = init))
-        ) |> device
-
-    """
-    CREATE AGENT
-    """
-    agent = Agent(
-        policy = QBasedPolicy(
[…]

### 2022-03-04 scripts/RLExp_DUQNS_Cartpole.jl

@@ -38,7 +38,7 @@ function RL.Experiment(
     """
     SET UP LOGGING
     """
-    lg = WandbLogger(project = "RLExp",
+    lg = WandbLogger(project = "BE",
                      name="DUQNS_CartPole",
                      config = Dict(
                         "B_lr" => 1e-4,
@@ -54,12 +54,12 @@ function RL.Experiment(
                         "updates_per_step" => 1,
                         "λ" => 1,
                         # "prior" => "GaussianPrior(200, 100)",
-                        "prior" => "CartpolePrior(20)",
-                        # "prior" => "FlatPrior()",
+                        # "prior" => "CartpolePrior(1)",
+                        "prior" => "FlatPrior()",
                         "n_samples" => 100,
-                        "η" => 0.95,
+                        "η" => 0.01,
                         "nev" => 6,
-                        "n_eigen_threshold" => 0.98,
+                        "n_eigen_threshold" => 0.99,
                         "is_enable_double_DQN" => true,
                         "traj_capacity" => 1_000_000,
                         "seed" => 1,
@@ -89,7 +89,7 @@ function RL.Experiment(
         """
         # init = glorot_uniform(rng)
         init(dims...) = (2 .* rand(dims...) .- 1) ./ Float32(sqrt(dims[end]))
-        init_σ(dims...) = fill(0.05f0 / Float32(sqrt(dims[end])), dims)
+        init_σ(dims...) = fill(0.4f0 / Float32(sqrt(dims[end])), dims)
 
 
         # B_model = Chain(
@@ -102,17 +102,11 @@ function RL.Experiment(
         # ) |> gpu
 
         B_model = Chain(
+            NoisyDense(ns, 128, leakyrelu; init_μ = init, init_σ = init_σ, rng = device_rng),
+            NoisyDense(128, 128, leakyrelu; init_μ = init, init_σ = init_σ, rng = device_rng),
             Split(
-                Chain(
-                    NoisyDense(ns, 128, relu; init_μ = init, init_σ = init_σ, rng = device_rng),
-                    NoisyDense(128, 128, relu; init_μ = init, init_σ = init_σ, rng = device_rng),
-                    NoisyDense(128, na, relu; init_μ = init, init_σ = init_σ, rng = device_rng),
-                    ),
-                Chain(
-                    NoisyDense(ns, 128, relu; init_μ = init, init_σ = init_σ, rng = device_rng),
[…]

### 2022-03-04 scripts/RLExp_DUQNS_LunarLander.jl

@@ -36,27 +36,28 @@ function RL.Experiment(
     """
     SET UP LOGGING
     """
-    lg = WandbLogger(project = "RLExp",
+    lg = WandbLogger(project = "BE",
                      name="DUQNS_LunarLander",
                      config = Dict(
-                        "B_lr" => 1e-2,
+                        "B_lr" => 1e-3,
                         "Q_lr" => 1.0,
-                        "B_clip_norm" => 10.0,
-                        "B_update_freq" => 1,
+                        "B_clip_norm" => 100.0,
+                        "B_update_freq" => 4,
                         "Q_update_freq" => 1_000,
                         "B_opt" => "ADAM",
                         "gamma" => 0.99f0,
                         "update_horizon" => 1,
                         "batch_size" => 32,
-                        "min_replay_history" => 10_000,
+                        "min_replay_history" => 32,
                         "updates_per_step" => 1,
                         "λ" => 1.0,
                         # "prior" => "GaussianPrior(0, 10)",
-                        "prior" => "LunarLanderPrior(50)",
-                        # "prior" => "FlatPrior()",
+                        # "prior" => "LunarLanderPrior(50)",
+                        "prior" => "FlatPrior()",
                         "n_samples" => 100,
-                        "η" => 0.95,
+                        "η" => 0.01,
                         "nev" => 6,
+                        "n_eigen_threshold" => 0.99,
                         "is_enable_double_DQN" => true,
                         "traj_capacity" => 1_000_000,
                         "seed" => 1,
@@ -87,7 +88,7 @@ function RL.Experiment(
     # init = glorot_uniform(rng)
     init(a, b) = (2 .* rand(rng, Float32, a, b) .- 1) ./ Float32(sqrt(b))
     # init_σ(dims...) = (2 .* rand(rng, Float32, dims) .- 1) ./ Float32(sqrt(dims[end]))
-    init_σ(dims...) = fill(0.05f0 / Float32(sqrt(dims[end])), dims)
+    init_σ(dims...) = fill(0.4f0 / Float32(sqrt(dims[end])), dims)
 
 
     # B_model = Chain(
@@ -100,19 +101,13 @@ function RL.Experiment(
     # ) |> gpu
 
     B_model = Chain(
-            Split(
-                Chain(
-                    NoisyDense(ns, 128, relu; init_μ = init, init_σ = init_σ, rng = device_rng),
[…]

### 2022-03-04 scripts/RLExp_FAC_Cartpole.jl

@@ -1,0 +1,121 @@
+using Base.Iterators: tail
+using BSON: @load, @save
+using CUDA
+using Dates: now
+using Distributions: Uniform, Product
+using DrWatson
+using Flux
+using Flux: Optimiser
+using Flux.Losses
+using Logging
+using RLExp
+using Random
+using ReinforcementLearning
+using Setfield
+using StableRNGs
+using Statistics
+using Wandb
+
+function RL.Experiment(
+    ::Val{:RLExp},
+    ::Val{:FAC},
+    ::Val{:Cartpole},
+    name;
+    save_dir = nothing,
+    seed = 123,
+)
+    lg = WandbLogger(project = "FAC",
+    name="CartPole",
+    )
+    save_dir = datadir("sims", "FAC", "CartPole", "$(now())")
+    mkpath(save_dir)
+
+    rng = StableRNG(seed)
+    N_ENV = 16
+    UPDATE_FREQ = 10
+    N_EVAL = 1_000
+    init(a, b) = (2 .* rand(a, b) .- 1) ./ sqrt(b)
+    init_σ(dims...) = fill(0.05f0 / Float32(sqrt(dims[end])), dims)
+    env = MultiThreadEnv([
+        CartPoleEnv(; T = Float32, rng = StableRNG(hash(seed + i))) for i in 1:N_ENV
+    ])
+    ns, na = length(state(env[1])), length(action_space(env[1]))
+    RLBase.reset!(env, is_force = true)
+    agent = Agent(
+        policy = QBasedPolicy(
+            learner = FACLearner(
+                approximator = ActorCritic(
+                    actor = NeuralNetworkApproximator(
+                        model = Chain(
+                            Dense(ns, 256, relu; init = glorot_uniform(rng)),
+                            Dense(256, na; init = glorot_uniform(rng)),
+                        ),
+                        optimizer = ADAM(1e-3),
+                    ),
+                    critic = NeuralNetworkApproximator(
+                        model = Chain(
+                            Dense(ns, 256, relu; init = glorot_uniform(rng)),
+                            Dense(256, 1; init = glorot_uniform(rng)),
+                        ),
+                        optimizer = ADAM(1e-3),
+                    ),
+                ) |> gpu,
+                γ = 0.99f0,
+                λ = 0.97f0,
+                actor_loss_weight = 1.0f0,
+                critic_loss_weight = 0.5f0,
+                entropy_loss_weight = 0.001f0,
+                update_freq = UPDATE_FREQ,
+            ),
[…]

### 2022-03-04 scripts/RLExp_NDQN_Atari.jl

@@ -1,227 +1,0 @@
-using Conda
-using CUDA
-using DrWatson
-using Flux
-using Flux: mse, logitcrossentropy
-using Images
-using Logging
-using RLExp
-using Random
-using ReinforcementLearning
-using Setfield
-using Statistics
-using Wandb
-using Zygote
-using Flux: glorot_uniform, unsqueeze
-using NNlib: softplus
-
-struct NoisyDense3
-    w_μ::AbstractMatrix
-    w_ρ::AbstractMatrix
-    b_μ::AbstractVector
-    b_ρ::AbstractVector
-    f::Any
-end
-
-function NoisyDense3(
-    in, out, f=identity; init_μ=glorot_uniform(), init_σ=(dims...) -> fill(0.0017f0, dims)
-)
-    return NoisyDense3(
-        init_μ(out, in),
-        log.(exp.(init_σ(out, in)) .- 1),
-        init_μ(out),
-        log.(exp.(init_σ(out)) .- 1),
-        f,
-    )
-end
-
-Flux.@functor NoisyDense3
-
-function (l::NoisyDense3)(x)
-    x = ndims(x) == 2 ? unsqueeze(x, 3) : x
-    tmp_x = reshape(x, size(x, 1), :)
-    μ = l.w_μ * tmp_x .+ l.b_μ
-    σ² = softplus.(l.w_ρ) * tmp_x .^ 2 .+ softplus.(l.b_ρ)
-    ϵ = Zygote.@ignore randn!(similar(μ, size(μ, 1), 1))
-    μ = reshape(μ, size(μ, 1), size(x, 2), :)
-    σ² = reshape(σ², size(μ, 1), size(x, 2), :)
-    return y = l.f.(μ .+ ϵ .* sqrt.(σ²))
-end
-
-function RL.Experiment(
-    ::Val{:RLExp},
-    ::Val{:NDQN},
-    ::Val{:Atari},
-    name::AbstractString;
-    save_dir = nothing,
-    seed = nothing
-)
-    """
-    SEEDS
-    """
-    rng = Random.GLOBAL_RNG
-    Random.seed!(rng, seed)
-    device_rng = CUDA.functional() ? CUDA.CURAND.RNG() : device_rng
-    Random.seed!(device_rng, isnothing(seed) ? nothing : hash(seed + 1))
-
-    """
-    SET UP LOGGING
-    """
-    simulation = @ntuple name
-    lg = WandbLogger(project = "RLExp", name=savename(simulation))
[…]

### 2022-03-04 scripts/RLExp_Noisy_Cartpole.jl

@@ -26,7 +26,7 @@ function RL.Experiment(
     """
     SET UP LOGGING
     """
-    lg = WandbLogger(project = "RLExp",
+    lg = WandbLogger(project = "BE",
                     name="Noisy_CartPole",
                     config = Dict(
                         "B_lr" => 1e-4,
@@ -39,13 +39,7 @@ function RL.Experiment(
                         "update_horizon" => 1,
                         "batch_size" => 32,
                         "min_replay_history" => 32,
-                        "updates_per_step" => 1,
-                        "λ" => 1.0,
                         # "prior" => "GaussianPrior(0, 10)",
-                        "prior" => "FlatPrior()",
-                        "n_samples" => 100,
-                        "η" => 0.01,
-                        "nev" => 10,
                         "is_enable_double_DQN" => true,
                         "traj_capacity" => 1_000_000,
                         "seed" => 1,
@@ -74,7 +68,7 @@ function RL.Experiment(
     """
     # init = glorot_uniform(rng)
     init(a, b) = (2 .* rand(a, b) .- 1) ./ sqrt(b)
-    init_σ(dims...) = fill(0.05f0 / Float32(sqrt(dims[end])), dims)
+    init_σ(dims...) = fill(0.4f0 / Float32(sqrt(dims[end])), dims)
 
 
     agent = Agent(

### 2022-03-04 scripts/RLExp_Noisy_LunarLander.jl

@@ -16,58 +16,58 @@ using Statistics
 using Wandb
 
 function RL.Experiment(
-    ::Val{:RLExp},
-    ::Val{:Noisy},
-    ::Val{:MountainCar},
-    name,
-    restore=nothing,
-   )
-
-   """
-   SET UP LOGGING
-   """
-   lg = WandbLogger(project = "RLExp",
-                    name="Noisy_MountainCar",
+::Val{:RLExp},
+::Val{:Noisy},
+::Val{:LunarLander},
+name,
+restore=nothing,
+)
+    """
+    SET UP LOGGING
+    """
+    lg = WandbLogger(project = "RLExp",
+                    name="Noisy_LunarLander",
                     config = Dict(
-                       "B_lr" => 1e-3,
-                       "Q_lr" => 1.0,
-                       "B_clip_norm" => 1000.0,
-                       "B_update_freq" => 1,
-                       "Q_update_freq" => 1000,
-                       "B_opt" => "ADAM",
-                       "gamma" => 0.99f0,
-                       "update_horizon" => 1,
-                       "batch_size" => 32,
-                       "min_replay_history" => 10_000,
-                       "updates_per_step" => 1,
-                       "is_enable_double_DQN" => true,
-                       "traj_capacity" => 1_000_000,
-                       "seed" => 1,
+                        "B_lr" => 1e-3,
+                        "Q_lr" => 1.0,
+                        "B_clip_norm" => 100.0,
+                        "B_update_freq" => 4,
+                        "Q_update_freq" => 1_000,
+                        "B_opt" => "ADAM",
+                        "gamma" => 0.99f0,
+                        "update_horizon" => 1,
+                        "batch_size" => 32,
+                        "min_replay_history" => 32,
+                        "updates_per_step" => 1,
+                        "is_enable_double_DQN" => true,
+                        "traj_capacity" => 1_000_000,
+                        "seed" => 1,
                     ),
-   )
-   save_dir = datadir("sims", "Noisy", "MountainCar", "$(now())")
+    )
+    save_dir = datadir("sims", "Noisy", "LunarLander", "$(now())")
 
-   """
-   SEEDS
-   """
-   seed = get_config(lg, "seed")
-   rng = MersenneTwister()
[…]

### 2022-03-04 scripts/run_experiment.jl

@@ -25,8 +25,10 @@ include("RLExp_DUQNS_Atari.jl")
 # games = ["breakout"]
 # experiments = [E`RLExp_BDQN_Atari($(game))` for game in games]
 # experiments = [E`RLExp_Noisy_Atari(pong)`]
-experiments = [E`RLExp_DUQNS_Atari(pong)`]
+experiments = [E`RLExp_DUQNS_Cartpole()`,
+               E`RLExp_DUQNS_Cartpole()`,
+               E`RLExp_DUQNS_Cartpole()`]
 # experiments = [E`Dopamine_DQN_Atari(pong)`]
 
-# pmap(run, experiments)
-run(experiments[1])
+pmap(run, experiments)
+# run(experiments[1])

### 2022-03-04 src/RLExp.jl

@@ -7,6 +7,7 @@ export ResizeImage
 export get_screen
 export DUQNLearner, FlatPrior, GeneralPrior, GaussianPrior, CartpolePrior, AcrobotPrior
 export DUQNSLearner
+export FACLearner
 export stop, CenteredRMSProp
 export MountainCarPrior, LunarLanderPrior
 export AcrobotEnv, GymEnv
@@ -34,9 +35,8 @@ include("utils/acrobot.jl")
 include("utils/priors.jl")
 include("utils/utils.jl")
 include("algorithms/common.jl")
-include("algorithms/BDQN.jl")
-include("algorithms/GDQN.jl")
 include("algorithms/DUQN.jl")
 include("algorithms/DUQNS.jl")
+include("algorithms/FAC.jl")
 
 end

### 2022-03-04 src/algorithms/BDQN.jl

@@ -1,192 +1,0 @@
-export BDQNLearner
-import ReinforcementLearning.RLBase.update!
-
-using CUDA: randn!
-using Random: randn!
-using StatsBase: sample
-
-mutable struct BDQNLearner{
-    Tq<:AbstractApproximator,
-    Tt<:AbstractApproximator,
-    Tv<:AbstractApproximator,
-    Tf,
-    R<:AbstractRNG,
-} <: AbstractLearner
-    approximator::Tq
-    target_approximator::Tt
-    variance_approximator::Tv
-    loss_func::Tf
-    min_replay_history::Int
-    update_freq::Int
-    update_step::Int
-    target_update_freq::Int
-    sampler::NStepBatchSampler
-    rng::R
-    sse::SpectralSteinEstimator
-    injected_noise::Float32
-    n_samples::Int
-    is_enable_double_DQN::Bool
-    # for logging
-    loss::Float32
-    kl::Float32
-    q_var::Float32
-    nll::Float32
-    σ::Float32
-end
-
-function BDQNLearner(;
-    approximator::Tq,
-    target_approximator::Tt,
-    variance_approximator::Tv,
-    loss_func::Tf,
-    stack_size::Union{Int,Nothing} = nothing,
-    γ::Float32 = 0.99f0,
-    batch_size::Int = 32,
-    update_horizon::Int = 1,
-    min_replay_history::Int = 32,
-    update_freq::Int = 1,
-    target_update_freq::Int = 100,
-    traces = SARTS,
-    update_step::Int = 0,
-    injected_noise::Float32 = 0.01f0,
-    n_samples::Int = 100,
-    η::Float32 = 0.05f0,
-    n_eigen_threshold::Float32 = 0.99f0,
-    rng = Random.GLOBAL_RNG,
-    is_enable_double_DQN::Bool = true,
-) where {Tq,Tt,Tv,Tf}
-    copyto!(approximator, target_approximator)
-    sampler = NStepBatchSampler{traces}(;
-        γ = γ,
-        n = update_horizon,
-        stack_size = stack_size,
-        batch_size = batch_size,
-    )
-    return BDQNLearner(
-        approximator,
-        target_approximator,
-        variance_approximator,
-        loss_func,
-        min_replay_history,
-        update_freq,
-        update_step,
-        target_update_freq,
-        sampler,
-        rng,
[…]

### 2022-03-04 src/algorithms/DUQNS.jl

@@ -39,7 +39,7 @@ function DUQNSLearner(;
     Q_approximator::Tt,
     Q_lr::Real = 0.01f0,
     prior::AbstractPrior = FlatPrior(),
-    λ::Union{Real, Nothing} = 1.0,
+    λ::Union{Real, Nothing} = 1,
     stack_size::Union{Int, Nothing} = nothing,
     γ::Real = 0.99f0,
     batch_size::Int = 32,
@@ -78,7 +78,7 @@ function DUQNSLearner(;
         update_step,
         sampler,
         rng,
-        SpectralSteinEstimator(Float32(η), nev, 0.99),
+        SpectralSteinEstimator(Float32(η), nev, 0.99f0),
         Float32(injected_noise),
         n_samples,
         is_enable_double_DQN,
@@ -144,16 +144,13 @@ function RLBase.update!(learner::DUQNSLearner, batch::NamedTuple)
 
     s, a, r, t, s′ = (send_to_device(D, batch[x]) for x in SARTS)
     a = CartesianIndex.(a, 1:batch_size)
-    seed = hash(rand())
-    rng_B = Random.MersenneTwister(seed)
-    rng_Q = Random.MersenneTwister(seed + 1)
 
     if is_enable_double_DQN
         # q_values = B(s′, n_samples, rng = rng_B)
         q_values = B(s′, n_samples)
         # rng_B = Random.MersenneTwister(seed)
     else
-        q_values = Q(s′, n_samples, rng = rng_Q)
+        q_values = Q(s′, n_samples)
     end
 
     if haskey(batch, :next_legal_actions_mask)
@@ -163,7 +160,7 @@ function RLBase.update!(learner::DUQNSLearner, batch::NamedTuple)
 
     if is_enable_double_DQN
         selected_actions = dropdims(argmax(q_values; dims = 1); dims = 1)
-        q′ = Q(s′, n_samples; rng = rng_Q)[selected_actions, :]
+        q′ = Q(s′, n_samples)[selected_actions, :]
         q′ = dropdims(q′, dims=ndims(q′))
     else
         q′ = dropdims(maximum(q_values; dims = 1); dims = 1)
@@ -171,14 +168,12 @@ function RLBase.update!(learner::DUQNSLearner, batch::NamedTuple)
     G = r .+ γ^n .* (1 .- t) .* q′
 
     gs = gradient(params(B)) do
[…]

### 2022-03-04 src/algorithms/common.jl

@@ -60,11 +60,11 @@ Flux.@functor NoisyDense
 #     return y = l.f.(μ .+ ϵ .* sqrt.(σ²))
 # end
 
-function make_noise_sqrt(dims...)
-    noise = CUDA.randn(Float32, dims...)
-    # noise .= copysign.(sqrt.(abs.(noise)), noise)
-    return noise
-end
+# function make_noise_sqrt(dims...)
+#     noise = CUDA.randn(Float32, dims...)
+#     noise .= copysign.(sqrt.(abs.(noise)), noise)
+#     return noise
+# end
 
 # function (l::NoisyDense)(x, num_samples::Union{Int, Nothing}=nothing; rng::Union{AbstractRNG, Nothing}=nothing)
 #     rng = rng === nothing ? l.rng : rng
@@ -93,60 +93,31 @@ end
 
 function (l::NoisyDense)(x, num_samples::Union{Int, Nothing}=nothing; rng::Union{AbstractRNG, Nothing}=nothing)
     rng = rng === nothing ? l.rng : rng
-    x = ndims(x) == 2 ? unsqueeze(x, 3) : x
     wσ² = l.w_ρ
     bσ² = l.b_ρ
 
     if num_samples === nothing
         tmp_x = reshape(x, size(x, 1), :)
-        ϵ_1 = Zygote.@ignore make_noise_sqrt(size(l.w_μ, 1), 1)
-        # ϵ_2 = Zygote.@ignore make_noise_sqrt(1, size(x, 2))
-        wϵ = ϵ_1
-        # wϵ = Zygote.@ignore ϵ_1 .* ϵ_2
-        bϵ = Zygote.@ignore make_noise_sqrt(size(bσ², 1), 1)
+        ϵ = Zygote.@ignore CUDA.randn(Float32,size(bσ², 1), 1)
 
         act_w = l.w_μ * tmp_x
         act_w_std = sqrt.(max.((wσ² .^ 2) * (tmp_x .^ 2), 1f-6))
 
-        # println(size(act_w), size(act_w_std), size(wϵ))
-        act_w_out = act_w .+ act_w_std .* wϵ
-        act_b_out = l.b_μ .+ bσ² .^ 2 .* bϵ
-        
-        # wϵ .= wϵ .* wσ² .+ l.w_μ
-        # bϵ .= bϵ .* bσ² .+ l.b_μ
+        mean_out = act_w .+ l.b_μ 
[…]

### 2022-07-18 papers/CDRL/sample_paper.tex
TEMPORARY DEPLOY COMMIT

\documentclass[twoside]{article}
%\usepackage{aistats2022}
% If your paper is accepted, change the options for the package
% aistats2022 as follows:
%
\usepackage[accepted]{aistats2022}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

% If you set papersize explicitly, activate the following three lines:
\special{papersize = 8.5in, 11in}
\setlength{\pdfpageheight}{11in}
\setlength{\pdfpagewidth}{8.5in}
\input{math.tex}
% If you use natbib package, activate the following three lines:
\usepackage[round]{natbib}
\renewcommand{\bibname}{References}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

% If you use BibTeX in apalike style, activate the following line:
\bibliographystyle{apalike}

\begin{document}

\twocolumn[

\aistatstitle{Normalizing Flows for Continous Distributional Reinforcement Learning}

\aistatsauthor{ Ludvig Killingberg}

\aistatsaddress{ Norwegian University of Science and Technology } ]

% \begin{abstract}
%   The Abstract paragraph should be indented 0.25 inch (1.5 picas) on
%   both left and right-hand margins. Use 10~point type, with a vertical
%   spacing of 11~points. The \textbf{Abstract} heading must be centered,
%   bold, and in point size 12. Two line spaces precede the
%   Abstract. The Abstract must be limited to one paragraph.
% \end{abstract}

\begin{abstract}
  The Abstract paragraph should be indented 0.25 inch (1.5 picas) on
  both left and right-hand margins. Use 10~point type, with a vertical
  spacing of 11~points. The \textbf{Abstract} heading must be centered,
  bold, and in point size 12. Two line spaces precede the
  Abstract. The Abstract must be limited to one paragraph.
\end{abstract}

\section{Introduction}

% The submission versions of the papers are limited to 8 pages,
% plus any additional pages needed for references (and, optionally, supplementary
% material; see more details below). The camera-ready versions of the accepted
% papers are limited to 9 pages plus references and supplement.

% Papers are in 2 columns with the overall line width of 6.75~inches (41~picas).
% Each column is 3.25~inches wide (19.5~picas).  The space
% between the columns is .25~inches wide (1.5~picas).  The left margin is 0.88~inches (5.28~picas).
% Use 10~point type with a vertical spacing of
% 11~points. The font type must be Computer Modern.
% Please use US Letter size paper and not A4.

% Paper title is 16~point, caps/lc, bold, centered between 2~horizontal rules.
% Top rule is 4~points thick and bottom rule is 1~point thick.
% Allow 1/4~inch space above and below title to rules.

% Author descriptions are center-justified, initial caps.  The lead
% author is to be listed first (left-most), and the Co-authors are set
% to follow.  If up to three authors, use a single row of author
% descriptions, each one center-justified, and all set side by side;
% with more authors or unusually long names or institutions, use more
% rows.

% Use one-half line space between paragraphs, with no indent.

As an agent interacts with an environment, the environment and the agent's
policy interjects randomness into the return. Q-learning algorithms aim to
capture the mean of the (discounted) cumulative reward from interracting
with the environment. Distributional reinforcement learning (RL) in contrast 
considers the randomness in the reward and aims to capture the following random
variable. In contrast to Q-learning algorithms, distributional reinforcement
learning algorithms aim to model distribution of the discounted cumulative
reward.

The difference in distributional reinforcement learning algorithms is mainly in
how the distribution is modeled.

\section{Background}

We consider the standard RL setting, where interaction between agent and
environment is modelled as a Markov Decision Process
\((\X, \A, R, P, \gamma)\)~\citep{puterman94}, where \(\X\) and \(\A\) denote
the state and action space respectively, \(R\) denotes the state-action
dependent reward function, \(P(\cdot \vert x, a)\) denotes the transition
probabilities, and \(\gamma \in [0,1]\) is the discount factor. A policy
\(\pi(\cdot \vert x)\) maps states to distributions over actions.

For an agent following policy \(\pi\), the return \(Z^\pi\),
or \emph{value distribution}~\citep{bellmare17}, is the sum of
discounted rewards along the agents trajectory

\begin{equation}
  Z^\pi(x, a) \defeq \sum_{t=0}^\infty{\gamma^t R(x_t,a_t)}
\end{equation}

\noindent
starting in state \(x_0 = x\), with \(a_0 = a\), \(a_t \sim \pi(\cdot \vert
x_t)\), and \(x_t \sim P(\cdot \vert x_{t-1}, a_{t-1})\).
The objective in RL can be summarized as finding the optimal policy \(\pi^*\)
that maximizes the expected return \(Q^\pi(x, a) \defeq \E{P, R, \pi}{Z^\pi(x, a)}
\). The most common approach is to find the unique fixed point of the Bellman
optimality operator~\citep{bellman57}

\begin{equation}
  \T Q^*(x, a) \defeq \E{}{R(x, a)} + \gamma \E{P}{\max_{a^\prime \in \A}
  Q^*(x^\prime, a^\prime)}.
\end{equation}

To approximate \(Q^*\), now usually modeled with a neural network \(Q_\theta\),
Q-learning~\citep{watkins89} iteratiely improves the estimate by minimizing the
squared temporal difference (TD) error

\begin{equation}
  \delta^2_t = \left[ r_t + \gamma \max_{a^\prime \in \A}
  Q_\theta(x_t, a^\prime) - Q_\theta(x_t, a_t) \right]^2
\end{equation}

for samples \((x_t, a_t, r_t, x_{t+1})\) in trajectory \(T\), observed as the
agent interracts with the environment according to an \(\epsilon\)-greedy policy
over \(Q_\theta\).

\subsection{Distributional Reinforcement Learning}

Rather than reducing the optimization problem to the expected return,
distributional reinforcement learning considers the full distribution of the 
random variable \(Z^\pi\). Similar to the Bellman operator for the scalar
\(Q^\pi(x,a)\), we have a distributional Bellman operator

\begin{equation}
  \T Z^\pi(x, a) \distdefeq R(x, a) + \gamma Z^\pi(X^\prime, A^\prime)
\end{equation}

\noindent
where \(A \eqdist B\) denotes equality in distribution, i.e. random variable
\(A\) and \(B\) have the same distribution functions.

\subsubsection{Quantile Regression}

\subsection{Variational Inference}

% Third level headings are flush left, initial caps, bold, and in point
% size 10. Use one line space before the third level heading and one-half line
% space after the third level heading.

Lately, techniques for modelling complex distributions have have seen a surge
in popularity, particularily for generating realistic images. Given a dataset
\(\data\), we would like to find the distribution of parameters
\(p(\vtheta \vert \data)\). This is known as the posterior distribution. Using
full Bayesian inference we would calculate the posterior using Baye's theorem,
\begin{equation}
  p(\vtheta \vert \data) = \frac{p(\data \vert \vtheta)p(\vtheta)}{
    \int p(\data \vert \vtheta) p(\vtheta) d\vtheta}.
\end{equation}

Often, \(p\) is modelled by a neural network, which makes the denominator
intractable to compute. Variational inference provides an alternative to
computing the full posterior, by approximating \(p(\vtheta \vert \data)\) with
a distribution \(q(\vtheta)\) from a family of distributions \(\Qfamily\). We
do this by minimizing some measure of difference between the distributions. The
KL-divergence is a common choice since it has some useful properties we will
see later,
\begin{equation*}
  \KL{q(\vtheta)}{p(\vtheta \vert \data)} =
  \E{q(\vtheta)}{\log \frac{q(\vtheta)}{p(\vtheta \vert \data)}}.
\end{equation*}

Although the is not a metric (it is not symmetric, and does not obey the
triangle inequality), it is non-negative, and zero only when
\(q(\vtheta) = p(\vtheta \vert \data)\). Finding the approximation to the
posterior using the KL-divergence means solving the optimization problem,
\begin{equation*}
  q^* = \argmin_{q \in \Qfamily} \KL{q(\vtheta)}{p(\vtheta \vert \data)}.
\end{equation*}

Unfortunately, this is still a hard optimization problem. We can, however,
manipulate the KL-term to make the optimization problem tractable.
\begin{align*}
  &\KL{q(\vtheta)}{p(\vtheta \vert \data)} =
  \E{q(\vtheta)}{\log \frac{q(\vtheta)}{p(\vtheta \vert \data)}}\\
  &= \E{q(\vtheta)}{\log q(\vtheta)} - \E{q(\vtheta)}{\log p(\vtheta \vert \data)}\\
  &= \E{q(\vtheta)}{\log q(\vtheta)} - \E{q(\vtheta)}{\log
  \frac{p(\vtheta, \data)}{p(\data)}}\\
  &= \E{q(\vtheta)}{\log q(\vtheta)} - \E{q(\vtheta)}{\log p(\vtheta, \data)} +
  \E{q(\vtheta)}{\log p(\data)}\\
  &= \E{q(\vtheta)}{\log q(\vtheta)} - \E{q(\vtheta)}{\log p(\vtheta, \data)} +
  \log p(\data)\\
\end{align*}
This shows that minimizing the KL-divergence is the same as maximizing the
evidence lower bound (\textbf{ELBO}),
\begin{equation*}
  \mathrm{ELBO}(q; \vtheta, \data) = \E{q(\vtheta)}{\log p(\vtheta, \data)} -
  \E{q(\vtheta)}{\log q(\vtheta)}.
\end{equation*}

How close the approximate distribution, \(q(\vtheta))\), gets to the posterior
\(p(\vtheta \vert \data)\) depends on the family of distributions \(\Qfamily\).
We need to be able to quickly evaluate \(\E{q(\vtheta)}{p(\vtheta, \data)}\) and
\(\E{q(\vtheta)}{q(\vtheta}\), but we also want flexible, complex distributions,
such that \(q^* \in \Qfamily\) is close to \(p(\vtheta \vert \data)\). Most
early application of variational inference focused on mean-field for efficent
inference. Assuming factorization in the distributional family,
\begin{equation}
  \Qfamily =
  \left\{ q(\vtheta) \middle\vert \prod_{\theta_i \in \vtheta}{q(\theta_i)} \right\},
\end{equation}
is a strong restriction. It is unlikely that \(p(\vtheta \vert \data)\) will 
factorize, and thus not be close to any \(q \in \Qfamily\). The nature of the
reverse KL-divergence will mean that the approximate posterior always
underestimates the variance of the true posterior.

\subsubsection{Normalizing Flows}
Normalizing flows is a method of transforming simple distributions into more
complex ones using parameterized functions. The change of variables formula is
used to construct a series of invertible transformations, where the probability
of the transformed variables can still be evaluated.

Let \(\bm{Z}\) be a random variable defined over the support \(S \subseteq \R^n\)
and a continous probability density function \(q(\rvz)\). Further, let \(v\) be
a continous, differentiable and invertible function from \(S\) to
\(T \in \R^n\), if we let \(\bm{Z}^\prime = v(\bm{Z})\), then the probability
function \(q(\rvz^\prime)\) of \(\bm{Z}^\prime\) is given by
\begin{align}
  q(\rvz^\prime) &= q(\rvz) \left\lvert \det \left( \frac{\partial \rvz}{
    \partial \rvz^\prime} \right) \right\rvert \nonumber\\
  &= q(v^{-1}(\rvz^\prime)) \left\lvert \det \left( \frac{\partial}{\partial
  \rvz^\prime} v^{-1}(\rvz^\prime) \right) \right\rvert
  \label{eq:change_var_form1}\\
  &= q(v^{-1}(\rvz^\prime)) \left\lvert \det \left( \frac{\partial}{\partial
  \rvz^\prime} v(\rvz^\prime) \right) \right\rvert^{-1}
  \label{eq:change_var_form2}
\end{align}

Normalizing flows takes advantage of this change of variables formula and create
a family of parameterized invertible transformation \(V\) with an easy to 
compute jacobian. These transformations can be chained together to (usually)
create an arbitrarily complex transformation.
\begin{equation}
  \rvz_K = v_K \circ \dots \circ v_2 \circ v_1(\rvz_0),
\end{equation}
\begin{equation}
  \log q(\rvz_K) = \log q(\rvz_0) - \sum_{k=1}^K{\log \left\lvert \det
  \frac{\partial v_k}{\partial \rvz_k} \right\rvert}
\end{equation}

The \emph{planar flow} is a normalizing flow defined by a series of
transformations that expand and contract the distribution perpendicular to a
hyperplane \(\rvw^\top \rvz  + b\). For a smooth element-wise non-linear
function \(h(\cdot)\), with derivative \(h^\prime(\cdot)\), the planar flow is
defined as,

\begin{equation}
  v(\rvz) = \rvz + \rvu h(\rvw \rvz + b),
\end{equation}
\begin{equation}
  \left\lvert \det \frac{\partial v}{\partial \rvz} \right\rvert =
  \left\lvert 1 + \rvu^\top h^\prime(\rvw^\top \rvz + b) \rvw \right\rvert,
\end{equation}

\noindent
where \(\rvu\), \(\rvw\), and \(b\) are free parameters.
\(h(z) = \tanh(z)\) is a common choice. For this choice of non-linearity,
\(v\) is invertible if-and-only-if \(\rvw^\top u \geq -1\). To satisfy this
condition, \citet{rezende15} suggest starting with an arbitrary vector
\(\rvu\) and modify its component parallel to \(\rvw\), resulting in a new
vector \(\hat{\rvu}\) that satisfies \(\rvw^\top \hat{\rvu} \leq -1\).

\begin{equation*}
  m(x) = -1 + \log{(1 + e^x)}
\end{equation*}
\begin{equation}
  \hat{\rvu}(\rvu, \rvw) = \rvu + \left[m(\rvw^\top \rvu) -
  \rvw^\top \rvu \right] \frac{\rvw}{\lVert\rvw\rVert^2}
\end{equation}

\section{Our Algorithm}

We propose to use conditional normalizing flows to model the value distribution
\(Z^\pi\) with a continous estimate.

\begin{figure}[ht]
\vspace{.3in}
% \centerline{\fbox{This figure intentionally left non-blank}}
\includegraphics[width=\columnwidth]{qdistr_6100.png}
\vspace{.3in}
\caption{Learned \(Z^\pi\)-distribution during an episode in Breakout.}
\end{figure}

% \paragraph{Fourth Level Heading}

% Fourth level headings must be flush left, initial caps, bold, and
% Roman type.  Use one line space before the fourth level heading, and
% place the section text immediately after the heading with no line
% break, but an 11 point horizontal space.

%%%
% \subsection{Citations, Figure, References}

% \subsubsection{Citations in Text}

% Citations within the text should include the author's last name and
% year, e.g., (Cheesman, 1985). 
% %Apart from including the author's last name and year, citations can follow any style, as long as the style is consistent throughout the paper.  
% Be sure that the sentence reads
% correctly if the citation is deleted: e.g., instead of ``As described
% by (Cheesman, 1985), we first frobulate the widgets,'' write ``As
% described by Cheesman (1985), we first frobulate the widgets.''

% The references listed at the end of the paper can follow any style as long as it is used consistently.

%Be sure to avoid
%accidentally disclosing author identities through citations.

% \subsubsection{Footnotes}

% Indicate footnotes with a number\footnote{Sample of the first
%   footnote.} in the text. Use 8 point type for footnotes. Place the
% footnotes at the bottom of the column in which their markers appear,
% continuing to the next column if required. Precede the footnote
% section of a column with a 0.5 point horizontal rule 1~inch (6~picas)
% long.\footnote{Sample of the second footnote.}

% \subsubsection{Figures}

% All artwork must be centered, neat, clean, and legible.  All lines
% should be very dark for purposes of reproduction, and art work should
% not be hand-drawn.  Figures may appear at the top of a column, at the
% top of a page spanning multiple columns, inline within a column, or
% with text wrapped around them, but the figure number and caption
% always appear immediately below the figure.  Leave 2 line spaces
% between the figure and the caption. The figure caption is initial caps
% and each figure should be numbered consecutively.

% Make sure that the figure caption does not get separated from the
% figure. Leave extra white space at the bottom of the page rather than
% splitting the figure and figure caption.
% \begin{figure}[ht]
% \vspace{.3in}
% \centerline{\fbox{This figure intentionally left non-blank}}
% \vspace{.3in}
% \caption{Sample Figure Caption}
% \end{figure}

% \subsubsection{Tables}

% All tables must be centered, neat, clean, and legible. Do not use hand-drawn tables.
% Table number and title always appear above the table.
% See Table~\ref{table}.

% Use one line space before the table title, one line space after the table title,
% and one line space after the table. The table title must be
% initial caps and each table numbered consecutively.

% \begin{table}[ht]
% \caption{Sample Table Title} \label{table}
% \begin{center}
% \begin{tabular}{ll}
% \textbf{PART}  &\textbf{DESCRIPTION} \\
% \hline \\
% Dendrite         &Input terminal \\
% Axon             &Output terminal \\
% Soma             &Cell body (contains cell nucleus) \\
% \end{tabular}
% \end{center}
% \end{table}

% \section{SUPPLEMENTARY MATERIAL}

% If you need to include additional appendices during submission, you can include them in the supplementary material at the end of this file. It can be in either one- or two-column format.

% In addition, you can submit a single file of additional non-textual supplementary material, which should be a ZIP file containing, e.g., code. 
% Note that reviewers are under no obligation to examine your supplementary material.

% \section{SUBMISSION INSTRUCTIONS}

% To submit your paper to AISTATS 2022, please follow these instructions.

% \begin{enumerate}
%     \item Download \texttt{aistats2022.sty}, \texttt{fancyhdr.sty}, and \texttt{sample\_paper.tex} provided in our starter pack. 
%     Please, do not modify the style files as this might result in a formatting violation.

%     \item Use \texttt{sample\_paper.tex} as a starting point.
%     \item Begin your document with
%     \begin{flushleft}
%     \texttt{\textbackslash documentclass[twoside]\{article\}}\\
%     \texttt{\textbackslash usepackage\{aistats2022\}}
%     \end{flushleft}
%     The \texttt{twoside} option for the class article allows the
%     package \texttt{fancyhdr.sty} to include headings for even and odd
%     numbered pages.
%     \item When you are ready to submit the manuscript, compile the latex file to obtain the pdf file.
%     \item Check that the content of your submission, \emph{excluding} references, is limited to \textbf{8 pages}. The number of pages containing references (and, optionally, supplementary material) is not limited. Note that the camera-ready version can have \textbf{9 pages}, see details below.
%     \item (Optional) Upload the ZIP file along with other supplementary material files to the CMT website.
% \end{enumerate}

% \subsection{Camera-ready Papers}

%For the camera-ready paper, if you are using \LaTeX, please make sure
%that you follow these instructions.  
% (If you are not using \LaTeX,
%please make sure to achieve the same effect using your chosen
%typesetting package.)

% If your papers are accepted, you will need to submit the camera-ready version. Please make sure that you follow these instructions:
% \begin{enumerate}
%     %\item Download \texttt{fancyhdr.sty} -- the
%     %\texttt{aistats2022.sty} file will make use of it.
%     \item Change the beginning of your document to
%     \begin{flushleft}
%     \texttt{\textbackslash documentclass[twoside]\{article\}}\\
%     \texttt{\textbackslash usepackage[accepted]\{aistats2022\}}
%     \end{flushleft}
%     The option \texttt{accepted} for the package
%     \texttt{aistats2022.sty} will write a copyright notice at the end of
%     the first column of the first page. This option will also print
%     headings for the paper.  For the \emph{even} pages, the title of
%     the paper will be used as heading and for \emph{odd} pages the
%     author names will be used as heading.  If the title of the paper
%     is too long or the number of authors is too large, the style will
%     print a warning message as heading. If this happens additional
%     commands can be used to place as headings shorter versions of the
%     title and the author names. This is explained in the next point.
%     \item  If you get warning messages as described above, then
%     immediately after $\texttt{\textbackslash
%     begin\{document\}}$, write
%     \begin{flushleft}
%     \texttt{\textbackslash runningtitle\{Provide here an alternative
%     shorter version of the title of your paper\}}\\
%     \texttt{\textbackslash runningauthor\{Provide here the surnames of
%     the authors of your paper, all separated by commas\}}
%     \end{flushleft}
%     Note that the text that appears as argument in \texttt{\textbackslash
%       runningtitle} will be printed as a heading in the \emph{even}
%     pages. The text that appears as argument in \texttt{\textbackslash
%       runningauthor} will be printed as a heading in the \emph{odd}
%     pages.  If even the author surnames do not fit, it is acceptable
%     to give a subset of author names followed by ``et al.''

%     %\item Use the file sample\_paper.tex as an example.

%     \item The camera-ready versions of the accepted papers are 9
%       pages, plus any additional pages needed for references (and,
%       optionally, supplementary material).

%     \item If you need to include additional appendices,
%       you can include them in the supplementary
%       material at the end of this file. There is no page limit
%       for the supplementary material.

%     \item Please, do not change the layout given by the above
%       instructions and by the style file.

% \end{enumerate}

% \subsubsection*{Acknowledgements}
% All acknowledgments go at the end of the paper, including thanks to reviewers who gave useful comments, to colleagues who contributed to the ideas, and to funding agencies and corporate sponsors that provided financial support. 
% To preserve the anonymity, please include acknowledgments \emph{only} in the camera-ready papers.

% \subsubsection*{References}

% References follow the acknowledgements.  Use an unnumbered third level
% heading for the references section.  Please use the same font
% size for references as for the body of the paper---remember that
% references do not count against your page length total.

\bibliography{references.bib}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%% SUPPLEMENT (OPTIONAL) %%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \clearpage
% \appendix

% \thispagestyle{empty}

% % For one-column format, uncomment the following:
% \onecolumn \makesupplementtitle
% % For two-column format, uncomment the following:
% %\twocolumn[ \makesupplementtitle ]

% \section{FORMATTING INSTRUCTIONS FOR THE SUPPLEMENTARY MATERIAL}

% Your supplementary material should go here. It may be in one-column or two-column format. To display the supplementary material in two-column format, comment out the line
% \begin{verbatim}
% \onecolumn \makesupplementtitle
% \end{verbatim}
% and uncomment the following line:
% \begin{verbatim}
% \twocolumn[ \makesupplementtitle ]
% \end{verbatim}

% Please submit your paper (including the supplementary material) as a single PDF file. Besides the PDF file, you may submit a single file of additional non-textual supplementary material, which should be a ZIP file containing, e.g., code.

% If you require to upload any video as part of the supplementary material of your camera-ready submission, do not submit it in the ZIP file. Instead, please send us via email the URL containing the video location.

% Note that reviewers are under no obligation to examine your supplementary material.

% \section{MISSING PROOFS}

% The supplementary materials may contain detailed proofs of the results that are missing in the main paper.

% \subsection{Proof of Lemma 3}

% \textit{In this section, we present the detailed proof of Lemma 3 and then [ ... ]}

% \section{ADDITIONAL EXPERIMENTS}

% If you have additional experimental results, you may include them in the supplementary materials.

% \subsection{The Effect of Regularization Parameter}

% \textit{Our algorithm depends on the regularization parameter $\lambda$. Here we illustrate the effect of this parameter on the performance of our algorithm [ ... ]}

\end{document}

### 2022-07-18 scripts/RLExp_DUQNS_Cartpole.jl

@@ -41,32 +41,6 @@ function RL.Experiment(
     """
     if isnothing(config)
         config = Dict(
-<<<<<<< HEAD
-                        "B_lr" => 1e-3,
-                        "Q_lr" => 0.1,
-                        "B_clip_norm" => 10.0,
-                        "B_update_freq" => 1,
-                        "Q_update_freq" => 1,
-                        "B_opt" => "ADAM",
-                        "gamma" => 0.99,
-                        "update_horizon" => 1,
-                        "batch_size" => 32,
-                        "min_replay_history" => 32,
-                        "updates_per_step" => 1,
-                        "λ" => 0.99,
-                        # "prior" => "GaussianPrior(200, 100)",
-                        # "prior" => "CartpolePrior(1)",
-                        "prior" => "FlatPrior()",
-                        # "prior" => "KernelPrior()",
-                        "n_samples" => 100,
-                        "η" => 0.01,
-                        "nev" => 6,
-                        "n_eigen_threshold" => 0.99,
-                        "is_enable_double_DQN" => true,
-                        "traj_capacity" => 1_000,
-                        "seed" => 1,
-                     )
-=======
             "B_lr" => 1e-3,
             "Q_lr" => 1,
             "B_clip_norm" => 10.0,
@@ -91,7 +65,6 @@ function RL.Experiment(
             "traj_capacity" => 100_000,
             "seed" => 1,
         )
->>>>>>> b0b5e96c0ca9b9c1160c5a9ad788b63568211c42
     end
 
     lg = WandbLogger(project="BE",
@@ -135,19 +108,11 @@ function RL.Experiment(
         # ) |> gpu
 
         B_model = Chain(
-<<<<<<< HEAD
-            NoisyDense(ns, 128, selu; init_μ = init, init_σ = init_σ, rng = device_rng),
-            NoisyDense(128, 128, selu; init_μ = init, init_σ = init_σ, rng = device_rng),
-            Split(
-                NoisyDense(128, na; init_μ = init, init_σ = init_σ, rng = device_rng),
-                NoisyDense(128, na; init_μ = init, init_σ = init_σ, rng = device_rng),
-=======
             NoisyDense(ns, 128, selu; init_μ=init, init_σ=init_σ, rng=device_rng),
[…]

### 2022-07-18 scripts/RLExp_QQFLOW_Atari.jl

@@ -1,0 +1,336 @@
+using Base.Iterators: tail
+# using BSON: @load, @save
+using JLD2
+using Conda
+using CUDA
+using Dates: now
+using Distributions: Uniform, Product
+using DrWatson
+using Flux
+using Flux: Optimiser
+using Images
+using Logging
+using Plots
+using StatsPlots
+using RLExp
+using Random
+using ReinforcementLearning
+using Setfield
+using Statistics
+using Wandb
+
+applychain(::Tuple{}, x, n; kwargs...) = x
+function applychain(fs::Tuple, x, n; kwargs...)
+    if isa(first(fs), NoisyDense) || isa(first(fs), Split)
+        return applychain(tail(fs), first(fs)(x, n; kwargs...), n; kwargs...)
+    else
+        return applychain(tail(fs), first(fs)(x), n; kwargs...)
+    end
+end
+(c::Chain)(x, n; kwargs...) = applychain(c.layers, x, n; kwargs...)
+
+function RL.Experiment(
+    ::Val{:RLExp},
+    ::Val{:QQFLOW},
+    ::Val{:Atari},
+    name;
+    restore=nothing,
+    config=nothing,
+)
+
+    """
+    SET UP LOGGING
+    """
+    if isnothing(config)
+        config = Dict(
+            "B_lr" => 5e-5,
+            "Q_lr" => 1,
+            "B_clip_norm" => 10.0,
+            "B_update_freq" => 4,
+            "Q_update_freq" => 10_000,
+            "n_samples_act" => 100,
+            "n_samples_target" => 100,
+            "hidden_dim" => 32,
+            "B_opt" => "ADAM",
+            "gamma" => 0.99,
+            "update_horizon" => 1,
+            "batch_size" => 32,
+            "min_replay_history" => 20_000,
+            "updates_per_step" => 1,
+            "is_enable_double_DQN" => true,
+            "traj_capacity" => 1_000_000,
+            "seed" => 1,
+        )
+    end
+
+    lg = WandbLogger(project="BE",
+        name="QQFLOW_Atari($name)",
+        config=config,
+    )
+    save_dir = datadir("sims", "QQFLOW", "Atari($name)", "$(now())")
+    mkpath(save_dir)
+
+    """
+    SEEDS
+    """
+    seed = get_config(lg, "seed")
+    rng = MersenneTwister()
+    Random.seed!(rng, seed)
[…]

### 2022-07-18 scripts/run_qqflow_atari.jl

@@ -21,7 +21,7 @@ addprocs_slurm(n_workers; topology=:master_worker, exeflags=["--project=.", "--c
     using DrWatson
     using RLExp
     using Random
-    include("RLExp_QFLOW_Atari.jl")
+    include("RLExp_QQFLOW_Atari.jl")
 end
 
-run(E`RLExp_QFLOW_Atari(pong)`)
+run(E`RLExp_QQFLOW_Atari(breakout)`)

### 2022-07-18 src/algorithms/DUQNS.jl

@@ -147,13 +147,7 @@ function RLBase.update!(learner::DUQNSLearner, batch::NamedTuple)
     a = CartesianIndex.(a, 1:batch_size)
 
     if is_enable_double_DQN
-<<<<<<< HEAD
-        # q_values = B(s′, n_samples, rng = rng_B)
-        q_values = Q(s′)
-        # rng_B = Random.MersenneTwister(seed)
-=======
         q_values = B(s′)
->>>>>>> b0b5e96c0ca9b9c1160c5a9ad788b63568211c42
     else
         q_values = Q(s′)
     end
@@ -165,12 +159,8 @@ function RLBase.update!(learner::DUQNSLearner, batch::NamedTuple)
 
     if is_enable_double_DQN
         selected_actions = dropdims(argmax(q_values; dims=1); dims=1)
-<<<<<<< HEAD
-        q′ = @view Q(s′)[selected_actions]
-=======
         q′ = Q(s′)
         q′ = @inbounds q′[selected_actions]
->>>>>>> b0b5e96c0ca9b9c1160c5a9ad788b63568211c42
         # q′ = dropdims(q′, dims=ndims(q′))
     else
         q′ = dropdims(maximum(q_values; dims=1); dims=1)
@@ -179,15 +169,6 @@ function RLBase.update!(learner::DUQNSLearner, batch::NamedTuple)
 
     gs = gradient(params(B)) do
         b_all, s_all = B(s, n_samples, rng=learner.rng) ## SLOW
-<<<<<<< HEAD
-        b = @view b_all[a, :]
-        ss = @view s_all[a, :]
-        # clamp!(ss, -2, 2)
-        B̂ = dropdims(sum(b, dims=ndims(b)) / size(b, ndims(b)), dims=ndims(b))
-        λ = learner.λ
-        sig = softplus.(ss)
-        𝐿 = sum(log.(sig) .+ (b .- G) .^ 2 ./ sig) / n_samples
-=======
         b = @inbounds b_all[a, :]
         ss = @inbounds s_all[a, :]
         preds = flow(G)
@@ -199,7 +180,6 @@ function RLBase.update!(learner::DUQNSLearner, batch::NamedTuple)
         # ll = huber_loss(b, preds)
         𝐿 = sum(ss .+ ll .* exp.(-ss)) .- sum(logpdf(flow, G))
         𝐿 = 𝐿 / n_samples * batch_size
[…]

### 2022-07-18 src/algorithms/QQFLOW.jl

@@ -5,23 +5,71 @@ using DataStructures: DefaultDict
 using Distributions: Uniform, Product
 using StatsBase: sample
 using Flux.Losses
+using CUDA: randn
+using MLUtils
 import Statistics.mean
 
-Base.@kwdef struct FlowNetwork{B,F}
+Base.@kwdef struct FlowNetwork{P,B,F}
     base::B
+    prior::P
     flow::F
 end
 
 Flux.@functor FlowNetwork
 
-function (m::FlowNetwork)(samples::AbstractMatrix, state::AbstractMatrix; action=nothing, reverse::Bool=true)
+function (m::FlowNetwork)(state::AbstractMatrix; inv::Bool=true)
     h = m.base(state)
-    return m.flow(samples, h; action, reverse)
+    p = m.prior(h)
+    μ, ρ = MLUtils.chunk(p, 2, dims=1)
+    σ = softplus.(ρ)
+    σ = clamp.(σ, 1f-4, 1000)
+    # samples = μ .+ randn!(similar(μ)) .* σ
+    samples = randn!(similar(μ))
+    # x1 = rand!(similar(μ))
+    # x2 = rand!(similar(μ))
+    # samples = μ .+ log.(x1 ./ x2) .* σ
+    if inv
+        preds, sldj = inverse(m.flow, samples, h)
+        preds = μ .+ preds .* σ
+    else
+        samples = (samples .- μ) ./ σ
+        preds, sldj = m.flow(samples, h)
+    end
+    return preds, sldj
 end
 
-function (m::FlowNetwork)(samples::AbstractArray{T,3}, state::AbstractMatrix; action=nothing, reverse::Bool=true) where {T}
+function (m::FlowNetwork)(state::AbstractArray, num_samples::Int; inv::Bool=true)
     h = m.base(state)
-    return m.flow(samples, h; action, reverse)
+    p = m.prior(h)
+    μ, ρ = MLUtils.chunk(p, 2, dims=1)
+    σ = softplus.(ρ)
+    σ = clamp.(σ, 1f-4, 1000)
+    # samples = μ .+ randn!(similar(μ, size(μ)..., num_samples)) .* σ
+    samples = randn!(similar(μ, size(μ)..., num_samples))
+    # x1 = rand!(similar(μ, size(μ)..., num_samples))
+    # x2 = rand!(similar(μ, size(μ)..., num_samples))
+    # samples = μ .+ log.(x1 ./ x2) .* σ
+    if inv
+        preds, sldj = inverse(m.flow, samples, h)
[…]

### 2022-07-22 papers/CDRL/sample_paper.tex
TEMPORARY DEPLOY COMMIT

@@
 
-Let \(\bm{Z}\) be a random variable defined over the support \(S \subseteq \R^n\)
+Let \(\rvZ\) be a random variable defined over the support \(S \subseteq \R^n\)
 and a continous probability density function \(q(\rvz)\). Further, let \(v\) be
 a continous, differentiable and invertible function from \(S\) to
-\(T \in \R^n\), if we let \(\bm{Z}^\prime = v(\bm{Z})\), then the probability
-function \(q(\rvz^\prime)\) of \(\bm{Z}^\prime\) is given by
+\(T \in \R^n\), if we let \(\rvZ^\prime = v(\rvZ)\), then the probability
+function \(q(\rvz^\prime)\) of \(\rvZ^\prime\) is given by
 \begin{align}
@@
   \rvz^\prime} v^{-1}(\rvz^\prime) \right) \right\rvert
-  \label{eq:change_var_form1}\\
-  &= q(v^{-1}(\rvz^\prime)) \left\lvert \det \left( \frac{\partial}{\partial
-  \rvz^\prime} v(\rvz^\prime) \right) \right\rvert^{-1}
-  \label{eq:change_var_form2}
+  \label{eq:change_var_form1}
+  % &= q(v^{-1}(\rvz^\prime)) \left\lvert \det \left( \frac{\partial}{\partial
+  % \rvz} v(\rvz) \right) \right\rvert^{-1}
+  % \label{eq:change_var_form2}
 \end{align}
@@
 
+\subsection{Conditional Normalizing Flows} \label{sec:cnf}
+Although normalizing flows is a good method for approximating distributions,
+they do not directly facilitate learning conditional likelihoods.
+\citet{winkler19} propose learning conditional distributions with
+\emph{conditional normalizing flows}. Given a conditioning variable
+\(\rvx \in U\), a random variale \(\rvZ \in S \subseteq \R^n\), and a continous,
+differentiable function \(v : S \times U \rightarrow T\), bijective in \(S\) and
+\(T\), the probability function \(q(\rvz^\prime)\), where
+\(\rvz^\prime = v(\rvz, \rvx)\), can be expressed as
+
+\begin{align}
+  q(\rvz^\prime \vert \rvx) &= q(\rvz \vert \rvx) \left\lvert \det
+  \left( \frac{\partial \rvz}{\partial \rvz^\prime} \right) \right\rvert
+  \nonumber\\
+  &= q(v^{-1}(\rvz^\prime, \rvx)) \left\lvert \det \left( \frac{\partial}
+  {\partial \rvz^\prime} v^{-1}(\rvz^\prime, \rvx) \right) \right\rvert.
+  \label{eq:cond_change_var_form1}
+  % &= q(v^{-1}(\rvz^\prime; \rvx)) \left\lvert \det \left( \frac{\partial}
+  % {\partial \rvz} v(\rvz; \rvx) \right) \right\rvert^{-1}
+\end{align}
+
+\noindent
+Compared to Equation~\eqref{eq:change_var_form1}, all distributions are now
+conditional, and the model has a conditional argument \(\rvx\).
+\citet{winkler19} suggest three conditional modules:
+
+\paragraph{Conditional Prior}
+\begin{equation*}
+  p(\rvz \vert \rvx) = \N(\rvz ; \mu(\rvx), \sigma^2(\rvx))
+\end{equation*}
+\paragraph{Conditional Split Prior}
+\begin{equation*}
+  p(\rvz_1 \vert \rvz_0, \rvx) =
+  \N (\rvz ; \mu(\rvz_0, \rvx), \sigma^2(\rvz_0, \rvx))
+\end{equation*}
+\paragraph{Conditional Coupling}
+\begin{equation*}
+  \rvz^\prime_0 = 
+  s(\rvz_1, \rvx) \cdot \rvz_0 + t(\rvz_1, \rvx); \qquad \rvz^\prime_1 = \rvz_1
+\end{equation*}
+
+The functions \(\mu\), \(\sigma^2\), \(s\) and \(t\) are implemented using
+neural networks.
+
 \section{Our Algorithm}
 
-We propose to use conditional normalizing flows to model the value distribution
-\(Z^\pi\) with a continous estimate.
+We propose to use conditional normalizing flows to model the value distribution,
+\(Z^\pi\), with a continous estimate. As opposed to quantile previous work on 
+quantile regression methods, which aim to minimize the Wasserstein distance
+to the target distribution, normalizing flows minimize KL-divergence. Our target
+is thus the KL-divergence from the target to the value distribution
+\footnote{Check order later}.
+
+\begin{equation}
+  \mathcal{L}_{\rvx,a}(\theta) \defeq \KL{\hat{\T}
+  Z_{\tilde{\theta}}(\rvx,a)}{Z_{\theta}(\rvx,a)}
+\end{equation}
+
+Using conditional normalizing flows described in Section~\ref{sec:cnf}, we
+define the value distribution model as an elementwise transformation of a
+standard normal distribution conditioned on a low-dimensional representation of
+the state \(\rvx\).
+
+\begin{equation}
+  Z_\theta(\rvx,a) = v_\theta^{-1}(z, \rvx^\prime)_a
+\end{equation}
+\begin{equation*}
+  z \sim \N(0, I); \quad \rvx^\prime = h(\rvx)
+\end{equation*}
 

### 2022-07-22 scripts/RLExp_QQFLOW_Atari.jl

@@ -47,7 +47,7 @@ function RL.Experiment(
             "Q_lr" => 1,
             "B_clip_norm" => 10.0,
             "B_update_freq" => 4,
-            "Q_update_freq" => 10_000,
+            "Q_update_freq" => 1_000,
             "n_samples_act" => 100,
             "n_samples_target" => 100,
             "hidden_dim" => 64,
@@ -61,6 +61,7 @@ function RL.Experiment(
             "traj_capacity" => 1_000_000,
             "seed" => 1,
             "flow_width" => 64,
+            "terminal_on_life_loss" => true,
         )
     end
 
@@ -83,13 +84,15 @@ function RL.Experiment(
     """
     SET UP ENVIRONMENT
     """
+    terminal_on_life_loss = get_config(lg, "terminal_on_life_loss")
     N_FRAMES = 4
     STATE_SIZE = (84, 84)
     env = atari_env_factory(
         name,
         STATE_SIZE,
         N_FRAMES;
-        seed=isnothing(seed) ? nothing : hash(seed + 1)
+        seed=isnothing(seed) ? nothing : hash(seed + 1),
+        terminal_on_life_loss = terminal_on_life_loss,
     )
     N_ACTIONS = length(action_space(env))
 
@@ -109,8 +112,8 @@ function RL.Experiment(
             Conv((4, 4), 32 => 64, leakyrelu; stride=2, pad=2, init=initc),
             Conv((3, 3), 64 => 64, leakyrelu; stride=1, pad=1, init=initc),
             x -> reshape(x, :, size(x)[end]),
-            Dense(11 * 11 * 64, 512, leakyrelu),
-            Dense(512, hidden_dim, leakyrelu),
+            Dense(11 * 11 * 64, 512, leakyrelu, init=initc),
+            Dense(512, hidden_dim, leakyrelu, init=initc),
         ) |> gpu
 
         Q_model = Chain(
@@ -119,8 +122,8 @@ function RL.Experiment(
             Conv((4, 4), 32 => 64, leakyrelu; stride=2, pad=2, init=initc),
             Conv((3, 3), 64 => 64, leakyrelu; stride=1, pad=1, init=initc),
             x -> reshape(x, :, size(x)[end]),
-            Dense(11 * 11 * 64, 512, leakyrelu),
-            Dense(512, hidden_dim, leakyrelu),
+            Dense(11 * 11 * 64, 512, leakyrelu, init=initc),
[…]

### 2022-07-22 scripts/RLExp_QQFLOW_Cartpole.jl

@@ -42,13 +42,13 @@ function RL.Experiment(
     """
     if isnothing(config)
         config = Dict(
-            "B_lr" => 5e-5,
+            "B_lr" => 1e-4,
             "Q_lr" => 1,
             "B_clip_norm" => 1.0,
             "B_update_freq" => 1,
-            "Q_update_freq" => 100,
+            "Q_update_freq" => 1000,
             "n_samples_act" => 100,
-            "n_samples_target" => 100,
+            "n_samples_target" => 1,
             "hidden_dim" => 32,
             "B_opt" => "ADAM",
             "gamma" => 0.99,
@@ -59,6 +59,7 @@ function RL.Experiment(
             "is_enable_double_DQN" => true,
             "traj_capacity" => 1_000_000,
             "seed" => 1,
+            "flow_width" => 32,
         )
     end
 
@@ -93,62 +94,65 @@ function RL.Experiment(
 
         hidden_dim = get_config(lg, "hidden_dim")
 
+        flow_width = get_config(lg, "flow_width")
         flow_B = Flow(
             [
-                PlanarLayer(na, hidden_dim, 32),
-                PlanarLayer(na, hidden_dim, 32),
-                PlanarLayer(na, hidden_dim, 32),
-                PlanarLayer(na, hidden_dim, 32),
-                PlanarLayer(na, hidden_dim, 32),
-                PlanarLayer(na, hidden_dim, 32),
-                PlanarLayer(na, hidden_dim, 32),
-                PlanarLayer(na, hidden_dim, 32),
-                PlanarLayer(na, hidden_dim, 32),
-                PlanarLayer(na, hidden_dim, 32),
-                PlanarLayer(na, hidden_dim, 32),
-                PlanarLayer(na, hidden_dim, 32),
-                PlanarLayer(na, hidden_dim, 32),
-                PlanarLayer(na, hidden_dim, 32),
-                PlanarLayer(na, hidden_dim, 32),
-                PlanarLayer(na, hidden_dim, 32),
-                PlanarLayer(na, hidden_dim, 32),
-                PlanarLayer(na, hidden_dim, 32),
+                PlanarLayer(na, hidden_dim, flow_width),
+                PlanarLayer(na, hidden_dim, flow_width),
+                PlanarLayer(na, hidden_dim, flow_width),
+                PlanarLayer(na, hidden_dim, flow_width),
+                PlanarLayer(na, hidden_dim, flow_width),
+                PlanarLayer(na, hidden_dim, flow_width),
[…]

### 2022-07-22 src/algorithms/QQFLOW.jl

@@ -24,7 +24,8 @@ function (m::FlowNetwork)(state::AbstractMatrix; inv::Bool=true)
     σ = softplus.(ρ)
     σ = clamp.(σ, 1f-4, 1000)
     # samples = μ .+ randn!(similar(μ)) .* σ
-    samples = randn!(similar(μ))
+    samples = Zygote.@ignore randn!(similar(μ, 1, size(μ, 2), size(μ,3)))
+    samples = Zygote.@ignore repeat(samples, size(μ, 1), 1, 1)
     # x1 = rand!(similar(μ))
     # x2 = rand!(similar(μ))
     # samples = μ .+ log.(x1 ./ x2) .* σ

### 2022-07-24 papers/CDRL/sample_paper.tex
TEMPORARY DEPLOY COMMIT

@@
 \begin{abstract}
-  The Abstract paragraph should be indented 0.25 inch (1.5 picas) on
-  both left and right-hand margins. Use 10~point type, with a vertical
-  spacing of 11~points. The \textbf{Abstract} heading must be centered,
-  bold, and in point size 12. Two line spaces precede the
-  Abstract. The Abstract must be limited to one paragraph.
+  % The Abstract paragraph should be indented 0.25 inch (1.5 picas) on
+  % both left and right-hand margins. Use 10~point type, with a vertical
+  % spacing of 11~points. The \textbf{Abstract} heading must be centered,
+  % bold, and in point size 12. Two line spaces precede the
+  % Abstract. The Abstract must be limited to one paragraph.
 \end{abstract}

### 2022-07-24 scripts/RLExp_QQFLOW_Atari.jl

@@ -108,22 +108,22 @@ function RL.Experiment(
 
         B_model = Chain(
             x -> x ./ 255,
-            Conv((8, 8), N_FRAMES => 32, leakyrelu; stride=4, pad=2, init=initc),
-            Conv((4, 4), 32 => 64, leakyrelu; stride=2, pad=2, init=initc),
-            Conv((3, 3), 64 => 64, leakyrelu; stride=1, pad=1, init=initc),
+            Conv((8, 8), N_FRAMES => 32, relu; stride=4, pad=2, init=initc),
+            Conv((4, 4), 32 => 64, relu; stride=2, pad=2, init=initc),
+            Conv((3, 3), 64 => 64, relu; stride=1, pad=1, init=initc),
             x -> reshape(x, :, size(x)[end]),
-            Dense(11 * 11 * 64, 512, leakyrelu, init=initc),
-            Dense(512, hidden_dim, leakyrelu, init=initc),
+            Dense(11 * 11 * 64, 512, relu, init=initc),
+            Dense(512, hidden_dim, relu, init=initc),
         ) |> gpu
 
         Q_model = Chain(
             x -> x ./ 255,
-            Conv((8, 8), N_FRAMES => 32, leakyrelu; stride=4, pad=2, init=initc),
-            Conv((4, 4), 32 => 64, leakyrelu; stride=2, pad=2, init=initc),
-            Conv((3, 3), 64 => 64, leakyrelu; stride=1, pad=1, init=initc),
+            Conv((8, 8), N_FRAMES => 32, relu; stride=4, pad=2, init=initc),
+            Conv((4, 4), 32 => 64, relu; stride=2, pad=2, init=initc),
+            Conv((3, 3), 64 => 64, relu; stride=1, pad=1, init=initc),
             x -> reshape(x, :, size(x)[end]),
-            Dense(11 * 11 * 64, 512, leakyrelu, init=initc),
-            Dense(512, hidden_dim, leakyrelu, init=initc),
+            Dense(11 * 11 * 64, 512, relu, init=initc),
+            Dense(512, hidden_dim, relu, init=initc),
         ) |> gpu
 
         flow_width = get_config(lg, "flow_width")
@@ -174,7 +174,7 @@ function RL.Experiment(
         B_approximator = NeuralNetworkApproximator(
             model=FlowNetwork(
                 base=B_model,
-                prior=Chain(Dense(hidden_dim, flow_width, leakyrelu),
+                prior=Chain(Dense(hidden_dim, flow_width, relu),
[…]

### 2022-07-24 src/algorithms/normflows.jl

@@ -28,8 +28,8 @@ Flux.@functor PlanarLayer
 
 function PlanarLayer(in::Int, h_size::Int, h_dims::Int, init=Flux.glorot_uniform)
     net = Chain(
-        Dense(h_size, h_dims, leakyrelu, init=init),
-        Dense(h_dims, h_dims, leakyrelu, init=init),
+        Dense(h_size, h_dims, relu, init=init),
+        Dense(h_dims, h_dims, relu, init=init),
         Dense(h_dims, 3 * in, init=init),
     )
     return PlanarLayer(net, 0.2f0)
@@ -38,7 +38,7 @@ end
 function (l::PlanarLayer)(x, h)
     m(x) = -1 + log(1 + exp(x))
     w, u, b = MLUtils.chunk(l.net(h), 3, dims=1)
-    u, w = 0.9f0 .* tanh.(u), tanh.(w)
+    u, w = tanh.(u), tanh.(w)
     # u = u .+ (m.(w .* u) .- w .* u) .* (w .+ 1f-8) ./ (abs2.(w) .+ 1f-8)
     f(x) = x .+ u .* tanh.(w .* x .+ b)
     ψ(x) = tanh_prime.(w .* x .+ b) .* w
@@ -50,7 +50,7 @@ end
 function inverse(l::PlanarLayer, x, h)
     m(x) = -1 + log(1 + exp(x))
     w, u, b = MLUtils.chunk(l.net(h), 3, dims=1)
-    u, w = 0.9f0 .* tanh.(u), tanh.(w)
+    u, w = tanh.(u), tanh.(w)
     # if any(w .* u .<= -1)
     # u = u .+ (m.(w .* u) .- w .* u) .* (w .+ 1f-8) ./ (abs2.(w) .+ 1f-8)
     # end

### 2022-07-24 scripts/RLExp_QQFLOW_Atari.jl
TEMPORARY DEPLOY COMMIT

@@ -113,7 +113,7 @@ function RL.Experiment(
             Conv((3, 3), 64 => 64, relu; stride=1, pad=1, init=initc),
             x -> reshape(x, :, size(x)[end]),
             Dense(11 * 11 * 64, 512, relu, init=initc),
-            Dense(512, hidden_dim, relu, init=initc),
+            Dense(512, hidden_dim, relu, init=(args...) -> initc(args...) ./ 100),
         ) |> gpu
 
         Q_model = Chain(
@@ -123,7 +123,7 @@ function RL.Experiment(
             Conv((3, 3), 64 => 64, relu; stride=1, pad=1, init=initc),
             x -> reshape(x, :, size(x)[end]),
             Dense(11 * 11 * 64, 512, relu, init=initc),
-            Dense(512, hidden_dim, relu, init=initc),
+            Dense(512, hidden_dim, relu, init=(args...) -> initc(args...) ./ 100),
         ) |> gpu
 
         flow_width = get_config(lg, "flow_width")
@@ -174,8 +174,8 @@ function RL.Experiment(
         B_approximator = NeuralNetworkApproximator(
             model=FlowNetwork(
                 base=B_model,
-                prior=Chain(Dense(hidden_dim, flow_width, relu),
-                            Dense(flow_width, 2N_ACTIONS),
+                prior=Chain(Dense(hidden_dim, flow_width, relu, init=initc),
+                            Dense(flow_width, 2N_ACTIONS, init=initc),
                 ),
                 flow=flow_B,
             ),
@@ -185,8 +185,8 @@ function RL.Experiment(
         Q_approximator = NeuralNetworkApproximator(
             model=FlowNetwork(
                 base=Q_model,
-                prior=Chain(Dense(hidden_dim, flow_width, relu),
-                            Dense(flow_width, 2N_ACTIONS),
+                prior=Chain(Dense(hidden_dim, flow_width, relu, init = initc),
+                            Dense(flow_width, 2N_ACTIONS, init = initc),
                 ),
                 flow=flow_Q,
             ),

### 2022-07-24 scripts/RLExp_QQFLOW_Cartpole.jl

@@ -44,9 +44,9 @@ function RL.Experiment(
         config = Dict(
             "B_lr" => 1e-4,
             "Q_lr" => 1,
-            "B_clip_norm" => 1.0,
+            "B_clip_norm" => 10.0,
             "B_update_freq" => 1,
-            "Q_update_freq" => 1000,
+            "Q_update_freq" => 100,
             "n_samples_act" => 100,
             "n_samples_target" => 1,
             "hidden_dim" => 32,
@@ -147,11 +147,11 @@ function RL.Experiment(
         B_approximator = NeuralNetworkApproximator(
             model=FlowNetwork(
                 base=Chain(
-                    Dense(ns, 128, leakyrelu, init=init),
-                    Dense(128, 128, leakyrelu, init=init),
-                    Dense(128, hidden_dim, leakyrelu, init=init),
+                    Dense(ns, 128, relu, init=init),
+                    Dense(128, 128, relu, init=init),
+                    Dense(128, hidden_dim, relu, init=init),
                 ),
-                prior=Chain(Dense(hidden_dim, 32, leakyrelu, init=init),
+                prior=Chain(Dense(hidden_dim, 32, relu, init=init),
                             Dense(32, 2na, init=init)
                 ),
                 flow=flow_B,
@@ -162,11 +162,11 @@ function RL.Experiment(
         Q_approximator = NeuralNetworkApproximator(
             model=FlowNetwork(
                 base=Chain(
-                    Dense(ns, 128, leakyrelu, init=init),
-                    Dense(128, 128, leakyrelu, init=init),
-                    Dense(128, hidden_dim, leakyrelu, init=init),
+                    Dense(ns, 128, relu, init=init),
+                    Dense(128, 128, relu, init=init),
+                    Dense(128, hidden_dim, relu, init=init),
                 ),
-                prior=Chain(Dense(hidden_dim, 32, leakyrelu, init=init),
+                prior=Chain(Dense(hidden_dim, 32, relu, init=init),
                             Dense(32, 2na, init=init)
                 ),
                 flow=flow_Q,

### 2022-07-24 src/algorithms/normflows.jl

@@ -30,7 +30,7 @@ function PlanarLayer(in::Int, h_size::Int, h_dims::Int, init=Flux.glorot_normal(
     net = Chain(
         Dense(h_size, h_dims, relu, init=init),
         Dense(h_dims, h_dims, relu, init=init),
-        Dense(h_dims, 3 * in, init=init),
+        Dense(h_dims, 3 * in, init=(args...) -> init(args...) ./ 100),
     )
     return PlanarLayer(net, 0.2f0)
 end

### 2022-07-26 scripts/RLExp_QQFLOW_Cartpole.jl
TEMPORARY DEPLOY COMMIT

@@ -44,7 +44,7 @@ function RL.Experiment(
         config = Dict(
             "B_lr" => 5e-5,
             "Q_lr" => 1,
-            "B_clip_norm" => 10.0,
+            "B_clip_norm" => 1.0,
             "B_update_freq" => 1,
             "Q_update_freq" => 100,
             "n_samples_act" => 100,
@@ -143,11 +143,11 @@ function RL.Experiment(
         B_approximator = NeuralNetworkApproximator(
             model=FlowNetwork(
                 base=Chain(
-                    Dense(ns, 128, relu, init=init),
-                    Dense(128, 128, relu, init=init),
-                    Dense(128, hidden_dim, relu, init=init),
+                    Dense(ns, 128, leakyrelu, init=init),
+                    Dense(128, 128, leakyrelu, init=init),
+                    Dense(128, hidden_dim, init=init),
                 ),
-                prior=Chain(Dense(hidden_dim, 32, relu, init=init),
+                prior=Chain(Dense(hidden_dim, 32, leakyrelu, init=init),
                     Dense(32, 2na, init=init)
                 ),
                 flow=flow_B,
@@ -158,11 +158,11 @@ function RL.Experiment(
         Q_approximator = NeuralNetworkApproximator(
             model=FlowNetwork(
                 base=Chain(
-                    Dense(ns, 128, relu, init=init),
-                    Dense(128, 128, relu, init=init),
-                    Dense(128, hidden_dim, relu, init=init),
+                    Dense(ns, 128, leakyrelu, init=init),
+                    Dense(128, 128, leakyrelu, init=init),
+                    Dense(128, hidden_dim, init=init),
                 ),
-                prior=Chain(Dense(hidden_dim, 32, relu, init=init),
+                prior=Chain(Dense(hidden_dim, 32, leakyrelu, init=init),
                     Dense(32, 2na, init=init)
                 ),
                 flow=flow_Q,
@@ -248,7 +248,7 @@ function RL.Experiment(
                 stop("Program most likely terminated through WandB interface.")
             end
         end,
-        DoEveryNEpisode(n=100) do t, agent, env
+        DoEveryNStep(n=2000) do t, agent, env
             @info "evaluating agent at $t step..."
             p = agent.policy
             h = ComposedHook(
@@ -293,7 +293,7 @@ function RL.Experiment(
         end,
         CloseLogger(lg),
     )
[…]

### 2022-08-01 papers/CDRL/sample_paper.tex
TEMPORARY DEPLOY COMMIT

@@
 \begin{equation}
-  \left\lvert \det \frac{\partial v}{\partial \rvz} \right\rvert =
+  \det \left\lvert \frac{\partial v}{\partial \rvz} \right\rvert =
   \left\lvert 1 + \rvu^\top h^\prime(\rvw^\top \rvz + b) \rvw \right\rvert,
@@
 
+Similar to other DQN methods, we let \(Z_\theta(\rvx, a)\) be the \(a\)-th
+element of a function \(\tilde{Z}_\theta : \R^{\lvert \X \rvert}
+\rightarrow \R^{\lvert \A \rvert}\). This means that we need a conditional
+normalizing flow \(v_\theta : \R^{\lvert \X \rvert} \times \R^{\lvert \A \rvert}
+\rightarrow \R^{\lvert \A \rvert}\). Given that we have
+
 \begin{equation}
-  Z_\theta(\rvx,a) = v_\theta^{-1}(z, \rvx^\prime)_a
+  \T \tilde{Z}_\theta(\rvx)_a \defeq R(\rvx, a) + \max_{a^\prime \in \A}
+  \tilde{Z}_\theta(\rvx^\prime)_{a^\prime}
 \end{equation}
+
+\noindent
+we can see that any learning signal would only come for a single action. This
+means that we need an elementwise flow so that we can learn each dimension
+independently. Given elementwise conditional normalizing flow \(v_\theta\), we
+define the loss function as
+
+\begin{multline}
+  \mathcal{L}_{\rvx, a}(\theta) \defeq \log p(v_\theta^{-1} (\rvx, v_{\tilde{
+  \theta}} (\rvx^\prime, \vepsilon))_a; 0, 1) \\- \log
+  \left\lvert \frac{\partial v^{-1}_{\theta}(\rvx, v_{\tilde{
+  \theta}} (\rvx^\prime, \vepsilon))_a}{\partial v_{\tilde{
+  \theta}} (\rvx^\prime, \vepsilon)_a} \right\rvert; \quad
+  \vepsilon \sim \N(0, I_{\lvert \A \rvert})
+\end{multline}
+
+The most popular normalizing flows right now are buildt for large dimensional
+spaces such as images. This includes coupling and autoregressive flows. Planar
+flow is very easy to turn elementwise, but unfortunately does not have a closed
+form inverse for most functions of \(h\). Although it does have one for
+piecewise linear funcitons, those do not have second derivative, hence the
+gradient of the log absolute determinant would be zero. This would mean it can
+not learn appropriate transformations. Instead we define our own flow.
+
+Equation~\ref{eq:luddeflow} shows the definitiona of the forward transformation
+\(v_{w, b, c, d}\), with 4 free parameters \(w, b, c, d\). Unlike the planar
+flow, this function is invertible and differentiable given any values for these
+parameters. Equation~\ref{eq:luddeflow_inv} and
+Equation~\ref{eq:luddeflow_inv_grad} show the closed form inverse and gradient
+respectively.
+
+% \begin{equation}
+%   Z_\theta(\rvx,a) = v_\theta^{-1}(z, \rvx^\prime)_a
+% \end{equation}
+% \begin{equation*}
+%   z \sim \N(0, I); \quad \rvx^\prime = h(\rvx)
+% \end{equation*}
+
 \begin{equation*}
-  z \sim \N(0, I); \quad \rvx^\prime = h(\rvx)
+  s(x) = \log(1 + \exp(x))
 \end{equation*}
+\begin{equation}
+  v_{w, b, c, d}(z) = \sign(z + c) \left[ s(\lvert w(z + c) \rvert + b) 
+  - s(b) \right] + d \label{eq:luddeflow}
+\end{equation}
+
+\begin{equation*}
+  s^{-1}(x) = \log(\exp(x) - 1); \quad x > 0
+\end{equation*}
+\begin{equation}
+  v^{-1}_{w, b, c, d}(z^\prime) = \frac{\sign(z^\prime - d)}{w}
+  [ s^{-1}(\lvert z^\prime - d \rvert + s(b)) - b] - c \label{eq:luddeflow_inv}
+\end{equation}
+
+\begin{equation}
+  \frac{\partial v^{-1}_{w,b,c,d}}{\partial z^\prime} = \frac{(e^b + 1)
+  (z^\prime - d) e^{\lvert z^\prime - d \rvert} \sign{(x - d)}}{w \lvert
+  z^\prime - d \rvert ((e^b + 1)e^{\lvert z^\prime - d \rvert} - 1)}
+  \label{eq:luddeflow_inv_grad}
+\end{equation}
+
+Figure~\ref{fig:luddeflow} shows the effect of the free parameters. A simple
+description is \(w\) changes the slope of the function, \(b\) changes the
+\emph{linearity} of the function (as \(b\) goes to infinity, \(v\) approaches a
+linear function), \(c\) shifts the horizontally, and \(d\) shifts the function
+vertically.
+
+\begin{figure}[ht]
+  \vspace{.3in}
+  % \centerline{\fbox{This figure intentionally left non-blank}}
+  \includegraphics[width=\columnwidth]{luddeflow.png}
+  \vspace{.3in}
+  \caption{Illustration of the effect the free parameters have on the function).
+  }\label{fig:luddeflow}
+\end{figure}
 

### 2022-08-01 scripts/RLExp_QQFLOW_Atari.jl

@@ -55,13 +55,13 @@ function RL.Experiment(
             "gamma" => 0.99,
             "update_horizon" => 1,
             "batch_size" => 32,
-            "min_replay_history" => 20_000,
+            "min_replay_history" => 50_000,
             "updates_per_step" => 1,
             "is_enable_double_DQN" => true,
             "traj_capacity" => 1_000_000,
             "seed" => 1,
             "flow_width" => 32,
-            "terminal_on_life_loss" => true,
+            "terminal_on_life_loss" => false,
         )
     end
 
@@ -272,19 +272,21 @@ function RL.Experiment(
                 @info "training" episode = t log_step_increment = 0
                 @info "training" episode_length = step_per_episode.steps[end] reward = reward_per_episode.rewards[end] log_step_increment = 0
             end
-            
-            s = agent.trajectory[:state]
-            beg = rand((1 + N_FRAMES):size(s,3))
-            s = s[:,:,(beg - N_FRAMES):(beg - 1)]
-            s = Flux.unsqueeze(s, 4) |> gpu
-            samples = agent.policy.learner.B_approximator(s, 500)[1] |> cpu
-            p = plot()
-            for action in 1:size(samples, 1)
-                density!(samples[action, 1, :], c=action, label="action $(action)")
-                vline!([mean(samples[action, 1, :])], c=action, label=false)
+            try
+                s = agent.trajectory[:state]
+                beg = rand((1 + N_FRAMES):size(s,3))
+                s = s[:,:,(beg - N_FRAMES):(beg - 1)]
+                s = Flux.unsqueeze(s, 4) |> gpu
+                samples = agent.policy.learner.B_approximator(s, 500)[1] |> cpu
+                p = plot()
+                for action in 1:size(samples, 1)
+                    density!(samples[action, 1, :], c=action, label="action $(action)")
+                    vline!([mean(samples[action, 1, :])], c=action, label=false)
+                end
+                Plots.savefig(p, save_dir * "/qdistr_$(t).png")
+            catch
+                @warn "Could not save plot"
             end
-            Plots.savefig(p, save_dir * "/qdistr_$(t).png")
-        
         end,
         DoEveryNStep(; n=EVALUATION_FREQ) do t, agent, env
             @info "Saving agent at step $t to $save_dir"

### 2022-08-01 src/algorithms/QQFLOW.jl

@@ -24,8 +24,9 @@ function (m::FlowNetwork)(state::AbstractMatrix; inv::Bool=true)
     σ = softplus.(ρ)
     σ = clamp.(σ, 1f-4, 1000)
     # samples = μ .+ randn!(similar(μ)) .* σ
-    samples = Zygote.@ignore randn!(similar(μ, 1, size(μ, 2), size(μ,3)))
-    samples = Zygote.@ignore repeat(samples, size(μ, 1), 1, 1)
+    samples = Zygote.@ignore randn!(similar(μ))
+    # samples = Zygote.@ignore randn!(similar(μ, 1, size(μ, 2), num_samples))
+    # samples = Zygote.@ignore repeat(samples, size(μ, 1), 1, 1)
     # x1 = rand!(similar(μ))
     # x2 = rand!(similar(μ))
     # samples = μ .+ log.(x1 ./ x2) .* σ
@@ -46,7 +47,9 @@ function (m::FlowNetwork)(state::AbstractArray, num_samples::Int; inv::Bool=true
     σ = softplus.(ρ)
     σ = clamp.(σ, 1f-4, 1000)
     # samples = μ .+ randn!(similar(μ, size(μ)..., num_samples)) .* σ
-    samples = randn!(similar(μ, size(μ)..., num_samples))
+    samples = Zygote.@ignore randn!(similar(μ, size(μ)..., num_samples))
+    # samples = Zygote.@ignore randn!(similar(μ, 1, size(μ, 2), num_samples))
+    # samples = Zygote.@ignore repeat(samples, size(μ, 1), 1, 1)
     # x1 = rand!(similar(μ, size(μ)..., num_samples))
     # x2 = rand!(similar(μ, size(μ)..., num_samples))
     # samples = μ .+ log.(x1 ./ x2) .* σ
@@ -68,7 +71,7 @@ function (m::FlowNetwork)(samples::AbstractArray, state::AbstractArray)
     σ = clamp.(σ, 1f-4, 1000)
     μ = reshape(μ, size(μ)..., 1)
     σ = reshape(σ, size(σ)..., 1)
-    samples = (samples .- μ) ./ σ 
+    samples = (samples .- μ) ./ σ
     preds, sldj = m.flow(samples, h)
     return preds, sldj, μ, σ
 end

### 2022-08-01 src/algorithms/normflows.jl

@@ -43,7 +43,7 @@ function (l::LuddeFlow)(x, h)
     out = sign.(xd) .* (log.(max.(inner, ϵ)) .- b) ./ w .- c
     eax = exp.(abs.(xd))
     eb = exp.(b) .+ 1
-    d_upper = eb .* xd .* eax .* sign.(xd)
+    d_upper = eb .* xd .* eax .* sign.(xd) .+ ϵ
     d_lower = w .* abs.(xd) .* (eb .* eax .- 1) .+ ϵ
     return out, log.(max.(abs.(d_upper ./ d_lower), ϵ))
 end

### 2022-08-02 src/algorithms/normflows.jl
Update paper

@@ -43,8 +43,8 @@ function (l::LuddeFlow)(x, h)
     out = sign.(xd) .* (log.(max.(inner, ϵ)) .- b) ./ w .- c
     eax = exp.(abs.(xd))
     eb = exp.(b) .+ 1
-    d_upper = eb .* xd .* eax .* sign.(xd) .+ ϵ
-    d_lower = w .* abs.(xd) .* (eb .* eax .- 1) .+ ϵ
+    d_upper = eb .* eax
+    d_lower = w .* (d_upper .- 1) .+ ϵ
     return out, log.(max.(abs.(d_upper ./ d_lower), ϵ))
 end
 

### 2022-08-16 src/algorithms/QQFLOW.jl
final QQFLOW

@@ -1,5 +1,5 @@
 export QQFLOWLearner, FlowNetwork, FlowNet
-import ReinforcementLearning.RLBase.update!
+import ReinforcementLearning.RLBase.optimise!
 
 using DataStructures: DefaultDict
 using Distributions: Uniform, Product
@@ -50,27 +50,31 @@ function v2(x, b, c, d)
     xc = x .- c
     axc = abs.(xc)
     u = max.(axc, b)
-    s = exp.(axc .- u) .+ exp.(b .- u) .- exp.(-u)
+    excu = exp.(axc .- u)
+    exbu = exp.(b .- u)
+    exu = exp.(-u)
+    s = excu .+ exbu .- exu
     r = u .+ log.(s) .- b
     out = sign.(xc) .* r .+ d
-    dupper = exp.(axc .- u)
-    dlower = dupper .+ exp.(b .- u) .- exp.(-u)
-    out, log.(dupper ./ dlower)
+    # dupper = excu
+    # dlower = s
+    out, log.(excu ./ s)
 end
 
-function v2⁻¹(x, b, c, d)
-    xc = x .- c
-    axc = abs.(xc)
-    u = max.(axc, b)
-    s = exp.(axc .- u) .+ exp.(b .- u) .- exp.(-u)
-    r = u .+ log.(s) .- b
-    out = sign.(xc) .* r .+ d
-    out, 0f0
-end
+v2⁻¹(x, b, c, d) = v2(x, -b, d, c)
+
+# function v2⁻¹(x, b, c, d)
+#     xc = x .- c
+#     axc = abs.(xc)
+#     u = max.(axc, b)
+#     s = exp.(axc .- u) .+ exp.(b .- u) .- exp.(-u)
+#     r = u .+ log.(s) .- b
+#     out = sign.(xc) .* r .+ d
+#     out, 0f0
+# end
 
 Base.@kwdef struct FlowNet{P}
     net::P
-    n_actions::Int
 end
 
 Flux.@functor FlowNet
@@ -93,8 +97,7 @@ Flux.@functor FlowNet
 #     z, lz
 # end
 
-function (m::FlowNet)(state::AbstractArray, num_samples::Int)
-    na = m.n_actions
+function (m::FlowNet)(state::AbstractArray, num_samples::Int, na::Int)
     p = m.net(state)
     μ = @inbounds p[1:na,:]
     ρ = @inbounds p[(na+1):(2na),:]
[…]

### 2022-08-25 papers/CDRL/ill.tex
TEMPORARY DEPLOY COMMIT

\documentclass[tikz, border=1mm]{standalone}
\usepackage{pgfplots}
\begin{document}
\pgfmathdeclarefunction{gauss}{2}{%
  \pgfmathparse{1/(#2*sqrt(2*pi))*exp(-((x-#1)^2)/(2*#2^2))}%
}
\begin{tikzpicture}
\begin{axis}[
    no markers, domain=-3:3, samples=100,
    every axis y label/.style={at=(current axis.above origin),anchor=south},
    every axis x label/.style={at=(current axis.right of origin),anchor=west},
    height=5cm, width=12cm,
    xtick={-2,-1,0,1,2,3}, ytick=\empty,
    enlargelimits=false, clip=false, axis on top,
    grid = major
    ]
    \addplot [very thick,cyan!50!black] {gauss(0,1)};
\end{axis}
\end{tikzpicture}
\begin{tikzpicture}
    \begin{axis}[
        no markers, domain=-3:3, samples=100,
        every axis y label/.style={at=(current axis.above origin),anchor=south},
        every axis x label/.style={at=(current axis.right of origin),anchor=west},
        height=5cm, width=12cm,
        xtick={-2,-1,0,1,2,3}, ytick=\empty,
        enlargelimits=false, clip=false, axis on top,
        grid = major
        ]
        \addplot [very thick,cyan!50!black] {
            sign(x - 1) * (ln(exp(abs(x - 1)) + exp(-2) - 1) + 2)
            };
    \end{axis}
    \end{tikzpicture}
\end{document}

### 2022-08-25 papers/CDRL/sample_paper.tex
Update paper
final QQFLOW
TEMPORARY DEPLOY COMMIT

--- 2022-07-24 papers/CDRL/sample_paper.tex
@@
 \usepackage[accepted]{aistats2022}
+\usepackage{minted}
 %
@@
 We propose to use conditional normalizing flows to model the value distribution,
-\(Z^\pi\), with a continous estimate. As opposed to quantile previous work on 
+\(Z^\pi\), with a continous estimate. As opposed to previous work on 
 quantile regression methods, which aim to minimize the Wasserstein distance
-to the target distribution, normalizing flows minimize KL-divergence. Our target
-is thus the KL-divergence from the target to the value distribution
-\footnote{Check order later}.
+to the target distribution, normalizing flows minimize the KL-divergence. Our
+target is thus the KL-divergence from the value to the target distribution.
 
 \begin{equation}
-  \mathcal{L}_{\rvx,a}(\theta) \defeq \KL{\hat{\T}
-  Z_{\tilde{\theta}}(\rvx,a)}{Z_{\theta}(\rvx,a)}
+  \mathcal{L}_{\rvx,a}(\theta) \defeq \KL{Z_{\theta}(\rvx,a)}{\hat{\T}
+  Z_{\tilde{\theta}}(\rvx,a)}
 \end{equation}
@@
 Using conditional normalizing flows described in Section~\ref{sec:cnf}, we
-define the value distribution model as an elementwise transformation of a
-standard normal distribution conditioned on a low-dimensional representation of
-the state \(\rvx\).
+define the value distribution model as a transformation of a
+standard normal distribution conditioned on the state \(\rvx\).
+
+% Similar to other DQN methods, we let \(Z_\theta(\rvx, a)\) be the \(a\)-th
+% element of a function \(\tilde{Z}_\theta : \R^{\lvert \X \rvert}
+% \rightarrow \R^{\lvert \A \rvert}\). This means that we need a conditional
+% normalizing flow \(v_\theta : \R^{\lvert \X \rvert} \times \R^{\lvert \A \rvert}
+% \rightarrow \R^{\lvert \A \rvert}\). Given that we have
+
+Starting with a random variable \(S\) with a standard normal distribution
+\(\N(0, I_{\lvert \A \rvert})\), we want a function \(v_\theta = v_{\theta_K}
+\circ \dots \circ v_{\theta_2} \circ v_{\theta_1} \), such that
+\(Z_\theta(\rvx, a) = v_\theta(S; \rvx)_a\). To learn \(v_\theta\) we note that
+we can take the inverse transformation \(v^{-1}_\theta\) of the value
+distribution to recover a random variable with the standard normal distribution,
+i.e. \(S = v^{-1}_\theta(Z_\theta; \rvx)\). This further means that
 
 \begin{equation}
-  Z_\theta(\rvx,a) = v_\theta^{-1}(z, \rvx^\prime)_a
+  S^\prime \eqdist v^{-1}_\theta \left(\T v_\theta(S; \rvx); \rvx^\prime \right).
 \end{equation}
-\begin{equation*}
-  z \sim \N(0, I); \quad \rvx^\prime = h(\rvx)
-\end{equation*}
+
+We can use this
+
+\begin{minted}[mathescape,
+  linenos,
+  numbersep=5pt,
+  gobble=2,
+  frame=lines,
+  framesep=2mm]{csharp}
+string title = "This is a Unicode π in the sky"
+/*
+Defined as $\pi=\lim_{n\to\infty}\frac{P_n}{d}$ where $P$ is the perimeter
+of an $n$-sided regular polygon circumscribing a
+circle of diameter $d$.
+*/
+const double pi = 3.1415926535
+\end{minted}
+
+% \begin{equation}
+%   \T \tilde{Z}_\theta(\rvx)_a \defeq R(\rvx, a) + \max_{a^\prime \in \A}
+%   \tilde{Z}_\theta(\rvx^\prime)_{a^\prime}
+% \end{equation}
+
+% \noindent
+% we can see that any learning signal would only come for a single action. This
+% means that we need an elementwise flow so that we can learn each dimension
+% independently. Given elementwise conditional normalizing flow \(v_\theta\), we
+% define the loss function as
+
+% \begin{multline}
+%   \mathcal{L}_{\rvx, a}(\theta) \defeq \log p(v_\theta^{-1} (\rvx, v_{\tilde{
+%   \theta}} (\rvx^\prime, \vepsilon))_a; 0, 1) \\- \log
+%   \left\lvert \frac{\partial v^{-1}_{\theta}(\rvx, v_{\tilde{
+%   \theta}} (\rvx^\prime, \vepsilon))_a}{\partial v_{\tilde{
+%   \theta}} (\rvx^\prime, \vepsilon)_a} \right\rvert; \quad
+%   \vepsilon \sim \N(0, I_{\lvert \A \rvert})
+% \end{multline}
+
+The most popular normalizing flows right now are buildt for large dimensional
+spaces such as images. This includes coupling and autoregressive flows. Planar
+flow is very easy to turn elementwise, but unfortunately does not have a closed
+form inverse for most functions of \(h\). Although it does have one for
+piecewise linear funcitons, those do not have second derivative, hence the
+gradient of the log absolute determinant would be zero. This would mean it can
+not learn appropriate transformations. Instead we define our own flow.
+
+Equation~\ref{eq:luddeflow} shows the definitiona of the forward transformation
+\(v_{w, b, c, d}\), with 4 free parameters \(w, b, c, d\). Unlike the planar
+flow, this function is invertible and differentiable given any values for these
+parameters. Equation~\ref{eq:luddeflow_inv} and
+Equation~\ref{eq:luddeflow_grad} show the closed form gradient.
+
+% \begin{equation}
+%   Z_\theta(\rvx,a) = v_\theta^{-1}(z, \rvx^\prime)_a
+% \end{equation}
+% \begin{equation*}
+%   z \sim \N(0, I); \quad \rvx^\prime = h(\rvx)
+% \end{equation*}
+
+% \begin{equation*}
+%   s(x) = \log(1 + \exp(x))
+% \end{equation*}
+% \begin{equation}
+%   v_{w, b, c, d}(z) = \sign(z + c) \left[ s(\lvert w(z + c) \rvert + b) 
+%   - s(b) \right] + d \label{eq:luddeflow}
+% \end{equation}
+
+% \begin{equation*}
+%   s^{-1}(x) = \log(\exp(x) - 1); \quad x > 0
+% \end{equation*}
+% \begin{equation}
+%   v^{-1}_{w, b, c, d}(z^\prime) = \frac{\sign(z^\prime - d)}{w}
+%   [ s^{-1}(\lvert z^\prime - d \rvert + s(b)) - b] - c \label{eq:luddeflow_inv}
+% \end{equation}
+
+% \begin{equation}
+%   \frac{\partial v^{-1}_{w,b,c,d}}{\partial z^\prime} = \frac{(e^b + 1) 
+%   e^{\lvert z^\prime - d \rvert}}{w (e^b + 1)e^{\lvert z^\prime - d \rvert} - w}
+%   \label{eq:luddeflow_inv_grad}
+% \end{equation}
+
+\begin{equation}
+  v(z; b, c, d) = \sign(z - c) \log \left( e^{\lvert x - c \rvert}
+   + e^{b} - 1 \right) + d \label{eq:luddeflow}
+\end{equation}
+
+\begin{equation}
+  \frac{\partial v(z; b, c, d)}{\partial z} = \frac{e^{\lvert x - c \rvert}}
+  {e^{\lvert x - c \rvert} + e^{b} - 1}
+  \label{eq:luddeflow_grad}
+\end{equation}
+
+\begin{equation}
+  v^{-1}(z^\prime; b, c, d) = v(z^\prime; -b, d, c) \label{eq:luddeflow_inv}
+\end{equation}
+
+Figure~\ref{fig:luddeflow} shows the effect of the free parameters. A simple
+description is \(w\) changes the slope of the function, \(b\) changes the
+\emph{linearity} of the function (as \(b\) goes to infinity, \(v\) approaches a
+linear function), \(c\) shifts the horizontally, and \(d\) shifts the function
+vertically.
+
+\begin{figure}[ht]
+  \vspace{.3in}
+  % \centerline{\fbox{This figure intentionally left non-blank}}
+  \includegraphics[width=\columnwidth]{luddeflow.png}
+  \vspace{.3in}
+  \caption{Illustration of the effect the free parameters have on the function).
+  }\label{fig:luddeflow}
+\end{figure}
 

### 2022-08-25 scripts/RLExp_QQFLOW_Atari.jl

@@ -157,7 +157,7 @@ function RL.Experiment(
                 rng=rng
             ),
             controller = InsertSampleRatioController(
-                ratio=1 / get_config(lg, "update_freq"),
+                ratio=1 // get_config(lg, "update_freq"),
                 threshold=get_config(lg, "min_replay_history"),
             ),
         ),

### 2022-08-25 src/utils/atari.jl

@@ -28,7 +28,7 @@ function atari_env_factory(
     n_frames,
     max_episode_steps=100_000;
     seed=nothing,
-    repeat_action_probability=0.25,
+    repeat_action_probability=0.0,
     n_replica=nothing,
     terminal_on_life_loss=false,
 )
@@ -40,7 +40,7 @@ function atari_env_factory(
                         name=string(name),
                         grayscale_obs=true,
                         noop_max=30,
-                        frame_skip=4,
+                        frame_skip=1,
                         terminal_on_life_loss=terminal_on_life_loss,
                         repeat_action_probability=repeat_action_probability,
                         max_num_frames_per_episode=n_frames * max_episode_steps,

### 2022-08-25 papers/CDRL/sample_paper.tex
TEMPORARY DEPLOY COMMIT

@@
 \usepackage[accepted]{aistats2022}
-\usepackage{minted}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+\algblock{Input}{EndInput}
+\algnotext{EndInput}
+\algblock{Output}{EndOutput}
+\algnotext{EndOutput}
+\newcommand{\Desc}[2]{\State \makebox[2em][l]{#1}#2}
 %
@@
 
-\begin{minted}[mathescape,
-  linenos,
-  numbersep=5pt,
-  gobble=2,
-  frame=lines,
-  framesep=2mm]{csharp}
-string title = "This is a Unicode π in the sky"
-/*
-Defined as $\pi=\lim_{n\to\infty}\frac{P_n}{d}$ where $P$ is the perimeter
-of an $n$-sided regular polygon circumscribing a
-circle of diameter $d$.
-*/
-const double pi = 3.1415926535
-\end{minted}
+\begin{algorithm}
+  \caption{An algorithm with caption}\label{alg:cap}
+  \begin{algorithmic}
+  \Require $n \geq 0$
+  \Input
+    1
+  \EndInput
+  \State $S \sim \N(0,I_{\lvert \A \rvert})$
+  \State $z \gets v^(S; )$
+  \State $N \gets n$
+  \While{$N \neq 0$}
+  \If{$N$ is even}
+      \State $X \gets X \times X$
+      \State $N \gets \frac{N}{2}$  \Comment{This is a comment}
+  \ElsIf{$N$ is odd}
+      \State $y \gets y \times X$
+      \State $N \gets N - 1$
+  \EndIf
+  \EndWhile
+  \end{algorithmic}
+\end{algorithm}
 

### 2022-08-25 scripts/RLExp_QQFLOW_Atari.jl
TEMPORARY DEPLOY COMMIT

@@ -53,7 +53,7 @@ function RL.Experiment(
         "is_enable_double_DQN" => true,
         "traj_capacity" => 1_000_000,
         "seed" => 1,
-        "flow_depth" => 8,
+        "flow_depth" => 4,
         "terminal_on_life_loss" => true,
         "n_steps" => 200_000_000,
     )

### 2022-08-25 papers/CDRL/sample_paper.tex
TEMPORARY DEPLOY COMMIT

--- 2022-08-25 papers/CDRL/sample_paper.tex
@@
 \usepackage[accepted]{aistats2022}
-\usepackage{minted}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+\usepackage{xcolor}
 %
@@
 
-\begin{minted}[mathescape,
-  linenos,
-  numbersep=5pt,
-  gobble=2,
-  frame=lines,
-  framesep=2mm]{csharp}
-string title = "This is a Unicode π in the sky"
-/*
-Defined as $\pi=\lim_{n\to\infty}\frac{P_n}{d}$ where $P$ is the perimeter
-of an $n$-sided regular polygon circumscribing a
-circle of diameter $d$.
-*/
-const double pi = 3.1415926535
-\end{minted}
+\begin{algorithm}
+  \caption{Flow-RL Loss}\label{alg:LTM}
+  \textbf{Require:} \(N, v, v^{-1}, \theta, \tilde{\theta}\)\\
+  \textbf{input} \(\rvx, a, r, \rvx^\prime, \gamma\)\\
+  \hspace*{1em} {\color{gray} \# Take \(N\) samples from the value distribution.}\\
+  \hspace*{1em} \textbf{for} \(i = 1 \dots N\)\\
+  \hspace*{2em} \(\epsilon_i \sim \N \left(0, I_{\lvert \A \rvert} \right)\)\\
+  \hspace*{2em} \textbf{for} \(a^\prime \in \A\)\\
+  \hspace*{3em} \(Z_{\tilde{\theta}}(\rvx^\prime, a^\prime)_i \gets v_{\tilde{\theta}}(\epsilon_i; \rvx^\prime)_{a^\prime}\)\\
+  \hspace*{2em} \textbf{end}\\
+  \hspace*{1em} \textbf{end}\\
+  \\\hspace*{1em} {\color{gray} \# Compute greedy next action.}\\
+  \hspace*{1em} \(a^* \gets \argmax_{a^\prime} \frac{1}{N} \sum_{i=1}^N Z_{\tilde{\theta}}(\rvx^\prime, a^\prime)_i\)\\
+  \\\hspace*{1em} {\color{gray} \# Calculate loss terms for each sample.}\\
+  \hspace*{1em} \textbf{for} \(i = 1 \dots N\)\\
+  \hspace*{2em} {\color{gray} \# Apply the distributional Bellman operator.}\\
+  \hspace*{2em} \(\hat{Z}_{\tilde{\theta}}(\rvx, a)_i \gets r + \gamma Z_{\tilde{\theta}}(\rvx^\prime, a^*)_i\)\\
+  \hspace*{2em} {\color{gray} \# Calculate log-probability under \(\N(0,1)\).}\\
+  \hspace*{2em} \(\delta_i \gets \frac{1}{2} v_{\theta}^{-1} 
+  \left(\hat{Z}_{\tilde{\theta}}(\rvx, a)_i; \rvx \right)^2\)\\
+  \hspace*{2em} {\color{gray} \# Calculate log-derivative of \(v^{-1}_\theta\).}\\
+  \hspace*{2em} \(\rho_i \gets \log \left\lvert \frac{\partial v_{\theta}^{-1} \left(\hat{Z}_{\tilde{\theta}}(\rvx, a)_i; \rvx \right)}{\hat{Z}_{\tilde{\theta}}(\rvx, a)_i} \right\rvert\)\\
+  \hspace*{1em} \textbf{end}\\
+  \textbf{output} \(\frac{1}{N}\sum_{i=1}^N \delta_i - \rho_i\)
+\end{algorithm}
 

### 2022-08-25 scripts/RLExp_QQFLOW_Atari.jl

@@ -202,7 +202,7 @@ function RL.Experiment(
             beg = rand((1 + N_FRAMES):size(s,3))
             s = s[:,:,(beg - N_FRAMES):(beg - 1)]
             s = Flux.unsqueeze(s, 4) |> gpu
-            samples = agent.policy.learner.B_approximator(s, 500)[1] |> cpu
+            samples = agent.policy.learner.approximator.source(s, 500)[1] |> cpu
             p = plot()
             for action in 1:size(samples, 1)
                 density!(samples[action, 1, :], c=action, label="action $(action)")

### 2022-08-27 papers/CDRL/sample_paper.tex
TEMPORARY DEPLOY COMMIT

@@
 \circ \dots \circ v_{\theta_2} \circ v_{\theta_1} \), such that
-\(Z_\theta(\rvx, a) = v_\theta(S; \rvx)_a\). To learn \(v_\theta\) we note that
+\(Z_\theta(\rvx, a) = v_\theta(S; \rvx^\prime)_a\). To learn \(v_\theta\) we note that
 we can take the inverse transformation \(v^{-1}_\theta\) of the value
@@
 \begin{equation}
-  S^\prime \eqdist v^{-1}_\theta \left(\T v_\theta(S; \rvx); \rvx^\prime \right).
+  S^\prime \eqdist v^{-1}_\theta \left(\T v_\theta(S; \rvx^\prime); \rvx \right).
 \end{equation}
 
-We can use this
+Because the inverse transformation of the value distribution given its state is
+standard normal, we can learn the parameters \(\theta\) using the
+change-of-variables formula from Equation~\ref{eq:change_var_form1}.
+Algorithm~\ref{alg:LTM} shows how to calculate the loss for this scheme.
 
@@
   \hspace*{2em} \(\hat{Z}_{\tilde{\theta}}(\rvx, a)_i \gets r + \gamma Z_{\tilde{\theta}}(\rvx^\prime, a^*)_i\)\\
-  \hspace*{2em} {\color{gray} \# Calculate log-probability under \(\N(0,1)\).}\\
+  \hspace*{2em} {\color{gray} \# Calculate log-likelihood under \(\N(0,1)\).}\\
   \hspace*{2em} \(\delta_i \gets \frac{1}{2} v_{\theta}^{-1} 

### 2022-08-27 scripts/RLExp_QQFLOW_Atari.jl

@@ -97,7 +97,7 @@ function RL.Experiment(
     
     flow_depth = get_config(lg, "flow_depth")
     # opt = eval(Meta.parse(get_config(lg, "opt")))
-    opt = ADAM(0.0000625, (0.9, 0.999), 0.00015)
+    opt = ADAM(0.00001, (0.9, 0.999), 0.00015)
     # lr = get_config(lg, "lr")
     # clip_norm = get_config(lg, "clip_norm")
 
@@ -107,8 +107,8 @@ function RL.Experiment(
         CrossCor((4, 4), 32 => 64, relu; stride=2, pad=2, init=initc),
         CrossCor((3, 3), 64 => 64, relu; stride=1, pad=1, init=initc),
         x -> reshape(x, :, size(x)[end]),
-        Dense(11 * 11 * 64, 512, relu, init=initc),
-        Dense(512, 1 + (3 * flow_depth) * N_ACTIONS, init=initc),
+        Dense(11 * 11 * 64, 1024, relu, init=initc),
+        Dense(1024, 1 + (3 * flow_depth) * N_ACTIONS, init=initc),
     ) |> gpu
 
 

### 2022-08-27 scripts/RLExp_QQFLOW_Cartpole.jl

@@ -37,7 +37,7 @@ function RL.Experiment(
     SET UP LOGGING
     """
     config = Dict(
-        "lr" => 5e-4,
+        "lr" => 5e-5,
         "update_freq" => 1,
         "target_update_freq" => 100,
         "n_samples_act" => 100,
@@ -50,8 +50,8 @@ function RL.Experiment(
         "is_enable_double_DQN" => true,
         "traj_capacity" => 100_000,
         "seed" => 2,
-        "flow_depth" => 8,
-        "num_steps" => 500,
+        "flow_depth" => 4,
+        "num_steps" => 5_000,
         "epsilon_decay_steps" => 500,
         "epsilon_stable" => 0.01,
     )
@@ -96,9 +96,9 @@ function RL.Experiment(
         model=TwinNetwork(
             FlowNet(;
                 net=Chain(
-                    Dense(ns, 512, relu; init=init),
-                    Dense(512, 512, relu; init=init),
-                    Dense(512, 1 + 3flow_depth * na; init=init),
+                    Dense(ns, 1024, relu; init=init),
+                    Dense(1024, 1024, relu; init=init),
+                    Dense(1024, 1 + 3flow_depth * na; init=init),
                     ),
                 ),
             ;
@@ -144,102 +144,105 @@ function RL.Experiment(
                 threshold=config["min_replay_history"],
             ),
             # controller = AsyncInsertSampleRatioController(
-            #     get_config(lg, "update_freq"),
+            #     1 ./ get_config(lg, "update_freq"),
             #     get_config(lg, "min_replay_history");
-            #     ch_in_sz = 1,
-            #     ch_out_sz = 1,
+            #     ch_in_sz = 10,
+            #     ch_out_sz = 10,
             # ),
         )
     )
-
+    @show "YESSSSS"
     """
     SET UP HOOKS
     """
-    # step_per_episode = StepsPerEpisode()
-    # reward_per_episode = TotalRewardPerEpisode()
-    # every_step = DoEveryNStep() do t, agent, env
-    #     try
-    #         with_logger(lg) do
-    #             p = agent.policy.learner.logging_params
-    #             L, nll, sldj, Qt, QA = p["loss"], p["nll"], p["sldj"], p["Qₜ"], p["QA"]
-    #             Q1, Q2, mu, sigma, l2norm = p["Q1"], p["Q2"], p["mu"], p["sigma"], p["l2norm"]
[…]

### 2022-08-27 scripts/run_qqflow_atari.jl

@@ -24,4 +24,4 @@ addprocs_slurm(n_workers; topology=:master_worker, exeflags=["--project=.", "--c
     include("RLExp_QQFLOW_Atari.jl")
 end
 
-run(E`RLExp_QQFLOW_Atari(game=asterix)`)
+run(E`RLExp_QQFLOW_Atari(game=breakout)`)

### 2022-08-27 src/algorithms/QQFLOW.jl

@@ -331,22 +331,22 @@ function RLBase.optimise!(learner::QQFLOWLearner, batch::NamedTuple)
         # loss = (sum(nll) - sum(sldj)) / n_samples_target + extra_loss
         loss = (loss + extra_loss) / batch_size
 
-        # ignore_derivatives() do
-        #     lp["loss"] = loss
-        #     lp["nll"] = sum(nll) / (batch_size * n_samples_target)
-        #     lp["sldj"] = sum(sldj) / (batch_size * n_samples_target)
-        #     lp["Qₜ"] = sum(target_distribution) / length(target_distribution)
-        #     lp["QA"] = sum(selected_actions)[1] / length(selected_actions)
-        #     lp["mu"] = sum(μ) / length(μ)
-        #     # lp["sigma"] = sum(σ[actions,:]) / length(σ[actions,:])
-        #     lp["max_weight"] = maximum(maximum.(Flux.params(Z)))
-        #     lp["min_weight"] = minimum(minimum.(Flux.params(Z)))
-        #     lp["max_pred"] = maximum(preds)
-        #     lp["min_pred"] = minimum(preds)
-        #     for i = 1:n_actions
-        #         lp["Q$i"] = sum(target_distribution[i,:]) / batch_size
-        #     end
-        # end
+        ignore_derivatives() do
+            lp["loss"] = loss
+            lp["extra_loss"] = extra_loss
+            # lp["sldj"] = sum(sldj) / (batch_size * n_samples_target)
+            # lp["Qₜ"] = sum(target_distribution) / length(target_distribution)
+            # lp["QA"] = sum(selected_actions)[1] / length(selected_actions)
+            lp["mu"] = mean(μ)
+            # lp["sigma"] = sum(σ[actions,:]) / length(σ[actions,:])
+            lp["max_weight"] = maximum(maximum.(Flux.params(Z)))
+            lp["min_weight"] = minimum(minimum.(Flux.params(Z)))
+            lp["max_pred"] = maximum(preds)
+            lp["min_pred"] = minimum(preds)
+            # for i = 1:n_actions
+            #     lp["Q$i"] = sum(target_distribution[i,:]) / batch_size
+            # end
+        end
 
         return loss
     end

### 2022-08-29 papers/CDRL/sample_paper.tex
TEMPORARY DEPLOY COMMIT

@@
 \begin{align*}
-  &\KL{q(\vtheta)}{p(\vtheta \vert \data)} =
-  \E{q(\vtheta)}{\log \frac{q(\vtheta)}{p(\vtheta \vert \data)}}\\
-  &= \E{q(\vtheta)}{\log q(\vtheta)} - \E{q(\vtheta)}{\log p(\vtheta \vert \data)}\\
-  &= \E{q(\vtheta)}{\log q(\vtheta)} - \E{q(\vtheta)}{\log
-  \frac{p(\vtheta, \data)}{p(\data)}}\\
-  &= \E{q(\vtheta)}{\log q(\vtheta)} - \E{q(\vtheta)}{\log p(\vtheta, \data)} +
-  \E{q(\vtheta)}{\log p(\data)}\\
-  &= \E{q(\vtheta)}{\log q(\vtheta)} - \E{q(\vtheta)}{\log p(\vtheta, \data)} +
-  \log p(\data)\\
+   & \KL{q(\vtheta)}{p(\vtheta \vert \data)} =
+  \E{q(\vtheta)}{\log \frac{q(\vtheta)}{p(\vtheta \vert \data)}}                     \\
+   & = \E{q(\vtheta)}{\log q(\vtheta)} - \E{q(\vtheta)}{\log p(\vtheta \vert \data)} \\
+   & = \E{q(\vtheta)}{\log q(\vtheta)} - \E{q(\vtheta)}{\log
+  \frac{p(\vtheta, \data)}{p(\data)}}                                                \\
+   & = \E{q(\vtheta)}{\log q(\vtheta)} - \E{q(\vtheta)}{\log p(\vtheta, \data)} +
+  \E{q(\vtheta)}{\log p(\data)}                                                      \\
+   & = \E{q(\vtheta)}{\log q(\vtheta)} - \E{q(\vtheta)}{\log p(\vtheta, \data)} +
+  \log p(\data)                                                                      \\
 \end{align*}
@@
 \begin{align}
-  q(\rvz^\prime) &= q(\rvz) \left\lvert \det \left( \frac{\partial \rvz}{
-    \partial \rvz^\prime} \right) \right\rvert \nonumber\\
-  &= q(v^{-1}(\rvz^\prime)) \left\lvert \det \left( \frac{\partial}{\partial
+  q(\rvz^\prime) & = q(\rvz) \left\lvert \det \left( \frac{\partial \rvz}{
+  \partial \rvz^\prime} \right) \right\rvert \nonumber                                       \\
+                 & = q(v^{-1}(\rvz^\prime)) \left\lvert \det \left( \frac{\partial}{\partial
     \rvz^\prime} v^{-1}(\rvz^\prime) \right) \right\rvert
@@
 \begin{align}
-  q(\rvz^\prime \vert \rvx) &= q(\rvz \vert \rvx) \left\lvert \det
+  q(\rvz^\prime \vert \rvx) & = q(\rvz \vert \rvx) \left\lvert \det
   \left( \frac{\partial \rvz}{\partial \rvz^\prime} \right) \right\rvert
-  \nonumber\\
-  &= q(v^{-1}(\rvz^\prime, \rvx)) \left\lvert \det \left( \frac{\partial}
+  \nonumber                                                                                          \\
+                            & = q(v^{-1}(\rvz^\prime, \rvx)) \left\lvert \det \left( \frac{\partial}
   {\partial \rvz^\prime} v^{-1}(\rvz^\prime, \rvx) \right) \right\rvert.
@@
   \hspace*{1em} \textbf{for} \(i = 1 \dots N\)\\
-  \hspace*{2em} \(\epsilon_i \sim \N \left(0, I_{\lvert \A \rvert} \right)\)\\
+  \hspace*{2em} \(\epsilon_i \sim \N \left(0, 1 \right)\)\\
   \hspace*{2em} \textbf{for} \(a^\prime \in \A\)\\
@@
   \hspace*{2em} \(\hat{Z}_{\tilde{\theta}}(\rvx, a)_i \gets r + \gamma Z_{\tilde{\theta}}(\rvx^\prime, a^*)_i\)\\
-  \hspace*{2em} {\color{gray} \# Calculate log-likelihood under \(\N(0,1)\).}\\
+  \hspace*{2em} {\color{gray} \# Calculate negative log-likelihood loss term.}\\
   \hspace*{2em} \(\delta_i \gets \frac{1}{2} v_{\theta}^{-1}
@@
 Equation~\ref{eq:luddeflow} shows the definitiona of the forward transformation
-\(v_{w, b, c, d}\), with 4 free parameters \(w, b, c, d\). Unlike the planar
-flow, this function is invertible and differentiable given any values for these
-parameters. Equation~\ref{eq:luddeflow_inv} and
-Equation~\ref{eq:luddeflow_grad} show the closed form gradient.
-
-% \begin{equation}
-%   Z_\theta(\rvx,a) = v_\theta^{-1}(z, \rvx^\prime)_a
-% \end{equation}
-% \begin{equation*}
-%   z \sim \N(0, I); \quad \rvx^\prime = h(\rvx)
-% \end{equation*}
-
-% \begin{equation*}
-%   s(x) = \log(1 + \exp(x))
-% \end{equation*}
-% \begin{equation}
-%   v_{w, b, c, d}(z) = \sign(z + c) \left[ s(\lvert w(z + c) \rvert + b) 
-%   - s(b) \right] + d \label{eq:luddeflow}
-% \end{equation}
-
-% \begin{equation*}
-%   s^{-1}(x) = \log(\exp(x) - 1); \quad x > 0
-% \end{equation*}
-% \begin{equation}
-%   v^{-1}_{w, b, c, d}(z^\prime) = \frac{\sign(z^\prime - d)}{w}
-%   [ s^{-1}(\lvert z^\prime - d \rvert + s(b)) - b] - c \label{eq:luddeflow_inv}
-% \end{equation}
-
-% \begin{equation}
-%   \frac{\partial v^{-1}_{w,b,c,d}}{\partial z^\prime} = \frac{(e^b + 1) 
-%   e^{\lvert z^\prime - d \rvert}}{w (e^b + 1)e^{\lvert z^\prime - d \rvert} - w}
-%   \label{eq:luddeflow_inv_grad}
-% \end{equation}
+\(v(\cdot; b, c, d)\), with 3 free parameters \(b, c, d\). Unlike the planar
+flow, this function has a closed form inverse and is differentiable given any values for these
+parameters, hence no reparameterization is necessary. Equation~\ref{eq:luddeflow_inv} and
+Equation~\ref{eq:luddeflow_grad} show the closed form inverse and gradient respectively.
 
@@
 Figure~\ref{fig:luddeflow} shows the effect of the free parameters. A simple
-description is \(w\) changes the slope of the function, \(b\) changes the
-\emph{linearity} of the function (as \(b\) goes to infinity, \(v\) approaches a
-linear function), \(c\) shifts the horizontally, and \(d\) shifts the function
-vertically.
+description is that \(b\) changes the
+\emph{linearity} of the function (\(v\) is linear when \(b = 0\), an expansive
+mapping when \(b < 0\) and a contraction when \(b > 0\)), \(c\) shifts \(v\) horizontally, and \(d\) shifts \(v\) vertically.
 
@@
   % \centerline{\fbox{This figure intentionally left non-blank}}
-  \includegraphics[width=\columnwidth]{luddeflow.png}
+  \includegraphics[width=\columnwidth]{new_flow.pdf}
   \vspace{.3in}
-  \caption{Illustration of the effect the free parameters have on the function).
+  \caption{Illustration of the effect the free parameters have on the function.
   }\label{fig:luddeflow}

### 2022-08-29 src/algorithms/DUQNS.jl

@@ -1,0 +1,209 @@
+export DUQNSLearner
+import ReinforcementLearning.RLBase.update!
+
+using DataStructures: DefaultDict
+using Distributions: Uniform, Product
+using StatsBase: sample
+using Flux.Losses
+import Statistics.mean
+
+mutable struct DUQNSLearner{
+    Tq<:AbstractApproximator,
+    Tt<:AbstractApproximator,
+    P<:AbstractPrior,
+    R<:AbstractRNG,
+} <: AbstractLearner
+    B_approximator::Tq
+    Q_approximator::Tt
+    flow
+    Q_lr::Float32
+    prior::P
+    λ::Union{Float32,Nothing}
+    min_replay_history::Int
+    B_update_freq::Int
+    Q_update_freq::Int
+    updates_per_step::Int
+    update_step::Int
+    sampler::NStepBatchSampler
+    rng::R
+    sse::SpectralSteinEstimator
+    injected_noise::Float32
+    n_samples::Int
+    is_enable_double_DQN::Bool
+    training::Bool
+    logging_params
+end
+
+function DUQNSLearner(;
+    B_approximator::Tq,
+    Q_approximator::Tt,
+    flow,
+    Q_lr::Real=0.01f0,
+    prior::AbstractPrior=FlatPrior(),
+    λ::Union{Real,Nothing}=1,
+    stack_size::Union{Int,Nothing}=nothing,
+    γ::Real=0.99f0,
+    batch_size::Int=32,
+    update_horizon::Int=1,
+    min_replay_history::Int=100,
+    B_update_freq::Int=1,
+    Q_update_freq::Int=1,
+    updates_per_step::Int=1,
+    traces=SARTS,
+    update_step::Int=0,
+    injected_noise::Real=0.01f0,
+    n_samples::Int=100,
+    η::Real=0.05f0,
+    nev::Int=10,
+    is_enable_double_DQN::Bool=false,
+    training::Bool=true,
+    rng=Random.GLOBAL_RNG
+) where {Tq,Tt,M}
+    sampler = NStepBatchSampler{traces}(;
+        γ=Float32(γ),
+        n=update_horizon,
+        stack_size=stack_size,
+        batch_size=batch_size
+    )
+    return DUQNSLearner(
+        B_approximator,
+        Q_approximator,
+        flow,
+        Float32(Q_lr),
+        prior,
+        Float32(λ),
+        min_replay_history,
+        B_update_freq,
+        Q_update_freq,
+        updates_per_step,
+        update_step,
[…]

### 2022-08-30 scripts/RLExp_QQFLOW_Atari.jl
TEMPORARY DEPLOY COMMIT

@@ -55,7 +55,7 @@ function RL.Experiment(
         "seed" => 1,
         "flow_depth" => 8,
         "terminal_on_life_loss" => true,
-        "adam_epsilon" => 1e-6,
+        "adam_epsilon" => 1e-8,
         "n_steps" => 200_000_000,
     )
 
@@ -86,7 +86,7 @@ function RL.Experiment(
         STATE_SIZE,
         N_FRAMES;
         seed=isnothing(seed) ? nothing : hash(seed + 1),
-        terminal_on_life_loss = terminal_on_life_loss,
+        terminal_on_life_loss=terminal_on_life_loss
     )
     N_ACTIONS = length(action_space(env))
 
@@ -95,10 +95,10 @@ function RL.Experiment(
     """
     initc = Flux.glorot_uniform(rng)
     # initc = Flux.kaiming_normal(rng)
-    
+
     flow_depth = get_config(lg, "flow_depth")
     # opt = eval(Meta.parse(get_config(lg, "opt")))
-    opt = ADAM(config["lr"], (0.9, 0.999), config["adam_epsilon"])
+    opt = AdaMax(config["lr"], (0.9, 0.999), config["adam_epsilon"])
     # opt = CenteredRMSProp(config["lr"], 0.0, config["adam_epsilon"])
     # lr = get_config(lg, "lr")
     # clip_norm = get_config(lg, "clip_norm")
@@ -121,7 +121,7 @@ function RL.Experiment(
             ),
             sync_freq=get_config(lg, "target_update_freq"),
         );
-        optimiser=opt,
+        optimiser=opt
     )
 
     """
@@ -138,27 +138,27 @@ function RL.Experiment(
                 n_samples_target=get_config(lg, "n_samples_target"),
                 is_enable_double_DQN=get_config(lg, "is_enable_double_DQN"),
             ),
-            explorer=EpsilonGreedyExplorer(                                                                                                                                                                                                             
-                ϵ_init = 1.0,
-                ϵ_stable = 0.01,
-                decay_steps = 1_000_000,
-                kind = :linear,
+            explorer=EpsilonGreedyExplorer(
+                ϵ_init=1.0,
+                ϵ_stable=0.01,
+                decay_steps=1_000_000,
+                kind=:linear,
                 rng=rng,
             ),
         ),
         trajectory=Trajectory(
-            container = CircularArraySARTTraces(
+            container=CircularArraySARTTraces(
[…]

### 2022-08-30 scripts/RLExp_QQFLOW_Cartpole.jl

@@ -45,7 +45,7 @@ function RL.Experiment(
         "opt" => "ADAM",
         "gamma" => 0.99,
         "update_horizon" => 1,
-        "batch_size" => 128,
+        "batch_size" => 32,
         "min_replay_history" => 100,
         "is_enable_double_DQN" => true,
         "traj_capacity" => 100_000,
@@ -89,7 +89,7 @@ function RL.Experiment(
 
     flow_depth = config["flow_depth"]
     # opt = eval(Meta.parse(get_config(lg, "opt")))
-    opt = ADAM(config["lr"], (0.9, 0.999), 0.0000015)
+    opt = AdaMax(config["lr"], (0.9, 0.999), 1e-8)
     approximator = Approximator(
         model=TwinNetwork(
             FlowNet(;

### 2022-08-30 src/algorithms/QQFLOW.jl

@@ -261,8 +261,9 @@ function RLBase.optimise!(learner::QQFLOWLearner, batch::NamedTuple)
     gs = gradient(Flux.params(Z)) do
         preds, sldj = Z(target_distribution, states, n_actions)
 
-        nll = preds[actions, :] .^ 2 / 2 .- sldj[actions, :]
-        loss = Flux.huber_loss(nll, zp[1, :, :] .^ 2 ./ 2) / (batch_size * n_samples_target)
+        nll = (preds[actions, :] .^ 2 / 2 .- sldj[actions, :])
+        # loss = Flux.huber_loss(nll, zp[1, :, :] .^ 2 ./ 2) 
+
 
         # abs_error = abs.(TD_error)
         # quadratic = min.(abs_error, 1)
@@ -275,7 +276,7 @@ function RLBase.optimise!(learner::QQFLOWLearner, batch::NamedTuple)
         # sldj = sldj[actions, :]
         # loss = sum(nll .- sldj) / n_samples_target #+ sum(log.(σ[actions, :]))
         # loss = (sum(nll) - sum(sldj)) / n_samples_target + extra_loss
-        # loss = (loss) / batch_size
+        loss = sum(nll) / (batch_size * n_samples_target)
 
         ignore_derivatives() do
             lp["loss"] = loss

### 2022-09-08 papers/CDRL/sample_paper.tex
TEMPORARY DEPLOY COMMIT
more

--- 2022-08-27 papers/CDRL/sample_paper.tex
@@
 
-\begin{equation}
-  \mathcal{L}_{\rvx,a}(\theta) \defeq \KL{Z_{\theta}(\rvx,a)}{\hat{\T}
-  Z_{\tilde{\theta}}(\rvx,a)}
-\end{equation}
+\begin{align}
+  \mathcal{L}_{\rvx,a}(\theta) &\defeq \KL{\hat{\T}
+  Z_{\tilde{\theta}}(\rvx,a)}{Z_{\theta}(\rvx,a)}\\
+  &= \E{\hat{\T} Z_{\tilde{\theta}}(\rvx,a)}{\log \hat{\T}
+  Z_{\tilde{\theta}}(\rvx,a) - \log Z_{\theta}(\rvx,a)}\nonumber\\
+  &= \E{\hat{\T} Z_{\tilde{\theta}}(\rvx,a)}{- \log Z_{\theta}(\rvx,a)} + const.\nonumber\\
+  &\propto -\E{v_\theta^{-1}(\hat{\T} Z_{\tilde{\theta}}(\rvx,a))}{
+    \log v^{-1}_\theta \left( \hat{\T} Z_{\tilde{\theta}}(\rvx,a) \right) + \log \left\lvert J_{v_\theta^{-1}}(\rvx, a) \right\rvert}\nonumber
+\end{align}
 
@@
   \hspace*{2em} \(\hat{Z}_{\tilde{\theta}}(\rvx, a)_i \gets r + \gamma Z_{\tilde{\theta}}(\rvx^\prime, a^*)_i\)\\
-  \hspace*{2em} {\color{gray} \# Calculate log-likelihood under \(\N(0,1)\).}\\
+  \hspace*{2em} {\color{gray} \# Calculate negative log-likelihood.}\\
   \hspace*{2em} \(\delta_i \gets \frac{1}{2} v_{\theta}^{-1} 
@@
   \hspace*{1em} \textbf{end}\\
-  \textbf{output} \(\frac{1}{N}\sum_{i=1}^N \delta_i - \rho_i\)
+  \textbf{output} \(\frac{1}{N}\sum_{i=1}^N huberloss(\delta_i - \rho_i, \epsilon_i)\)
 \end{algorithm}
@@
 The most popular normalizing flows right now are buildt for large dimensional
-spaces such as images. This includes coupling and autoregressive flows. Planar
-flow is very easy to turn elementwise, but unfortunately does not have a closed
-form inverse for most functions of \(h\). Although it does have one for
-piecewise linear funcitons, those do not have second derivative, hence the
-gradient of the log absolute determinant would be zero. This would mean it can
-not learn appropriate transformations. Instead we define our own flow.
+spaces such as images. This includes coupling and autoregressive flows. These
+will not work for our method, since \(Z_\theta(\rvx, a)\) is a univariate
+distribution. Planar flow is also not a good option since it does not have a
+closed form inverse 
+% Planar
+% flow is very easy to turn elementwise, but unfortunately does not have a closed
+% form inverse for most functions of \(h\). Although it does have one for
+% piecewise linear funcitons, those do not have second derivative, hence the
+% gradient of the log absolute determinant would be zero. This would mean it can
+% not learn appropriate transformations. Instead we define our own flow.
 
 Equation~\ref{eq:luddeflow} shows the definitiona of the forward transformation
-\(v_{w, b, c, d}\), with 4 free parameters \(w, b, c, d\). Unlike the planar
+\(v(z; b, c, d)\), with 3 free parameters \(b, c, d\). Unlike the planar
 flow, this function is invertible and differentiable given any values for these
@@
 Figure~\ref{fig:luddeflow} shows the effect of the free parameters. A simple
-description is \(w\) changes the slope of the function, \(b\) changes the
-\emph{linearity} of the function (as \(b\) goes to infinity, \(v\) approaches a
-linear function), \(c\) shifts the horizontally, and \(d\) shifts the function
-vertically.
+description is that \(b\) changes the
+\emph{linearity} of the function \(c\) shifts the horizontally, and
+\(d\) shifts the function vertically.
 

### 2022-09-08 src/algorithms/QQFLOW.jl

@@ -190,9 +190,9 @@ function (m::FlowNet)(state::AbstractArray, num_samples::Int, na::Int)
     z, pz
 end
 
-function (m::FlowNet)(z::AbstractArray, state::AbstractArray, na::Int)
+function (m::FlowNet)(z::AbstractArray{Float32}, state::AbstractArray{Float32}, na::Int)
     ξ = m.net(state)
-    i = size(ξ, 1)
+    # i = size(ξ, 1)
     # μ = @inbounds ξ[i:i,:]
     # ρ = @inbounds ξ[(na+1):(2na),:]
     # σ = Flux.softplus.(ρ)
@@ -290,6 +290,7 @@ function RLBase.optimise!(learner::QQFLOWLearner, batch::NamedTuple)
     if learner.is_enable_double_DQN
         q_values, pz = Z(next_states, n_samples_target, n_actions)
     else
+        # q_values, pz = Z(next_states, n_samples_target, n_actions)
         q_values, pz = Zₜ(next_states, n_samples_target, n_actions)
     end
 
@@ -318,9 +319,9 @@ function RLBase.optimise!(learner::QQFLOWLearner, batch::NamedTuple)
         preds, sldj = Z(target_distribution, states, n_actions)
 
         nll = preds[actions, :] .^ 2 ./ 2 .- sldj[actions, :]
-        
 
-        loss = Flux.huber_loss(nll, nll2) / (n_samples_target * batch_size)
+        # loss = Flux.huber_loss(nll, nll2)
+        loss = mean(nll)
 
         ignore_derivatives() do
             lp["loss"] = loss
